### 2022-06-15 Seminar/preamble.tex
Adding seminar files

%load any additional packages

\usepackage[UKenglish]{babel}
\usepackage[utf8]{inputenc} % so we can input characters with accents (e.g. ő)

\usepackage{statsbeamer}
\usepackage{multirow,booktabs}%pacotes para tabelas
\usepackage{subcaption}
\usepackage[font=footnotesize,skip=2pt]{caption}
%\captionsetup[table]{skip=2pt}
\usepackage{ragged2e}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}
\tikzset{%
  >={Latex[width=2mm,length=2mm]},
  % Specifications for style of nodes:
            base/.style = {rectangle, rounded corners, draw=black,
                           minimum width=4cm, minimum height=1cm,
                           text centered, font=\sffamily},
  activityStarts/.style = {base, fill=oxfordblue!30},
       startstop/.style = {base, fill=oxfordblue!30},
    activityRuns/.style = {base, fill=oxfordblue!30},
         process/.style = {base, minimum width=2.5cm, fill=orange!15},
}

\usepackage{graphicx} % ease graphics management
\graphicspath{{figs/}} % define folder with images
\usefonttheme{serif} % change font to allow \textbf{}
\usepackage{charter} % Nicer fonts

\usepackage{cancel}
\usepackage{amsmath,amsthm,amssymb} % for math equations

\usepackage[numbers]{natbib} % richer citation
\usepackage{breakcites} % avoid overfull hbox for long cites

\usepackage{algorithm,algorithmic}                                          % Pseudo-code environment
\usepackage{amsmath,amsfonts,amsthm,amssymb,bm,mathdots,mathtools,bigints}  % Math packages

\usepackage{caption}                        % Tools for customizing the \caption{} command
\usepackage{subcaption}						% Environment to create subcaptions

\captionsetup{singlelinecheck = false, format= hang, justification=raggedright, font=footnotesize, labelsep=space} % ABNT Format for Caption

### 2022-06-15 Additional Problems/Multilinear Transformations and Multilinear Rank/manuscript.tex
Adding files

\documentclass[a4paper,10pt]{article}

\usepackage{cite}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amstext,amsmath,amssymb}
\usepackage[shortlabels]{enumitem}

\setlength{\oddsidemargin}{0cm} %
\setlength{\evensidemargin}{0cm} %
\setlength{\topmargin}{0cm} %
\setlength{\textwidth}{16cm} %
\setlength{\textheight}{22.5cm} %

\pagestyle{fancy}
\newcommand{\assunto}{Multilinear Transformations and Rank}

\sloppy

\begin{document}

\input{front.tex}
\thispagestyle{empty}

\newpage

\thispagestyle{empty}

\begin{enumerate}
\renewcommand{\labelenumi}{{\Large\bfseries\arabic{enumi}.}}

    \item This problem can be solved by showing that the multilinear rank of the tensor $\mathcal{Y}$ is the same one as in tensor $\mathcal{X}$. The tensor $\mathcal{X}$ has dimensions $\mathbb{C}^{I_{1} \times ... \times I_{N}}$. Since the multilinear rank is defined by the rank of each unfold of a given tensor we can then define the multilinear rank of $\mathcal{X}$ as the group of values obtained with the following operation

        \begin{align}
            \forall n \in \{1, \cdots, N\}, R_{n} &= \text{Rank}\left( \left[ \mathcal{X} \right]_{(n)} \right) \leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\}. \label{eq:01}
        \end{align}

        \paragraph{}In a similar fashion we can define the multilinear rank of the tensor $\mathcal{Y}$  writing its unfoldings according to the equation of the multilinear transformation

        \begin{align}
            \mathcal{Y} &= \mathcal{X} \times_{1} \boldsymbol{A}^{(1)} \times_{2} \cdots \times_{N} \boldsymbol{A}^{(N)} \in \mathbb{C}^{I_{1} \times ... \times I_{N}}, \\
            \left[ \mathcal{Y} \right]_{(n)} &= \boldsymbol{A}^{(n)} \left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right)^{\text{T}} \in \mathbb{C}^{I_{n} \times \prod_{m \neq n} I_{m}}.
        \end{align}

        \paragraph{}From equation above we can then write the following expression for the multilinear rank of $\mathcal{Y}$, considering $\forall n \in \{1, \cdots, N\}$, as

        \begin{align}
            R_{n} = \text{Rank}\left( \left[ \mathcal{Y} \right]_{(n)} \right) = \text{Rank}\left( \boldsymbol{A}^{(n)} \left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right)^{\text{T}} \right),
        \end{align}

        and we know that every $\boldsymbol{A}^{(n)}$ matrix is full-rank since by the definition of the multilinear transformation these matrices are nonsingular. Furthermore, is necessary to remember that the kronecker product will not increase the rank and thus the product on the right will have its rank limited by the rank of $\mathcal{X}$ and will be the product between the ranks of each matrix. In the same manner the matrix on the left will have its rank limited by the tensor $\mathcal{X}$. Consequently, knowing that the column rank and the row rank of a square matrix coincide and that the rank of a nonsquare matrix is at most the minimum between the column rank and the row rank we have

        \begin{align}
            \text{Rank}\left( \boldsymbol{A}^{(n)} \right) &= I_{n}, \label{mtx1} \\
            \text{Rank}\left( \left[ \mathcal{X} \right]_{(n)} \right) &\leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\}, \label{mtx2} \\
            \text{Rank}\left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right) &= \prod_{m \neq n} I_{m}. \label{mxt3}
        \end{align}

        \paragraph{}Now the product between (\ref{mtx2}) and (\ref{mxt3}) it is a full-rank matrix projected onto the column space of the relevant matrices and its rank is defined as

        \begin{align}
            \text{Rank}\left( \left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right) \right) &\leq \text{min} \left\{ \prod_{m \neq n} I_{m}, \prod_{m \neq n} I_{m} \right\}, \\  
            \text{Rank}\left( \left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right) \right) &= \prod_{m \neq n} I_{m}.
        \end{align}

        \paragraph{}Therefore, the product between $\boldsymbol{A}^{(n)}$ and $\left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right) $ is projected onto the column space of these matrices and can be evaluate as

        \begin{align}
            \text{Rank}\left( \boldsymbol{A}^{(n)} \left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right) \right) &\leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\}, \\
            \text{Rank}\left( \mathcal{Y} \right) &\leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\}.
        \end{align}

        \paragraph{}As consequence we have that the multilinear rank of tensor $\mathcal{Y}$ is limited by the multilinear rank of the core tensor meaning that both share the geometric structure\footnote{Only if the matrices $\boldsymbol{A}^{(n)} \in \mathbb{C}^{I_{n} \times I_{n}}$ are nonsingular.}

        \begin{align}
            \forall n \in \{1, \cdots, N\}, R_{n} = \text{Rank}\left( \left[ \mathcal{Y} \right]_{(n)} \right) = \text{Rank}\left( \left[ \mathcal{X} \right]_{(n)} \right).
        \end{align}

    \item

        \begin{enumerate}

            \item Proof $\mathcal{Y} = \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}$ that is indeed a projection:

            \paragraph{}Since we have that the matrix $\boldsymbol{P}^{(n)}$ is idempotent and self-adjoint then $\left(\boldsymbol{P}^{(n)}\right)^2 = \boldsymbol{P}^{(n)}$ and $\left(\boldsymbol{P}^{(n)}\right)^{\text{H}} = \boldsymbol{P}^{(n)}$, respectively. To show that $\boldsymbol{P}^{(n)}$ is a projection of tensor $\mathcal{X}$ onto $\mathcal{Y}$ tensor subspace defined by $\mathcal{Y} = \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}$ we need to show that

            \begin{align}
                \left( \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} \right) \times_{n} \boldsymbol{P}^{(n)} &= \left( \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} \right), \\
                \left< \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}, \mathcal{Y} \right> &= \left< \mathcal{X},  \mathcal{Y} \times_{n} \boldsymbol{P}^{(n)}\right>.  
            \end{align}

            \paragraph{}The first expression can be obtained if we develop the nth mode product by using the unfolding operation

            \begin{align}
                \left( \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} \right) \times_{n} \boldsymbol{P}^{(n)}, \\
                \left( \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} \right) \times_{n} \boldsymbol{P}^{(n)}, \\
                \boldsymbol{P}^{(n)} \left( \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} \right) = \left(\boldsymbol{P}^{(n)}\right)^2 \left[\mathcal{X}\right]_{(n)}, \\
            \end{align}

            and because we have $\left(\boldsymbol{P}^{(n)}\right)^2 = \boldsymbol{P}^{(n)}$ then

            \begin{align}
                \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} = \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}.
            \end{align}

            \paragraph{}Relatively to the nth mode product self-adjoint property we can start by writing

            \begin{align}
                \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} &= \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \\
                \mathcal{Y} \times_{n} \left(\boldsymbol{P}^{(n)}\right)^{\text{H}} &= \left(\boldsymbol{P}^{(n)}\right)^{\text{H}} \left[\mathcal{Y}\right]_{(n)}, \\
            \end{align}

            \paragraph{} and starting from the inner-product expression we can write

            \begin{align}
                \left< \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}, \mathcal{Y} \right>, \\
                \left< \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}, \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} \right>, \\
                \left< \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} \right>,
            \end{align}

            and as long as $\boldsymbol{P}^{(n)}$ has a self-adjoint

            \begin{align}
                \left< \left[\mathcal{X}\right]_{(n)}, \left( \boldsymbol{P}^{(n)} \right)^{\text{H}} \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} \right>, \\
                \left< \left[\mathcal{X}\right]_{(n)}, \boldsymbol{P}^{(n)} \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} \right>,
            \end{align}

            and knowing that $\left[\mathcal{Y}\right]_{(n)} = \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}$

            \begin{align}
                \left< \left[\mathcal{X}\right]_{(n)}, \boldsymbol{P}^{(n)} \left[\mathcal{Y}\right]_{(n)} \right>,
            \end{align}

            and redoing the nth mode product leads to

            \begin{align}
                \left< \mathcal{X}, \mathcal{Y} \times_{n} \boldsymbol{P}^{(n)} \right>.
            \end{align}

            \item Proof the nonexpansiveness of $|| \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} ||_{\text{F}} = || \mathcal{X} ||_{\text{F}}$:

            \paragraph{}We can start by writing the squared Frobenius norm with the inner product notation and then defining the self-adjoint of the projection

            \begin{align}
                || \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} ||^{2}_{\text{F}} &= || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} ||^{2}_{\text{F}} , \\ || <\boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}} &= || < \left( \boldsymbol{P}^{(n)} \right)^{*} \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}}, \\
                || < \boldsymbol{P}^{(n)} \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}} &= || < \left( \boldsymbol{P}^{(n)} \right)^{2} \left[\mathcal{X}\right]_{(n)}, \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}},
            \end{align}

            and since we already know that $\boldsymbol{P}^{(n)}$ is idempotent then

            \begin{align}
                || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} ||^{2}_{\text{F}} &= || < \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}}. \label{eq:03}
            \end{align}

            \paragraph{}Equation (\ref{eq:03}) is a well known expression from Linear Algebra and with this the tensor expression could be reduced to a regular matrix expression. To finish, we can apply the Cauchy-Schwarz inequality and

            \begin{align}
                || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} ||^{2}_{\text{F}} &= || < \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}}, \\
                || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} ||^{2}_{\text{F}} &\leq || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}||_{\text{F}} \hspace{.25cm} || \left[\mathcal{X}\right]_{(n)} ||_{\text{F}} , \\
                || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} ||_{\text{F}} &\leq || \left[\mathcal{X}\right]_{(n)} ||_{\text{F}}.
            \end{align}

            \paragraph{}Thus, the nth-mode product is a non-expansive operation.

        \end{enumerate}

    \item From previous problems we know that the multilinear rank of $\mathcal{X} \in \mathbb{C}^{I_{1} \times \cdots \times I_{N}}$ is $(R_{1}, \cdots, R_{N})$ and that we can easily acquire an expression for it by analyzing the profile of the unfoldings of said tensor. Moreover we can define a multilinear transformation where tensor $\mathcal{X}$ acts as the core tensor. Thus, we define another tensor, let's call it $\mathcal{Y}$, where its nth mode unfolding can be written as

        \begin{align}
            \mathcal{Y} &= \mathcal{X} \times_{1} \boldsymbol{A}^{(1)} \times_{2} \cdots \times_{N} \boldsymbol{A}^{(N)} \in \mathbb{C}^{I_{1} \times ... \times I_{N}}, \\
            \left[\mathcal{Y}\right]_{(n)} &= \boldsymbol{A}^{(n)} \left[\mathcal{X}\right]_{(n)} \left(\boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right)^{T} \in \mathbb{C}^{I_{n} \times \prod_{m \neq n} I_{m}}. \label{eq:02}
        \end{align}

        \paragraph{}From Equation (\ref{eq:02}) and with a similar procedure already developed in a previous problem we can obtain an expression for the multilinear rank of $\mathcal{Y}$ as

        \begin{align}
            \forall n \in \{1, \cdots, N\}, \text{Rank} \left( \left[\mathcal{Y}\right]_{(n)} \right) \leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\},
        \end{align}

        and as proofed before we know that tensors are objects with a well-defined geometry and that the multilinear rank is in fact a property of the tensor that is not lost when a multilinear transformation is applied\footnote{If the group of factor matrices are nonsingular.}. Thus, we can guarantee that the multilinear rank of the tensor $\mathcal{Y}$ will be the same as the one for the tensor $\mathcal{X}$

        \begin{align}
            \forall n \in \{1, \cdots, N\}, \text{Rank} \left( \left[\mathcal{X}\right]_{(n)} \right) \leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\},
        \end{align}

    \item In the context of multilinear transformation

        \begin{enumerate}

            \item Proof that the operation is linear in the transformed tensor:

                \begin{align}
                    (\alpha_{1} \mathcal{X}_{1} + \alpha_{2} \mathcal{X}_{2}) \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{N} \boldsymbol{A}^{(N)} \in \mathbb{C}^{I_{1} \times ... \times I_{N}}.
                \end{align}

                \paragraph{}Starting by applying the following property of the n-mode product we can reorder the expression in a usefully way

                \begin{align}
                    \mathcal{X} \times_{m} \boldsymbol{A}^{(m)} \times_{n} \boldsymbol{A}^{(n)} = \mathcal{X} \times_{n} \boldsymbol{A}^{(n)} \times_{m} \boldsymbol{A}^{(m)}. 
                \end{align}

                \paragraph{}The core of this demonstration is the fact that we can reduce the nth mode product to a regular product between matrices which is known to be a linear operation. Thus,

                \begin{align}
                    &(\alpha_{1} \mathcal{X}_{1} + \alpha_{2} \mathcal{X}_{2}) \times_{n} \boldsymbol{A}^{(n)} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)}, \\
                    &\boldsymbol{A}^{(n)} \left( \alpha_{1} \left[\mathcal{X}_{1}\right]_{(n)} +  \alpha_{2} \left[\mathcal{X}_{2}\right]_{(n)} \right) \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)},
                \end{align}

                and now considering that the product between matrices is linear we have

                \begin{align}
                    \left(\alpha_{1} \boldsymbol{A}^{(n)} \left[\mathcal{X}_{1}\right]_{(n)}\right) \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)} + \\ 
                    \left(\alpha_{2} \boldsymbol{A}^{(n)} \left[\mathcal{X}_{2}\right]_{(n)}\right)  \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)},
                \end{align}

                and finally redoing the nth mode product leads to

                \begin{align}
                    \alpha_{1} \mathcal{X}_{1} \times_{n} \boldsymbol{A}^{(n)} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)} + \\ 
                    \alpha_{2} \mathcal{X}_{2} \times_{n} \boldsymbol{A}^{(n)} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)},
                \end{align}

            \item Proof that the operation is linear for each factor matrix:

                \begin{align}
                    \mathcal{X} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n} (\alpha_{1} \boldsymbol{Z}^{(n)}_{1} + \alpha_{2} \boldsymbol{Z}^{(n)}_{2}) \times_{n+1} \cdots \times_{N} \boldsymbol{A}^{(N)} \in \mathbb{C}^{I_{1} \times ... \times I_{N}}.
                \end{align}

                \paragraph{}In a similar view of the previous item we can start by reordering the n-mode product and explore the regular properties of the product between matrices

                \begin{align*}
                    \mathcal{X} \times_{n} (\alpha_{1} \boldsymbol{Z}^{(n)}_{1} + \alpha_{2} \boldsymbol{Z}^{(n)}_{2}) \times_{1} \boldsymbol{A}^{(1)} \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)} \in \mathbb{C}^{I_{1} \times ... \times I_{N}}, \\
                    (\alpha_{1} \boldsymbol{Z}^{(n)}_{1} + \alpha_{2} \boldsymbol{Z}^{(n)}_{2}) \left[\mathcal{X}\right]_{(n)} \times_{1} \boldsymbol{A}^{(1)} \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)}.
                \end{align*}

                \paragraph{}Now applying the distribute property and redoing the nth mode product notation

                \begin{align*}
                    &\alpha_{1} \boldsymbol{Z}^{(n)}_{1} \left[\mathcal{X}\right]_{(n)} \times_{1} \boldsymbol{A}^{(1)}  \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)} + \\
                    &\alpha_{2} \boldsymbol{Z}^{(n)}_{2} \left[\mathcal{X}\right]_{(n)} \times_{1} \boldsymbol{A}^{(1)} \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)}, \\
                    &\alpha_{1} \mathcal{X} \times_{n} \boldsymbol{Z}^{(n)}_{1} \times_{1} \boldsymbol{A}^{(1)} \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)} + \\
                    &\alpha_{2} \mathcal{X} \times_{n} \boldsymbol{Z}^{(n)}_{2} \times_{1} \boldsymbol{A}^{(1)} \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)},
                \end{align*}

                and reordering the expression results the following expression

                \begin{align*}
                    &\alpha_{1} \mathcal{X}  \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n} \boldsymbol{Z}^{(n)}_{1} \cdots \times_{N} \boldsymbol{A}^{(N)} + \\
                    &\alpha_{2} \mathcal{X}  \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n} \boldsymbol{Z}^{(n)}_{2} \cdots \times_{N} \boldsymbol{A}^{(N)},
                \end{align*}

            \item Using the previous problems obtain an expression for:

                \begin{align}
                    \mathcal{X} = \boldsymbol{u}_{1} \circ \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1} + \boldsymbol{u}_{2} \circ \boldsymbol{v}_{2} \circ \boldsymbol{w}_{2} \rightarrow \mathcal{X} \times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C}.
                \end{align}

                \paragraph{}First, we can input the low-rank decomposition of tensor $\mathcal{X}$ into the multilinear transformation

                \begin{align}
                    \mathcal{X} &\times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C}, \\
                    \left( \boldsymbol{u}_{1} \circ \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1} + \boldsymbol{u}_{2} \circ \boldsymbol{v}_{2} \circ \boldsymbol{w}_{2} \right) &\times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C},
                \end{align}

                and knowing that the nth mode product is a linear operation

                \begin{align}
                    \left( \boldsymbol{u}_{1} \circ \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1} \right) &\times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C} + \left( \boldsymbol{u}_{2} \circ \boldsymbol{v}_{2} \circ \boldsymbol{w}_{2} \right) \times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C},
                \end{align}

                considering that both terms have the same structure we can focus on only one and later apply the result to the other. Before we proceed we should define the unfolding of the subtensor formed by the outer product of $\mathcal{X}_{1} = \boldsymbol{u}_{1} \circ \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1}$ as\footnote{Since we are manipulating vectors the Khatri-Rao product can be simply reduced to the Kronecker product.}

                \begin{align}
                    \left[\mathcal{X}_{1}\right]_{(1)} = \boldsymbol{u}_{1} (\boldsymbol{v}_{1} \otimes \boldsymbol{w}_{1})^{\text{T}} \in \mathbb{C}^{I_{1} \times I_{2} I_{3}}, \\
                    \left[\mathcal{X}_{1}\right]_{(2)} = \boldsymbol{v}_{1} (\boldsymbol{u}_{1} \otimes \boldsymbol{w}_{1})^{\text{T}} \in \mathbb{C}^{I_{2} \times I_{1} I_{3}}, \\
                    \left[\mathcal{X}_{1}\right]_{(3)} = \boldsymbol{w}_{1} (\boldsymbol{u}_{1} \otimes \boldsymbol{v}_{1})^{\text{T}} \in \mathbb{C}^{I_{3} \times I_{1} I_{2}}.
                \end{align}

                \paragraph{}Now applying these expressions onto the multilinear transformation of the first subtensor as

                \begin{align}
                    \left( \boldsymbol{A} \left[\mathcal{X}_{1}\right]_{(1)} \right) \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C} = \left[ \boldsymbol{A}\boldsymbol{u}_{1} (\boldsymbol{v}_{1} \otimes \boldsymbol{w}_{1})^{\text{T}}  \right] \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C},
                \end{align}

                and by understanding that $\boldsymbol{A}\boldsymbol{u}_{1} \in \mathbb{C}^{I_{1} \times 1}$ is a vector we can redo the outer product by doing the folding operation, creating a new subtensor each time, and repeat the process for each factor matrix. By the end of this we reach the expression

                \begin{align}
                    \left( \boldsymbol{A} \boldsymbol{u}_{1} \circ \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1} \right) \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C}, \\
                    \left( \boldsymbol{A} \boldsymbol{u}_{1} \circ \boldsymbol{B} \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1} \right) \times_{3} \boldsymbol{C}, \\
                    \left( \boldsymbol{A} \boldsymbol{u}_{1} \circ \boldsymbol{B} \boldsymbol{v}_{1} \circ \boldsymbol{C} \boldsymbol{w}_{1} \right) \in \mathbb{C}^{I_{1} \times I_{2} \times I_{3}}.
                \end{align}

                \paragraph{}Now we can apply the same process to the other subtensor defined as $\mathcal{X}_{2} = \boldsymbol{u}_{2} \circ \boldsymbol{v}_{2} \circ \boldsymbol{w}_{2}$ and sum the contributions of each one since the nth mode product is already known to be a linear operation

                \begin{align}
                    \mathcal{X} &\times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C} = \left( \boldsymbol{A} \boldsymbol{u}_{1} \circ \boldsymbol{B} \boldsymbol{v}_{1} \circ \boldsymbol{C} \boldsymbol{w}_{1} \right) + \left( \boldsymbol{A} \boldsymbol{u}_{2} \circ \boldsymbol{B} \boldsymbol{v}_{2} \circ \boldsymbol{C} \boldsymbol{w}_{2} \right) \in \mathbb{C}^{I_{1} \times I_{2} \times I_{3}}.
                \end{align}

                \paragraph{}Thus, by applying the nth mode product between a tensor and a factor matrix we are projecting the fibers of said tensor onto the column space of the corespondent factor matrix.
        \end{enumerate}

    \item In the context of High-Order Single Value Decomposition (HOSVD)

        \begin{enumerate}

            \item Show that, for any orthogonal projector $\boldsymbol{P}$ and any mode $\boldsymbol{n}$, we have

                \begin{align}
                    \left< \mathcal{X} \times_{n} \boldsymbol{P}, \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) \right> &= 0, \label{eq:04} \\
                    || \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} &= || \mathcal{X} \times_{n} \boldsymbol{P} ||^{2}_{\text{F}} + ||  \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} \label{eq:05}.
                \end{align}

                \paragraph{}To obtain Equation (\ref{eq:04}) we can just reduce it to the matrix case by developing the nth mode product

                \begin{align}
                    \left< \mathcal{X} \times_{n} \boldsymbol{P}, \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) \right> &=\left< \boldsymbol{P} \left[\mathcal{X}\right]_{(n)}, (\boldsymbol{I} - \boldsymbol{P}) \left[\mathcal{X}\right]_{(n)} \right>,
                \end{align}

                but we know from Linear Algebra that the matrix $(\boldsymbol{I} - \boldsymbol{P})$ is the orthogonal complement of the projection $\boldsymbol{P}$ meaning that the inner product between $\boldsymbol{P} \left[\mathcal{X}\right]_{(n)}$ and $(\boldsymbol{I} - \boldsymbol{P}) \left[\mathcal{X}\right]_{(n)}$ will be zero. In sequence we can use this knowledge to develop the expression for $|| \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}}$ as

                \begin{align*}
                    || \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} &= || \mathcal{X} \times_{n} \boldsymbol{P} ||^{2}_{\text{F}} + ||  \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} -2 ||  \mathcal{X} \times_{n} \boldsymbol{P}  ||_{\text{F}} || \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||_{\text{F}},
                \end{align*}

                and we know that $||  \mathcal{X} \times_{n} \boldsymbol{P}  ||_{\text{F}} || \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||_{\text{F}} = \left< \mathcal{X} \times_{n} \boldsymbol{P}, \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) \right> = 0$ which leads to

                \begin{align*}
                    || \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} &= || \mathcal{X} \times_{n} \boldsymbol{P} ||^{2}_{\text{F}} + || \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} -2 \cdot 0, \\
                    || \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} &= || \mathcal{X} \times_{n} \boldsymbol{P} ||^{2}_{\text{F}} + || \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}}.
                \end{align*}

                \paragraph{}An interesting way to see this expression is by the Pythagorean theorem where $|| \mathcal{X} \times_{n} \boldsymbol{P} ||^{2}_{\text{F}}$ and $|| \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}}$ acts as the opposing sides to the hypotenuse $|| \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}}$.

            \item

            \item

            \item

        \end{enumerate}

\end{enumerate}

%\bibliographystyle{ieeetr}
%\bibliography{bibliography.bib}

\end{document}

### 2022-06-15 Additional Problems/PARAFAC and Tensor Rank/manuscript.tex
Adding files

--- 2022-06-15 Additional Problems/Multilinear Transformations and Multilinear Rank/manuscript.tex
@@
 \pagestyle{fancy}
-\newcommand{\assunto}{Multilinear Transformations and Rank}
+\newcommand{\assunto}{PARAFAC and Tensor Rank}
 
@@
 
-    \item This problem can be solved by showing that the multilinear rank of the tensor $\mathcal{Y}$ is the same one as in tensor $\mathcal{X}$.
-The tensor $\mathcal{X}$ has dimensions $\mathbb{C}^{I_{1} \times ...
-\times I_{N}}$.
-Since the multilinear rank is defined by the rank of each unfold of a given tensor we can then define the multilinear rank of $\mathcal{X}$ as the group of values obtained with the following operation
-
-        \begin{align}
-            \forall n \in \{1, \cdots, N\}, R_{n} &= \text{Rank}\left( \left[ \mathcal{X} \right]_{(n)} \right) \leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\}. \label{eq:01}
-        \end{align}
-
-        \paragraph{}In a similar fashion we can define the multilinear rank of the tensor $\mathcal{Y}$  writing its unfoldings according to the equation of the multilinear transformation
-
-        \begin{align}
-            \mathcal{Y} &= \mathcal{X} \times_{1} \boldsymbol{A}^{(1)} \times_{2} \cdots \times_{N} \boldsymbol{A}^{(N)} \in \mathbb{C}^{I_{1} \times ... \times I_{N}}, \\
-            \left[ \mathcal{Y} \right]_{(n)} &= \boldsymbol{A}^{(n)} \left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right)^{\text{T}} \in \mathbb{C}^{I_{n} \times \prod_{m \neq n} I_{m}}.
-        \end{align}
-
-        \paragraph{}From equation above we can then write the following expression for the multilinear rank of $\mathcal{Y}$, considering $\forall n \in \{1, \cdots, N\}$, as
-
-        \begin{align}
-            R_{n} = \text{Rank}\left( \left[ \mathcal{Y} \right]_{(n)} \right) = \text{Rank}\left( \boldsymbol{A}^{(n)} \left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right)^{\text{T}} \right),
-        \end{align}
-
-        and we know that every $\boldsymbol{A}^{(n)}$ matrix is full-rank since by the definition of the multilinear transformation these matrices are nonsingular.
-Furthermore, is necessary to remember that the kronecker product will not increase the rank and thus the product on the right will have its rank limited by the rank of $\mathcal{X}$ and will be the product between the ranks of each matrix.
-In the same manner the matrix on the left will have its rank limited by the tensor $\mathcal{X}$.
-Consequently, knowing that the column rank and the row rank of a square matrix coincide and that the rank of a nonsquare matrix is at most the minimum between the column rank and the row rank we have
-
-        \begin{align}
-            \text{Rank}\left( \boldsymbol{A}^{(n)} \right) &= I_{n}, \label{mtx1} \\
-            \text{Rank}\left( \left[ \mathcal{X} \right]_{(n)} \right) &\leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\}, \label{mtx2} \\
-            \text{Rank}\left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right) &= \prod_{m \neq n} I_{m}.
-\label{mxt3}
-        \end{align}
-
-        \paragraph{}Now the product between (\ref{mtx2}) and (\ref{mxt3}) it is a full-rank matrix projected onto the column space of the relevant matrices and its rank is defined as
-
-        \begin{align}
-            \text{Rank}\left( \left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right) \right) &\leq \text{min} \left\{ \prod_{m \neq n} I_{m}, \prod_{m \neq n} I_{m} \right\}, \\
-            \text{Rank}\left( \left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right) \right) &= \prod_{m \neq n} I_{m}.
-        \end{align}
-
-        \paragraph{}Therefore, the product between $\boldsymbol{A}^{(n)}$ and $\left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right) $ is projected onto the column space of these matrices and can be evaluate as
-
-        \begin{align}
-            \text{Rank}\left( \boldsymbol{A}^{(n)} \left[ \mathcal{X} \right]_{(n)} \left( \boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right) \right) &\leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\}, \\
-            \text{Rank}\left( \mathcal{Y} \right) &\leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\}.
-        \end{align}
-
-        \paragraph{}As consequence we have that the multilinear rank of tensor $\mathcal{Y}$ is limited by the multilinear rank of the core tensor meaning that both share the geometric structure\footnote{Only if the matrices $\boldsymbol{A}^{(n)} \in \mathbb{C}^{I_{n} \times I_{n}}$ are nonsingular.}
-
-        \begin{align}
-            \forall n \in \{1, \cdots, N\}, R_{n} = \text{Rank}\left( \left[ \mathcal{Y} \right]_{(n)} \right) = \text{Rank}\left( \left[ \mathcal{X} \right]_{(n)} \right).
-        \end{align}
-
-    \item
-
-        \begin{enumerate}
-
-            \item Proof $\mathcal{Y} = \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}$ that is indeed a projection:
-
-            \paragraph{}Since we have that the matrix $\boldsymbol{P}^{(n)}$ is idempotent and self-adjoint then $\left(\boldsymbol{P}^{(n)}\right)^2 = \boldsymbol{P}^{(n)}$ and $\left(\boldsymbol{P}^{(n)}\right)^{\text{H}} = \boldsymbol{P}^{(n)}$, respectively.
-To show that $\boldsymbol{P}^{(n)}$ is a projection of tensor $\mathcal{X}$ onto $\mathcal{Y}$ tensor subspace defined by $\mathcal{Y} = \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}$ we need to show that
-
-            \begin{align}
-                \left( \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} \right) \times_{n} \boldsymbol{P}^{(n)} &= \left( \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} \right), \\
-                \left< \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}, \mathcal{Y} \right> &= \left< \mathcal{X},  \mathcal{Y} \times_{n} \boldsymbol{P}^{(n)}\right>.  
-            \end{align}
-
-            \paragraph{}The first expression can be obtained if we develop the nth mode product by using the unfolding operation
-
-            \begin{align}
-                \left( \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} \right) \times_{n} \boldsymbol{P}^{(n)}, \\
-                \left( \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} \right) \times_{n} \boldsymbol{P}^{(n)}, \\
-                \boldsymbol{P}^{(n)} \left( \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} \right) = \left(\boldsymbol{P}^{(n)}\right)^2 \left[\mathcal{X}\right]_{(n)}, \\
-            \end{align}
-
-            and because we have $\left(\boldsymbol{P}^{(n)}\right)^2 = \boldsymbol{P}^{(n)}$ then
-
-            \begin{align}
-                \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} = \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}.
-            \end{align}
-
-            \paragraph{}Relatively to the nth mode product self-adjoint property we can start by writing
-
-            \begin{align}
-                \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} &= \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \\
-                \mathcal{Y} \times_{n} \left(\boldsymbol{P}^{(n)}\right)^{\text{H}} &= \left(\boldsymbol{P}^{(n)}\right)^{\text{H}} \left[\mathcal{Y}\right]_{(n)}, \\
-            \end{align}
-
-            \paragraph{} and starting from the inner-product expression we can write
-
-            \begin{align}
-                \left< \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}, \mathcal{Y} \right>, \\
-                \left< \mathcal{X} \times_{n} \boldsymbol{P}^{(n)}, \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} \right>, \\
-                \left< \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} \right>,
-            \end{align}
-
-            and as long as $\boldsymbol{P}^{(n)}$ has a self-adjoint
-
-            \begin{align}
-                \left< \left[\mathcal{X}\right]_{(n)}, \left( \boldsymbol{P}^{(n)} \right)^{\text{H}} \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} \right>, \\
-                \left< \left[\mathcal{X}\right]_{(n)}, \boldsymbol{P}^{(n)} \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} \right>,
-            \end{align}
-
-            and knowing that $\left[\mathcal{Y}\right]_{(n)} = \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}$
-
-            \begin{align}
-                \left< \left[\mathcal{X}\right]_{(n)}, \boldsymbol{P}^{(n)} \left[\mathcal{Y}\right]_{(n)} \right>,
-            \end{align}
-
-            and redoing the nth mode product leads to
-
-            \begin{align}
-                \left< \mathcal{X}, \mathcal{Y} \times_{n} \boldsymbol{P}^{(n)} \right>.
-            \end{align}
-
-            \item Proof the nonexpansiveness of $|| \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} ||_{\text{F}} = || \mathcal{X} ||_{\text{F}}$:
-
-            \paragraph{}We can start by writing the squared Frobenius norm with the inner product notation and then defining the self-adjoint of the projection
-
-            \begin{align}
-                || \mathcal{X} \times_{n} \boldsymbol{P}^{(n)} ||^{2}_{\text{F}} &= || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} ||^{2}_{\text{F}} , \\ || <\boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}} &= || < \left( \boldsymbol{P}^{(n)} \right)^{*} \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}}, \\
-                || < \boldsymbol{P}^{(n)} \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}} &= || < \left( \boldsymbol{P}^{(n)} \right)^{2} \left[\mathcal{X}\right]_{(n)}, \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}},
-            \end{align}
-
-            and since we already know that $\boldsymbol{P}^{(n)}$ is idempotent then
-
-            \begin{align}
-                || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} ||^{2}_{\text{F}} &= || < \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}}.
-\label{eq:03}
-            \end{align}
-
-            \paragraph{}Equation (\ref{eq:03}) is a well known expression from Linear Algebra and with this the tensor expression could be reduced to a regular matrix expression.
-To finish, we can apply the Cauchy-Schwarz inequality and
-
-            \begin{align}
-                || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} ||^{2}_{\text{F}} &= || < \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}, \left[\mathcal{X}\right]_{(n)}>||^{2}_{\text{F}}, \\
-                || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} ||^{2}_{\text{F}} &\leq || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)}||_{\text{F}} \hspace{.25cm} || \left[\mathcal{X}\right]_{(n)} ||_{\text{F}} , \\
-                || \boldsymbol{P}^{(n)} \left[\mathcal{X}\right]_{(n)} ||_{\text{F}} &\leq || \left[\mathcal{X}\right]_{(n)} ||_{\text{F}}.
-            \end{align}
-
-            \paragraph{}Thus, the nth-mode product is a non-expansive operation.
-
-        \end{enumerate}
-
-    \item From previous problems we know that the multilinear rank of $\mathcal{X} \in \mathbb{C}^{I_{1} \times \cdots \times I_{N}}$ is $(R_{1}, \cdots, R_{N})$ and that we can easily acquire an expression for it by analyzing the profile of the unfoldings of said tensor.
-Moreover we can define a multilinear transformation where tensor $\mathcal{X}$ acts as the core tensor.
-Thus, we define another tensor, let's call it $\mathcal{Y}$, where its nth mode unfolding can be written as
-
-        \begin{align}
-            \mathcal{Y} &= \mathcal{X} \times_{1} \boldsymbol{A}^{(1)} \times_{2} \cdots \times_{N} \boldsymbol{A}^{(N)} \in \mathbb{C}^{I_{1} \times ... \times I_{N}}, \\
-            \left[\mathcal{Y}\right]_{(n)} &= \boldsymbol{A}^{(n)} \left[\mathcal{X}\right]_{(n)} \left(\boldsymbol{A}^{(N)} \otimes \cdots \otimes \boldsymbol{A}^{(n+1)} \otimes \boldsymbol{A}^{(n-1)} \otimes \cdots \otimes \boldsymbol{A}^{(1)} \right)^{T} \in \mathbb{C}^{I_{n} \times \prod_{m \neq n} I_{m}}.
-\label{eq:02}
-        \end{align}
-
-        \paragraph{}From Equation (\ref{eq:02}) and with a similar procedure already developed in a previous problem we can obtain an expression for the multilinear rank of $\mathcal{Y}$ as
-
-        \begin{align}
-            \forall n \in \{1, \cdots, N\}, \text{Rank} \left( \left[\mathcal{Y}\right]_{(n)} \right) \leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\},
-        \end{align}
-
-        and as proofed before we know that tensors are objects with a well-defined geometry and that the multilinear rank is in fact a property of the tensor that is not lost when a multilinear transformation is applied\footnote{If the group of factor matrices are nonsingular.}.
-Thus, we can guarantee that the multilinear rank of the tensor $\mathcal{Y}$ will be the same as the one for the tensor $\mathcal{X}$
-
-        \begin{align}
-            \forall n \in \{1, \cdots, N\}, \text{Rank} \left( \left[\mathcal{X}\right]_{(n)} \right) \leq \text{min} \left\{ I_{n}, \prod_{m \neq n} I_{m} \right\},
-        \end{align}
-
-    \item In the context of multilinear transformation
-
-        \begin{enumerate}
-
-            \item Proof that the operation is linear in the transformed tensor:
-
-                \begin{align}
-                    (\alpha_{1} \mathcal{X}_{1} + \alpha_{2} \mathcal{X}_{2}) \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{N} \boldsymbol{A}^{(N)} \in \mathbb{C}^{I_{1} \times ... \times I_{N}}.
-                \end{align}
-
-                \paragraph{}Starting by applying the following property of the n-mode product we can reorder the expression in a usefully way
-
-                \begin{align}
-                    \mathcal{X} \times_{m} \boldsymbol{A}^{(m)} \times_{n} \boldsymbol{A}^{(n)} = \mathcal{X} \times_{n} \boldsymbol{A}^{(n)} \times_{m} \boldsymbol{A}^{(m)}. 
-                \end{align}
-
-                \paragraph{}The core of this demonstration is the fact that we can reduce the nth mode product to a regular product between matrices which is known to be a linear operation. Thus,
-
-                \begin{align}
-                    &(\alpha_{1} \mathcal{X}_{1} + \alpha_{2} \mathcal{X}_{2}) \times_{n} \boldsymbol{A}^{(n)} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)}, \\
-                    &\boldsymbol{A}^{(n)} \left( \alpha_{1} \left[\mathcal{X}_{1}\right]_{(n)} +  \alpha_{2} \left[\mathcal{X}_{2}\right]_{(n)} \right) \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)},
-                \end{align}
-
-                and now considering that the product between matrices is linear we have
-
-                \begin{align}
-                    \left(\alpha_{1} \boldsymbol{A}^{(n)} \left[\mathcal{X}_{1}\right]_{(n)}\right) \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)} + \\
-                    \left(\alpha_{2} \boldsymbol{A}^{(n)} \left[\mathcal{X}_{2}\right]_{(n)}\right)  \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)},
-                \end{align}
-
-                and finally redoing the nth mode product leads to
-
-                \begin{align}
-                    \alpha_{1} \mathcal{X}_{1} \times_{n} \boldsymbol{A}^{(n)} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)} + \\
-                    \alpha_{2} \mathcal{X}_{2} \times_{n} \boldsymbol{A}^{(n)} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)},
-                \end{align}
-
-            \item Proof that the operation is linear for each factor matrix:
-
-                \begin{align}
-                    \mathcal{X} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n} (\alpha_{1} \boldsymbol{Z}^{(n)}_{1} + \alpha_{2} \boldsymbol{Z}^{(n)}_{2}) \times_{n+1} \cdots \times_{N} \boldsymbol{A}^{(N)} \in \mathbb{C}^{I_{1} \times ...
-\times I_{N}}.
-                \end{align}
-
-                \paragraph{}In a similar view of the previous item we can start by reordering the n-mode product and explore the regular properties of the product between matrices
-
-                \begin{align*}
-                    \mathcal{X} \times_{n} (\alpha_{1} \boldsymbol{Z}^{(n)}_{1} + \alpha_{2} \boldsymbol{Z}^{(n)}_{2}) \times_{1} \boldsymbol{A}^{(1)} \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)} \in \mathbb{C}^{I_{1} \times ...
-\times I_{N}}, \\
-                    (\alpha_{1} \boldsymbol{Z}^{(n)}_{1} + \alpha_{2} \boldsymbol{Z}^{(n)}_{2}) \left[\mathcal{X}\right]_{(n)} \times_{1} \boldsymbol{A}^{(1)} \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)}.
-                \end{align*}
-
-                \paragraph{}Now applying the distribute property and redoing the nth mode product notation
-
-                \begin{align*}
-                    &\alpha_{1} \boldsymbol{Z}^{(n)}_{1} \left[\mathcal{X}\right]_{(n)} \times_{1} \boldsymbol{A}^{(1)}  \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)} + \\
-                    &\alpha_{2} \boldsymbol{Z}^{(n)}_{2} \left[\mathcal{X}\right]_{(n)} \times_{1} \boldsymbol{A}^{(1)} \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)}, \\
-                    &\alpha_{1} \mathcal{X} \times_{n} \boldsymbol{Z}^{(n)}_{1} \times_{1} \boldsymbol{A}^{(1)} \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)} + \\
-                    &\alpha_{2} \mathcal{X} \times_{n} \boldsymbol{Z}^{(n)}_{2} \times_{1} \boldsymbol{A}^{(1)} \cdots  \times_{n-1} \boldsymbol{A}^{(n-1)} \times_{n+1} \boldsymbol{A}^{(n+1)} \cdots \times_{N} \boldsymbol{A}^{(N)},
-                \end{align*}
-
-                and reordering the expression results the following expression
-
-                \begin{align*}
-                    &\alpha_{1} \mathcal{X}  \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n} \boldsymbol{Z}^{(n)}_{1} \cdots \times_{N} \boldsymbol{A}^{(N)} + \\
-                    &\alpha_{2} \mathcal{X}  \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{n} \boldsymbol{Z}^{(n)}_{2} \cdots \times_{N} \boldsymbol{A}^{(N)},
-                \end{align*}
-
-            \item Using the previous problems obtain an expression for:
-
-                \begin{align}
-                    \mathcal{X} = \boldsymbol{u}_{1} \circ \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1} + \boldsymbol{u}_{2} \circ \boldsymbol{v}_{2} \circ \boldsymbol{w}_{2} \rightarrow \mathcal{X} \times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C}.
-                \end{align}
-
-                \paragraph{}First, we can input the low-rank decomposition of tensor $\mathcal{X}$ into the multilinear transformation
-
-                \begin{align}
-                    \mathcal{X} &\times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C}, \\
-                    \left( \boldsymbol{u}_{1} \circ \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1} + \boldsymbol{u}_{2} \circ \boldsymbol{v}_{2} \circ \boldsymbol{w}_{2} \right) &\times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C},
-                \end{align}
-
-                and knowing that the nth mode product is a linear operation
-
-                \begin{align}
-                    \left( \boldsymbol{u}_{1} \circ \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1} \right) &\times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C} + \left( \boldsymbol{u}_{2} \circ \boldsymbol{v}_{2} \circ \boldsymbol{w}_{2} \right) \times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C},
-                \end{align}
-
-                considering that both terms have the same structure we can focus on only one and later apply the result to the other.
-Before we proceed we should define the unfolding of the subtensor formed by the outer product of $\mathcal{X}_{1} = \boldsymbol{u}_{1} \circ \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1}$ as\footnote{Since we are manipulating vectors the Khatri-Rao product can be simply reduced to the Kronecker product.}
-
-                \begin{align}
-                    \left[\mathcal{X}_{1}\right]_{(1)} = \boldsymbol{u}_{1} (\boldsymbol{v}_{1} \otimes \boldsymbol{w}_{1})^{\text{T}} \in \mathbb{C}^{I_{1} \times I_{2} I_{3}}, \\
-                    \left[\mathcal{X}_{1}\right]_{(2)} = \boldsymbol{v}_{1} (\boldsymbol{u}_{1} \otimes \boldsymbol{w}_{1})^{\text{T}} \in \mathbb{C}^{I_{2} \times I_{1} I_{3}}, \\
-                    \left[\mathcal{X}_{1}\right]_{(3)} = \boldsymbol{w}_{1} (\boldsymbol{u}_{1} \otimes \boldsymbol{v}_{1})^{\text{T}} \in \mathbb{C}^{I_{3} \times I_{1} I_{2}}.
-                \end{align}
-
-                \paragraph{}Now applying these expressions onto the multilinear transformation of the first subtensor as
-
-                \begin{align}
-                    \left( \boldsymbol{A} \left[\mathcal{X}_{1}\right]_{(1)} \right) \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C} = \left[ \boldsymbol{A}\boldsymbol{u}_{1} (\boldsymbol{v}_{1} \otimes \boldsymbol{w}_{1})^{\text{T}}  \right] \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C},
-                \end{align}
-
-                and by understanding that $\boldsymbol{A}\boldsymbol{u}_{1} \in \mathbb{C}^{I_{1} \times 1}$ is a vector we can redo the outer product by doing the folding operation, creating a new subtensor each time, and repeat the process for each factor matrix.
-By the end of this we reach the expression
-
-                \begin{align}
-                    \left( \boldsymbol{A} \boldsymbol{u}_{1} \circ \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1} \right) \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C}, \\
-                    \left( \boldsymbol{A} \boldsymbol{u}_{1} \circ \boldsymbol{B} \boldsymbol{v}_{1} \circ \boldsymbol{w}_{1} \right) \times_{3} \boldsymbol{C}, \\
-                    \left( \boldsymbol{A} \boldsymbol{u}_{1} \circ \boldsymbol{B} \boldsymbol{v}_{1} \circ \boldsymbol{C} \boldsymbol{w}_{1} \right) \in \mathbb{C}^{I_{1} \times I_{2} \times I_{3}}.
-                \end{align}
-
-                \paragraph{}Now we can apply the same process to the other subtensor defined as $\mathcal{X}_{2} = \boldsymbol{u}_{2} \circ \boldsymbol{v}_{2} \circ \boldsymbol{w}_{2}$ and sum the contributions of each one since the nth mode product is already known to be a linear operation
-
-                \begin{align}
-                    \mathcal{X} &\times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C} = \left( \boldsymbol{A} \boldsymbol{u}_{1} \circ \boldsymbol{B} \boldsymbol{v}_{1} \circ \boldsymbol{C} \boldsymbol{w}_{1} \right) + \left( \boldsymbol{A} \boldsymbol{u}_{2} \circ \boldsymbol{B} \boldsymbol{v}_{2} \circ \boldsymbol{C} \boldsymbol{w}_{2} \right) \in \mathbb{C}^{I_{1} \times I_{2} \times I_{3}}.
-                \end{align}
-
-                \paragraph{}Thus, by applying the nth mode product between a tensor and a factor matrix we are projecting the fibers of said tensor onto the column space of the corespondent factor matrix.
-        \end{enumerate}
-
-    \item In the context of High-Order Single Value Decomposition (HOSVD)
-
-        \begin{enumerate}
-
-            \item Show that, for any orthogonal projector $\boldsymbol{P}$ and any mode $\boldsymbol{n}$, we have
-
-                \begin{align}
-                    \left< \mathcal{X} \times_{n} \boldsymbol{P}, \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) \right> &= 0, \label{eq:04} \\
-                    || \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} &= || \mathcal{X} \times_{n} \boldsymbol{P} ||^{2}_{\text{F}} + ||  \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} \label{eq:05}.
-                \end{align}
-
-                \paragraph{}To obtain Equation (\ref{eq:04}) we can just reduce it to the matrix case by developing the nth mode product
-
-                \begin{align}
-                    \left< \mathcal{X} \times_{n} \boldsymbol{P}, \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) \right> &=\left< \boldsymbol{P} \left[\mathcal{X}\right]_{(n)}, (\boldsymbol{I} - \boldsymbol{P}) \left[\mathcal{X}\right]_{(n)} \right>,
-                \end{align}
-
-                but we know from Linear Algebra that the matrix $(\boldsymbol{I} - \boldsymbol{P})$ is the orthogonal complement of the projection $\boldsymbol{P}$ meaning that the inner product between $\boldsymbol{P} \left[\mathcal{X}\right]_{(n)}$ and $(\boldsymbol{I} - \boldsymbol{P}) \left[\mathcal{X}\right]_{(n)}$ will be zero.
-In sequence we can use this knowledge to develop the expression for $|| \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}}$ as
-
-                \begin{align*}
-                    || \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} &= || \mathcal{X} \times_{n} \boldsymbol{P} ||^{2}_{\text{F}} + ||  \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} -2 ||  \mathcal{X} \times_{n} \boldsymbol{P}  ||_{\text{F}} || \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||_{\text{F}},
-                \end{align*}
-
-                and we know that $||  \mathcal{X} \times_{n} \boldsymbol{P}  ||_{\text{F}} || \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||_{\text{F}} = \left< \mathcal{X} \times_{n} \boldsymbol{P}, \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) \right> = 0$ which leads to
-
-                \begin{align*}
-                    || \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} &= || \mathcal{X} \times_{n} \boldsymbol{P} ||^{2}_{\text{F}} + || \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} -2 \cdot 0, \\
-                    || \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}} &= || \mathcal{X} \times_{n} \boldsymbol{P} ||^{2}_{\text{F}} + || \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}}.
-                \end{align*}
-
-                \paragraph{}An interesting way to see this expression is by the Pythagorean theorem where $|| \mathcal{X} \times_{n} \boldsymbol{P} ||^{2}_{\text{F}}$ and $|| \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}}$ acts as the opposing sides to the hypotenuse $|| \mathcal{X} \times_{n} \boldsymbol{P} - \mathcal{X} \times_{n} (\boldsymbol{I} - \boldsymbol{P}) ||^{2}_{\text{F}}$.
-
-            \item
-
-            \item
-
-            \item
-
-        \end{enumerate}
+    \item Teste
 

### 2022-06-20 Seminar/codes/atlms.m
Seminar Update

@@ -1,0 +1,64 @@
+%% Alternating Tensor LMS Algorithm
+clc;
+close all;
+clear all;
+
+Nh = 5;
+Nv = 5;
+Kh = 10;
+Kv = 10;
+
+runs = 5;
+mu = 0.005;
+
+QAM = 2;
+snr = 30;
+var_noise = 1/(10^(snr/10));  
+
+buffer = Nh*Nv;
+Samples = 10000;
+mse = zeros(Samples,1);
+Kb = floor(Samples/(Kh + Kv));
+for rr = 1:runs
+    
+    weights_v = complex(randn(Nv,Samples),randn(Nv,Samples));
+    weights_h = complex(zeros(Nh,Samples),randn(Nh,Samples));
+    
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+   
+    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+    signal_x = signal_d + noise;
+    kh = 1;
+    kv = 1;
+    for kk = 1:(Kh + Kv):(Kb*(Kh + Kv)) - 2*(Kh + Kv)
+        for kh = kk:(kk+Kh-1)
+            xmtx = signal_x(kh:kh+buffer-1);
+            uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kh));
+            error = signal_d(kh) - (tensor.mtx_prod_kron(weights_v(:,kh),weights_h(:,kh))')*xmtx;
+            mu_norm = mu/(norm(uh,2)^2);
+            weights_h(:,kh+1) = weights_h(:,kh) + mu_norm*uh*conj(error); 
+            weights = tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh+1));
+            mse(kh,1) =  mse(kh,1) + abs(signal_d(kh) - weights'*xmtx).^2;
+        end
+        for kv = (kk+Kh):(kk+Kh+Kv-1)
+            xmtx = signal_x(kv+Kv:kv+buffer+Kv-1);
+            uv = (reshape(xmtx,[Nh Nv]).')*conj(weights_h(:,kv));
+            error = signal_d(kv) - (tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh+1))')*xmtx;
+            mu_norm = mu/(norm(uv,2)^2);
[…]

### 2022-06-20 Seminar/codes/gradient.m

@@ -1,86 +1,0 @@
-%% Deterministic Gradient Algorithm
-clc;
-close all;
-clear all;
-
-% Learning rate
-mi = 1e-3;
-% Filter order
-order = 2;
-% Number of samples
-Samples = 5000;
-% Defining the mse error and filter coeficients vectors.
-error = zeros(Samples,1);
-weights = zeros(order, Samples);
-
-%Wiener Solution
-wiener = [0.35;-0.15];
-
-% Defining the energy of the noise vector.
-SNR_dB = inf;
-SNR_li = 10^(SNR_dB/10);
-variance_noise = 1/SNR_li;
-noise = sqrt(variance_noise/2).*randn(Samples,1);
-
-% Generating the original signal.
-signal_d = randn(Samples,1);
-
-% Convolving the channel and the signal.
-Hz = [1 1.6];
-signal_x = filter(Hz,1,signal_d);
-
-% Generating the noisy received signal.
-signal_x = signal_x + noise;
-
-% Defining the autocorrelation matrix and the cross-correlation vector.
-Rx = [3.56, 1.60; 1.60, 3.56;];
-p = [1; 0;];
-
-% Obtaining the optimal wiener solution.
-wopt = inv(Rx)*p;
-
-% To prevent the missmatch between the filtered signal and the desired
-% signal. After some hours of debug I found out that the filtered signal
-% was a shifted version of the desired signal.
-signal_d = signal_d(order:end,1); 
-for ss = 1:(Samples - order - 1)
-    % Error between the desired signal and the filtered signal.
-    error(ss,1) = signal_d(ss) - weights(:,ss)'*signal_x(ss:ss+order-1);
-    % Recursive expression.
-    weights(:,ss+1) = weights(:,ss) - 2*mi*(Rx*weights(:,ss) - p);
-end
-
-% MSE Curve
-figure
-semilogy(1:Samples, error.^2,'-','color', [0.3010 0.7450 0.9330], "linewidth", 1, "markersize", 8);
-title('Deterministic Gradient Algorithm Behavior');
-xlabel('Iterations');
-ylabel('MSE');
-grid on;
-saveas(gcf,'gradient_mse.png')
-
-% Contour
-figure
-[W0, W1] = meshgrid (-1:0.01:1,-1:0.01:1);
-w0 = reshape(W0,[],1);
-w1 = reshape(W1,[],1);
[…]

### 2022-06-20 Seminar/codes/lms.m

@@ -1,84 +1,39 @@
-%% LMS Filter Implementation
+%% LMS Algorithm
 clc;
 close all;
 clear all;
 
-% Learning rate
-mi = 1e-3;
-% Filter order
-order = 2;
-% Number of samples
-Samples = 5000;
-% Defining the mse error and filter coeficients vectors.
-error = zeros(Samples,1);
-weights = zeros(order, Samples);
+runs = 5;
+mu = 0.005;
 
-%Wiener Solution
-wiener = [0.35;-0.15];
+QAM = 2;
+snr = 30;
+var_noise = 1/(10^(snr/10));     
 
-% Defining the energy of the noise vector.
-SNR_dB = inf;
-SNR_li = 10^(SNR_dB/10);
-variance_noise = 1/SNR_li;
-noise = sqrt(variance_noise/2).*randn(Samples,1);
-
-% Generating the original signal.
-signal_d = randn(Samples,1);
-
-% Convolving the channel and the signal.
-Hz = [1 1.6];
-signal_x = filter(Hz,1,signal_d);
-
-% Generating the noisy received signal.
-signal_x = signal_x + noise;
-
-% Defining the autocorrelation matrix and the cross-correlation vector.
-Rx = [3.56, 1.60; 1.60, 3.56;];
-p = [1; 0;];
-
-% To prevent the missmatch between the filtered signal and the desired
-% signal. After some hours of debug I found out that the filtered signal
-% was a shifted version of the desired signal.
-signal_d = signal_d(order:end,1); 
-for ss = 1:(Samples - order - 1)
-    % Error between the desired signal and the filtered signal.
-    error(ss) = signal_d(ss) - weights(:,ss)' * signal_x(ss:ss+order-1); 
-    % Recursive expression.
-    weights(:,ss+1) = weights(:,ss) + 2 * mi * error(ss) * signal_x(ss:ss+order-1);
+order = 10;
+Samples = 10000;
+mse = zeros(Samples,1);
+weights = complex(zeros(order, Samples),0);
+for rr = 1:runs
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+    signal_x = signal_d + noise;
[…]

### 2022-06-20 Seminar/codes/newton.m

@@ -1,87 +1,0 @@
-%% Newton Algorithm Implementation
-clc;
-close all;
-clear all;
-
-% Learning rate
-mi = 1e-1;
-% Filter order
-order = 2;
-% Number of samples
-Samples = 5000;
-% Defining the mse error and filter coeficients vectors.
-error = zeros(Samples,1);
-weights = zeros(order, Samples);
-
-%Wiener Solution
-wiener = [0.35;-0.15];
-
-% Defining the energy of the noise vector.
-SNR_dB = inf;
-SNR_li = 10^(SNR_dB/10);
-variance_noise = 1/SNR_li;
-noise = sqrt(variance_noise/2).*randn(Samples,1);
-
-% Generating the original signal.
-signal_d = randn(Samples,1);
-
-% Convolving the channel and the signal.
-Hz = [1 1.6];
-signal_x = filter(Hz,1,signal_d);
-
-% Generating the noisy received signal.
-signal_x = signal_x + noise;
-
-% Defining the autocorrelation matrix and the cross-correlation vector.
-Rx = [3.56, 1.60; 1.60, 3.56;];
-p = [1; 0;];
-
-% Obtaining the optimal wiener solution.
-wopt = inv(Rx)*p;
-
-% To prevent the missmatch between the filtered signal and the desired
-% signal. After some hours of debug I found out that the filtered signal
-% was a shifted version of the desired signal.
-signal_d = signal_d(order:end,1); 
-for ss = 1:(Samples - order - 1)
-    % Error between the desired signal and the filtered signal.
-    error(ss,1) = signal_d(ss) - weights(:,ss)'*signal_x(ss:ss+order-1);
-    % Recursive expression.
-    weights(:,ss+1) = weights(:,ss) - mi*(weights(:,ss) - wopt);
-end
-
-% MSE Curve
-figure
-semilogy(1:Samples, error.^2,'-','color', [0.3010 0.7450 0.9330], "linewidth", 1, "markersize", 8);
-title('Newton Algorithm Behavior');
-xlabel('Iterations');
-ylabel('MSE');
-grid on;
-saveas(gcf,'newton_mse.png')
-
-% Contour
-figure
-[W0, W1] = meshgrid (-1:0.01:1,-1:0.01:1);
-w0 = reshape(W0,[],1);
-w1 = reshape(W1,[],1);
-[aux,~] = size(w0);
-for i = 1:aux
[…]

### 2022-06-20 Seminar/codes/nlms.m

@@ -1,88 +1,40 @@
-%% NLMS Filter Implementation
+%% Normalized LMS Algorithm
 clc;
 close all;
 clear all;
 
-% Learning rate
-mi = 0.5;
-% Filter order
-order = 2;
-% Number of samples
-Samples = 5000;
-% Defining the mse error and filter coeficients vectors.
-error = zeros(Samples,1);
-weights = zeros(order, Samples);
+runs = 5;
+mu = 0.005;
 
-%Wiener Solution
-wiener = [0.35;-0.15];
+QAM = 2;
+snr = 30;
+var_noise = 1/(10^(snr/10));     
 
-% Defining the energy of the noise vector.
-SNR_dB = inf;
-SNR_li = 10^(SNR_dB/10);
-variance_noise = 1/SNR_li;
-noise = sqrt(variance_noise/2).*randn(Samples,1);
-
-% Generating the original signal.
-signal_d = randn(Samples,1);
-
-% Convolving the channel and the signal.
-Hz = [1 1.6];
-signal_x = filter(Hz,1,signal_d);
-
-% Generating the noisy received signal.
-signal_x = signal_x + noise;
-
-% Defining the autocorrelation matrix and the cross-correlation vector.
-Rx = [3.56, 1.60; 1.60, 3.56;];
-p = [1; 0;];
-
-% To prevent the missmatch between the filtered signal and the desired
-% signal. After some hours of debug I found out that the filtered signal
-% was a shifted version of the desired signal.
-signal_d = signal_d(order:end,1); 
-for ss = 1:(Samples - order - 1)
-    % Normalized learning rate.
-    mi_normalized = mi/(norm(signal_x));
-    % Error between the desired signal and the filtered signal.
-    error(ss) = signal_d(ss) - weights(:,ss)' * signal_x(ss:ss+order-1); 
-    % Recursive expression.
-    weights(:,ss+1) = weights(:,ss) +  2 * mi_normalized * error(ss) * signal_x(ss:ss+order-1);
+order = 10;
+Samples = 10000;
+mse = zeros(Samples,1);
+weights = complex(zeros(order, Samples),0);
+for rr = 1:runs
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
[…]

### 2022-06-20 Seminar/codes/tensor.m

@@ -1,0 +1,455 @@
+classdef tensor
+    methods(Static)
+%% Vectorize
+
+% This function computes the vec operator of a given matrix or tensor.   
+% Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+% Created: May 2022
+
+function Y = vec(X)
+    Y = reshape(X,[],1);
+end
+
+%% Hadamard Product
+
+% This function computes the Hadarmard Product of two given matrices.   
+% Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+% Created: January 2022
+
+function C = mtx_prod_had(A,B)
+    
+    [ia,ja] = size(A);
+    [ib,jb] = size(B);
+    
+    if (ia ~= ib) || (ja~=jb)
+        disp('Invalid Matrices!')
+        return;
+    else
+        C = A.*B;
+        %C = zeros(ia,ja);
+        %for i = 1:ia 
+            %for j = 1:ja
+                %C(i,j) = A(i,j)*B(i,j);
+            %end
+        %end
+    end
+end
+
+%% Kronecker Product
+
+% This function computes the Kronecker Product of two given matrices. 
+% Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+% Created: January 2022
+
+function C = mtx_prod_kron(A,B)
+    
+    [ia,ja] = size(A);
+    [ib,jb] = size(B);
+    
+    A = repelem(A,ib,jb);
+    B = repmat(B,[ia ja]);
+    C = A.*B;
+    
+end
+
+%% Khatri-Rao Product
+
+% This function computes the Khatri-Rao Product of two given matrices. 
+% Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+% Created: January 2022
+
+function C = mtx_prod_kr(A,B)
+    [ia,ja] = size(A);
+    [ib,jb] = size(B);
+    
+    if (ja~=jb)
+        disp('Invalid Matrices!')
+        return;
+    else
+        C = zeros(ia*ib,ja);
+        for j = 1:ja
+            C(:,j) = tensor.mtx_prod_kron(A(:,j),B(:,j));
+        end
+    end
+end
+
+%% Least-Squares Khatri-Rao Factorization (LSKRF)
+
+% This function computes the LSKRF of a given matrix.   
+% Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+% Created: February 2022
+
[…]

### 2022-06-20 Seminar/codes/tlms.m

@@ -1,0 +1,51 @@
+%% Tensor LMS Algorithm
+clc;
+close all;
+clear all;
+
+Nh = 5;
+Nv = 5;
+
+runs = 5;
+mu = 0.5;
+
+QAM = 2;
+snr = 30;
+var_noise = 1/(10^(snr/10));  
+
+buffer = Nh*Nv;
+Samples = 10000;
+mse = zeros(Samples,1);
+for rr = 1:runs
+    
+    weights_v = complex(randn(Nv,Samples),randn(Nv,Samples));
+    weights_h = complex(zeros(Nh,Samples),randn(Nh,Samples));
+    
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+   
+    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+    signal_x = signal_d + noise;
+    
+    for kk = 1:(Samples - buffer - 1)
+        xmtx = signal_x(kk:kk+buffer-1);
+        uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kk));
+        uv = (reshape(xmtx,[Nh Nv]).')*conj(weights_h(:,kk));
+        error = signal_d(kk) - (tensor.mtx_prod_kron(weights_v(:,kk),weights_h(:,kk))')*xmtx;
+        mu_norm = mu/(norm(uh,2)^2 + norm(uv,2)^2);
+        weights_h(:,kk+1) = weights_h(:,kk) + mu_norm*uh*conj(error); 
+        weights_v(:,kk+1) = weights_v(:,kk) + mu_norm*uv*conj(error); 
+        weights = tensor.mtx_prod_kron(weights_v(:,kk),weights_h(:,kk));
+        mse(kk,1) =  mse(kk,1) + abs(signal_d(kk) - weights'*xmtx).^2;
+    end
+end
+mse = mse/runs;
+
+% MSE Curve
+figure
+plot(1:Samples, 10*log10(mse),'-','color', [0.3010 0.7450 0.9330], "linewidth", 1, "markersize", 8);
+title('TLMS Behavior');
+xlabel('Samples');
+ylabel('MSE');
+grid on;
+saveas(gcf,'tlms_mse.png')

### 2022-06-21 Seminar/codes/L3Q6A.m
All the codes are ready

@@ -1,115 +1,0 @@
-clc;
-close all;
-clear all;
-
-%% Training Stage  
-% Learning rate
-mi = 0.4;
-gamma = 1e-3;
-% Filter order
-order = 15;
-% Number of samples
-Samples = 500;
-% Defining the mse error and filter coeficients vectors.
-error = zeros(Samples,1);
-weights = zeros(order, Samples);
-
-% Defining the energy of the noise vector.
-SNR = 30;
-QAM_train = 4;
-signal_d_train = randi([0,QAM_train - 1],[Samples 1]); % The same pilot for every pilot frame and block.
-signal_d_train = (1/sqrt(2)) * qammod(signal_d_train,QAM_train); % 4-QAM Pilot Signal.
-
-% Convolving the channel and the signal.
-Hz = [0.5 1.2 1.5 -1];
-signal_x_train = filter(Hz,1,signal_d_train);
-
-% Training noise
-snr = 10^(SNR/10);
-energy_symbol = mean(abs(signal_x_train(:)).^2); % Energy symbol pilot. 
-var_noise = energy_symbol .*  1/snr; % Variance of the noise.
-noise = sqrt(var_noise/2) * (randn(Samples,1) + 1i*randn(Samples,1));
-
-% Generating the noisy received signal.
-signal_x_train = signal_x_train + noise;
-
-for s = order:Samples
-    aux = signal_x_train(s:-1:s-order+1);
-    mi_normalized = mi/(gamma + norm(aux)^2);
-    error(s) = signal_d_train(s-order+1) - weights(:,s)'*aux;
-    % Recursive expression.
-    weights(:,s+1) = weights(:,s) + mi_normalized * conj(error(s)) * aux;
-end
-
-%% Transmission Stage 
-% Number of samples
-Samples = 5000;
-% Defining the mse error and filter coeficients vectors.
-error = zeros(Samples,1);
-weights = zeros(order, Samples);
-
-% Defining the energy of the noise vector.
-SNR = 30;
-QAM = 16;
-signal_d = randi([0,QAM - 1],[Samples 1]); % The same pilot for every pilot frame and block.
-signal_d = (1/sqrt(2)) * qammod(signal_d,QAM); % 4-QAM Pilot Signal.
-
-% Convolving the channel and the signal.
-Hz = [0.5 1.2 1.5 -1];
[…]

### 2022-06-21 Seminar/codes/L3Q6B.m

@@ -1,281 +1,0 @@
-clc;
-close all;
-clear all;
-
-% Learning rate
-mi = 1e-3;
-% Filter order
-order = 15;
-
-% If we want to evaluate the impact of the training size then we should
-% apply the same transmitted sequence to all the cases
-
-% Number of samples
-Samples = 5000;
-% Defining the energy of the noise vector.
-SNR = 30;
-QAM = 16;
-signal_d = randi([0,QAM - 1],[Samples 1]); % The same pilot for every pilot frame and block.
-signal_d = (1/sqrt(2)) * qammod(signal_d,QAM); % 4-QAM Pilot Signal.
-
-% Convolving the channel and the signal.
-Hz = [0.5 1.2 1.5 -1];
-signal_x = filter(Hz,1,signal_d);
-
-% Training noise
-snr = 10^(SNR/10);
-energy_symbol = mean(abs(signal_x(:)).^2); % Energy symbol pilot. 
-var_noise = energy_symbol .*  1/snr; % Variance of the noise.
-noise = sqrt(var_noise/2) * (randn(Samples,1) + 1i*randn(Samples,1));
-
-% Generating the noisy received signal.
-signal_x = signal_x + noise;
-
-%% Training with 50 Samples
-% Number of samples
-Samples = 50;
-% Defining the mse error and filter coeficients vectors.
-error = zeros(Samples,1);
-weights = zeros(order, Samples);
-
-% Defining the energy of the noise vector.
-SNR = 30;
-QAM_train = 4;
-signal_d_train = randi([0,QAM_train - 1],[Samples 1]); % The same pilot for every pilot frame and block.
-signal_d_train = (1/sqrt(2)) * qammod(signal_d_train,QAM_train); % 4-QAM Pilot Signal.
-
-% Convolving the channel and the signal.
-Hz = [0.5 1.2 1.5 -1];
-signal_x_train = filter(Hz,1,signal_d_train);
-
-% Training noise
-snr = 10^(SNR/10);
-energy_symbol = mean(abs(signal_x_train(:)).^2); % Energy symbol pilot. 
-var_noise = energy_symbol .*  1/snr; % Variance of the noise.
-noise = sqrt(var_noise/2) * (randn(Samples,1) + 1i*randn(Samples,1));
-
-% Generating the noisy received signal.
-signal_x_train = signal_x_train + noise;
-
-for s = order:Samples
[…]

### 2022-06-21 Seminar/codes/L3Q6C.m

@@ -1,115 +1,0 @@
-clc;
-close all;
-clear all;
-
-%% Training Stage  
-% Learning rate
-mi = 0.4;
-gamma = 1e-3;
-% Filter order
-order = 15;
-% Number of samples
-Samples = 500;
-% Defining the mse error and filter coeficients vectors.
-error = zeros(Samples,1);
-weights = zeros(order, Samples);
-
-% Defining the energy of the noise vector.
-SNR = 30;
-QAM_train = 4;
-signal_d_train = randi([0,QAM_train - 1],[Samples 1]); % The same pilot for every pilot frame and block.
-signal_d_train = (1/sqrt(2)) * qammod(signal_d_train,QAM_train); % 4-QAM Pilot Signal.
-
-% Convolving the channel and the signal.
-Hz = [0.5 1.2 1.5 -1];
-signal_x_train = filter(Hz,1,signal_d_train);
-
-% Training noise
-snr = 10^(SNR/10);
-energy_symbol = mean(abs(signal_x_train(:)).^2); % Energy symbol pilot. 
-var_noise = energy_symbol .*  1/snr; % Variance of the noise.
-noise = sqrt(var_noise/2) * (randn(Samples,1) + 1i*randn(Samples,1));
-
-% Generating the noisy received signal.
-signal_x_train = signal_x_train + noise;
-
-for s = order:Samples
-    aux = signal_x_train(s:-1:s-order+1);
-    mi_normalized = mi/(gamma + norm(aux)^2);
-    error(s) = signal_d_train(s-order+1) - weights(:,s)'*aux;
-    % Recursive expression.
-    weights(:,s+1) = weights(:,s) + mi_normalized * conj(error(s)) * aux;
-end
-
-%% Transmission Stage 
-% Number of samples
-Samples = 5000;
-% Defining the mse error and filter coeficients vectors.
-error = zeros(Samples,1);
-weights = zeros(order, Samples);
-
-% Defining the energy of the noise vector.
-SNR = 30;
-QAM = 256;
-signal_d = randi([0,QAM - 1],[Samples 1]); % The same pilot for every pilot frame and block.
-signal_d = (1/sqrt(2)) * qammod(signal_d,QAM); % 4-QAM Pilot Signal.
-
-% Convolving the channel and the signal.
-Hz = [0.5 1.2 1.5 -1];
[…]

### 2022-06-21 Seminar/codes/L3Q6D.m

@@ -1,345 +1,0 @@
-clc;
-close all;
-clear all;
-
-% Learning rate
-mi = 0.4;
-gamma = 1e-3;
-% Filter order
-order = 15;
-
-%% 4QAM
-QAM = 4;
-runs = 1000;
-snrs = [0 5 10 15 20 25 30];
-SER = zeros(length(snrs),1);
-for ii = 1:length(snrs)
-    for rr = 1:runs
-        %% Training Stage  
-        % Number of samples
-        Samples = 500;
-        % Defining the mse error and filter coeficients vectors.
-        error = zeros(Samples,1);
-        weights = zeros(order, Samples);
-
-        % Defining the energy of the noise vector.
-        QAM_train = 4;
-        signal_d_train = randi([0,QAM_train - 1],[Samples 1]); % The same pilot for every pilot frame and block.
-        signal_d_train = (1/sqrt(2)) * qammod(signal_d_train,QAM_train); % 4-QAM Pilot Signal.
-
-        % Convolving the channel and the signal.
-        Hz = [0.5 1.2 1.5 -1];
-        signal_x_train = filter(Hz,1,signal_d_train);
-
-        % Training noise
-        snr = 10^(inf/10);
-        energy_symbol = mean(abs(signal_x_train(:)).^2); % Energy symbol pilot. 
-        var_noise = energy_symbol .*  1/snr; % Variance of the noise.
-        noise = sqrt(var_noise/2) * (randn(Samples,1) + 1i*randn(Samples,1));
-
-        % Generating the noisy received signal.
-        signal_x_train = signal_x_train + noise;
-
-        for s = order:Samples
-            aux = signal_x_train(s:-1:s-order+1);
-            mi_normalized = mi/(gamma + norm(aux)^2);
-            error(s) = signal_d_train(s-order+1) - weights(:,s)'*aux;
-            % Recursive expression.
-            weights(:,s+1) = weights(:,s) + mi_normalized * conj(error(s)) * aux;
-        end
-
-        %% Transmission Stage 
-        % Number of samples
-        Samples = 5000;
-        % Defining the mse error and filter coeficients vectors.
-        error = zeros(Samples,1);
-        weights = zeros(order, Samples);
-
-        % Defining the energy of the noise vector.
-        signal_d = randi([0,QAM - 1],[Samples 1]); % The same pilot for every pilot frame and block.
[…]

### 2022-06-21 Seminar/codes/atlms.m

@@ -1,64 +1,0 @@
-%% Alternating Tensor LMS Algorithm
-clc;
-close all;
-clear all;
-
-Nh = 5;
-Nv = 5;
-Kh = 10;
-Kv = 10;
-
-runs = 5;
-mu = 0.005;
-
-QAM = 2;
-snr = 30;
-var_noise = 1/(10^(snr/10));  
-
-buffer = Nh*Nv;
-Samples = 10000;
-mse = zeros(Samples,1);
-Kb = floor(Samples/(Kh + Kv));
-for rr = 1:runs
-    
-    weights_v = complex(randn(Nv,Samples),randn(Nv,Samples));
-    weights_h = complex(zeros(Nh,Samples),randn(Nh,Samples));
-    
-    signal_d = randi([0,1],Samples,1);
-    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-   
-    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-    signal_x = signal_d + noise;
-    kh = 1;
-    kv = 1;
-    for kk = 1:(Kh + Kv):(Kb*(Kh + Kv)) - 2*(Kh + Kv)
-        for kh = kk:(kk+Kh-1)
-            xmtx = signal_x(kh:kh+buffer-1);
-            uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kh));
-            error = signal_d(kh) - (tensor.mtx_prod_kron(weights_v(:,kh),weights_h(:,kh))')*xmtx;
-            mu_norm = mu/(norm(uh,2)^2);
-            weights_h(:,kh+1) = weights_h(:,kh) + mu_norm*uh*conj(error); 
-            weights = tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh+1));
-            mse(kh,1) =  mse(kh,1) + abs(signal_d(kh) - weights'*xmtx).^2;
-        end
-        for kv = (kk+Kh):(kk+Kh+Kv-1)
-            xmtx = signal_x(kv+Kv:kv+buffer+Kv-1);
-            uv = (reshape(xmtx,[Nh Nv]).')*conj(weights_h(:,kv));
-            error = signal_d(kv) - (tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh+1))')*xmtx;
-            mu_norm = mu/(norm(uv,2)^2);
[…]

### 2022-06-21 Seminar/codes/atlms_mse.m

@@ -1,0 +1,223 @@
+%% Alternating Tensor LMS Algorithm
+clc;
+close all;
+clear all;
+
+% System parameters
+Nh = 5;
+Nv = 5;
+Kh = 3;
+Kv = 3;
+QAM = 2;
+runs = 1000;
+buffer = Nh*Nv;
+Samples = 15000;
+
+% Noise energy
+snr = 30;
+var_noise = 1/(10^(snr/10));  
+
+%% 0.1 Learning Step
+mu = 0.1;
+
+% Monter Carlo simulations
+mse = zeros(Samples,1);
+Kb = floor(Samples/(Kh + Kv));
+for rr = 1:runs
+    % Filter weights
+    weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
+    weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));
+    
+    % M-QAM source signal
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+    % Adding noise to the M-QAM source signal
+    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+    signal_x = signal_d + noise;
+    kh = 1;
+    kv = 1;
+    % ATLMS algorithm
+    for kk = 1:(Kh + Kv):(Kb*(Kh + Kv)) - 5*(Kh + Kv)
+        for kh = kk:(kk+Kh-1)
+            weights_v(:,kh+1) = weights_v(:,kh);
+            xmtx = signal_x(kh:kh+buffer-1);
+            uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kv));
+            error = signal_d(kh) - (tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh))')*xmtx;
+            mu_norm = mu/(norm(uh,2)^2);
+            weights_h(:,kh+1) = weights_h(:,kh) + mu_norm*uh*conj(error); 
+            weights = tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh));
+            mse(kh,1) =  mse(kh,1) + abs(signal_d(kh) - weights'*xmtx).^2;
+        end
+        for kv = (kk+Kh):(kk+Kh+Kv-1)
+            weights_h(:,kv+1) = weights_h(:,kv);
+            xmtx = signal_x(kv:kv+buffer-1);
[…]

### 2022-06-21 Seminar/codes/atlms_sampling.m

@@ -1,0 +1,243 @@
+%% Alternating Tensor LMS Algorithm Sampling and Time 
+clc;
+close all;
+clear all;
+
+% System parameters
+Nh = 5;
+Nv = 5;
+QAM = 2;
+runs = 1000;
+buffer = Nh*Nv;
+Samples = 15000;
+
+% Noise energy
+snr = 30;
+var_noise = 1/(10^(snr/10));  
+
+%% ATLMS with learning step 0.5 and Kh = Kv = 50
+mu = 0.5;
+Kh = 50;
+Kv = 50;
+
+% Monter Carlo simulations
+mse = zeros(Samples,1);
+Kb = floor(Samples/(Kh + Kv));
+tic();
+for rr = 1:runs
+    % Filter weights
+    weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
+    weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));
+    
+    % M-QAM source signal
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+    % Adding noise to the M-QAM source signal
+    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+    signal_x = signal_d + noise;
+    kh = 1;
+    kv = 1;
+    % ATLMS algorithm
+    for kk = 1:(Kh + Kv):(Kb*(Kh + Kv)) - 5*(Kh + Kv)
+        for kh = kk:(kk+Kh-1)
+            weights_v(:,kh+1) = weights_v(:,kh);
+            xmtx = signal_x(kh:kh+buffer-1);
+            uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kv));
+            error = signal_d(kh) - (tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh))')*xmtx;
+            mu_norm = mu/(norm(uh,2)^2);
+            weights_h(:,kh+1) = weights_h(:,kh) + mu_norm*uh*conj(error); 
+            weights = tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh));
+            mse(kh,1) =  mse(kh,1) + abs(signal_d(kh) - weights'*xmtx).^2;
+        end
+        for kv = (kk+Kh):(kk+Kh+Kv-1)
+            weights_h(:,kv+1) = weights_h(:,kv);
[…]

### 2022-06-21 Seminar/codes/generate_curves.m

@@ -1,0 +1,31 @@
+% MSE curves
+clc;
+close all;
+clear all;
+atlms_mse;
+clc;
+close all;
+clear all;
+tlms_mse;
+lms_mse;
+clc;
+close all;
+clear all;
+nlms_mse;
+% ATLMS sampling and time curves
+clc;
+close all;
+clear all;
+atlms_sampling;
+% Modulation curves
+clc;
+close all;
+clear all;
+modulation;
+% SER curves for all algorithms
+clc;
+close all;
+clear all;
+symbol_error_rate;
+
+

### 2022-06-21 Seminar/codes/lms.m

@@ -1,39 +1,0 @@
-%% LMS Algorithm
-clc;
-close all;
-clear all;
-
-runs = 5;
-mu = 0.005;
-
-QAM = 2;
-snr = 30;
-var_noise = 1/(10^(snr/10));     
-
-order = 10;
-Samples = 10000;
-mse = zeros(Samples,1);
-weights = complex(zeros(order, Samples),0);
-for rr = 1:runs
-    signal_d = randi([0,1],Samples,1);
-    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-    signal_x = signal_d + noise;
-    for kk = 1:(Samples - order - 1)
-       % Error between the desired signal and the filtered signal.
-        error = signal_d(kk) - weights(:,kk)' * signal_x(kk:kk+order-1); 
-        % Recursive expression.
-        weights(:,kk+1) = weights(:,kk) + 2 * mu * error * signal_x(kk:kk+order-1);
-        mse(kk,1) =  mse(kk,1) + abs(signal_d(kk) - weights(:,kk+1)'*signal_x(kk:kk+order-1)).^2;
-    end
-end
-mse = mse/runs;
-
-% MSE Curve
-figure
-plot(1:Samples, 10*log10(mse),'-','color', [0.3010 0.7450 0.9330], "linewidth", 1, "markersize", 8);
-title('LMS Behavior');
-xlabel('Samples');
-ylabel('MSE');
-grid on;
-saveas(gcf,'lms_mse.png')

### 2022-06-21 Seminar/codes/lms_mse.m

@@ -1,0 +1,151 @@
+%% LMS Algorithm
+clc;
+close all;
+clear all;
+
+% System parameters
+QAM = 2;
+runs = 1000;
+order = 1;
+Samples = 15000;
+
+% Noise energy
+snr = 30;
+var_noise = 1/(10^(snr/10));     
+
+%% 0.1 Learning Step
+mu = 0.1;
+
+% Monter Carlo simulations
+mse = zeros(Samples,1);
+for rr = 1:runs
+    % Filter weights
+    weights = complex(zeros(order, Samples),0);
+    
+    % M-QAM source signal
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+    
+    % Adding noise to the M-QAM source signal
+    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+    signal_x = signal_d + noise;
+    
+    % LMS algorithm
+    for kk = 1:(Samples - order - 1)
+        % Error between the desired signal and the filtered signal.
+        error = signal_d(kk) - weights(:,kk)' * signal_x(kk:kk+order-1); 
+        % Recursive expression.
+        weights(:,kk+1) = weights(:,kk) + 2 * mu * error * signal_x(kk:kk+order-1);
+        mse(kk,1) =  mse(kk,1) + abs(signal_d(kk) - weights(:,kk+1)'*signal_x(kk:kk+order-1)).^2;
+    end
+end
+mse = mse/runs;
+
+% MSE Curve
+figure
+txt = ['\mu = 0.1'];
+plot(1:Samples, 10*log10(mse),'-','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+hold on;
+
+%% 0.5 Learning Step
+mu = 0.5;
+
+% Monter Carlo simulations
+mse = zeros(Samples,1);
+for rr = 1:runs
+    % Filter weights
+    weights = complex(zeros(order, Samples),0);
+    
+    % M-QAM source signal
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+    
+    % Adding noise to the M-QAM source signal
+    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+    signal_x = signal_d + noise;
+    
+    % LMS algorithm
[…]

### 2022-06-21 Seminar/codes/modulation.m

@@ -1,0 +1,336 @@
+%% Symbol Error Rate (SER) vs. SNR for different Modulations
+clc;
+close all;
+clear all;
+
+% System parameters
+Nh = 5;
+Nv = 5;
+Kh = 5;
+Kv = 5;
+
+mu = 0.1;
+runs = 1;
+buffer = Nh*Nv;
+Samples = 15000;
+
+% SNR vector
+SNR = [0 5 10 15 20 25 30];
+
+%% ATLMS SER algorithm for 2-QAM
+QAM = 2;
+
+% Monter Carlo simulations
+ser = zeros(length(SNR),1);
+Kb = floor(Samples/(Kh + Kv));
+for ss = 1:length(SNR)
+    ss
+    for rr = 1:runs
+        rr
+        % Filter weights
+        weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
+        weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));
+
+        % M-QAM source signal
+        signal_d = randi([0,1],Samples,1);
+        signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+        % Adding noise to the M-QAM source signal
+        var_noise = 1/(10^(SNR(ss)/10));  
+        noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+        signal_x = signal_d + noise;
+        kh = 1;
+        kv = 1;
+        % ATLMS algorithm
+        for kk = 1:(Kh + Kv):(Kb*(Kh + Kv)) - 5*(Kh + Kv)
+            for kh = kk:(kk+Kh-1)
+                weights_v(:,kh+1) = weights_v(:,kh);
+                xmtx = signal_x(kh:kh+buffer-1);
+                uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kv));
+                error = signal_d(kh) - (tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh))')*xmtx;
+                mu_norm = mu/(norm(uh,2)^2);
+                weights_h(:,kh+1) = weights_h(:,kh) + mu_norm*uh*conj(error); 
+                weights = tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh));
+                if kh>250
+                    ser(ss,1) =  ser(ss,1) + (qamdemod(signal_d(kh),QAM)~=qamdemod(weights'*xmtx,QAM));
+                end
+            end
[…]

### 2022-06-21 Seminar/codes/nlms.m

@@ -1,40 +1,0 @@
-%% Normalized LMS Algorithm
-clc;
-close all;
-clear all;
-
-runs = 5;
-mu = 0.005;
-
-QAM = 2;
-snr = 30;
-var_noise = 1/(10^(snr/10));     
-
-order = 10;
-Samples = 10000;
-mse = zeros(Samples,1);
-weights = complex(zeros(order, Samples),0);
-for rr = 1:runs
-    signal_d = randi([0,1],Samples,1);
-    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-    signal_x = signal_d + noise;
-    for kk = 1:(Samples - order - 1)
-        mu_normalized = mu/(norm(signal_x(kk:kk+order-1)));
-       % Error between the desired signal and the filtered signal.
-        error(kk) = signal_d(kk) - weights(:,kk)' * signal_x(kk:kk+order-1); 
-        % Recursive expression.
-        weights(:,kk+1) = weights(:,kk) + mu_normalized * error(kk) * signal_x(kk:kk+order-1);
-        mse(kk,1) =  mse(kk,1) + abs(signal_d(kk) - weights(:,kk+1)'*signal_x(kk:kk+order-1)).^2;
-    end
-end
-mse = mse/runs;
-
-% MSE Curve
-figure
-plot(1:Samples, 10*log10(mse),'-','color', [0.3010 0.7450 0.9330], "linewidth", 1, "markersize", 8);
-title('NLMS Behavior');
-xlabel('Samples');
-ylabel('MSE');
-grid on;
-saveas(gcf,'nlms_mse.png')

### 2022-06-21 Seminar/codes/nlms_mse.m

@@ -1,0 +1,155 @@
+%% Normalized LMS Algorithm
+clc;
+close all;
+clear all;
+
+% System parameters
+QAM = 2;
+runs = 1000;
+order = 1;
+Samples = 15000;
+
+% Noise energy
+snr = 30;
+var_noise = 1/(10^(snr/10));   
+
+%% 0.1 Learning Step
+mu = 0.1;
+
+% Monter Carlo simulations
+mse = zeros(Samples,1);
+for rr = 1:runs
+    % Filter weights
+    weights = complex(zeros(order, Samples),0);
+    
+    % M-QAM source signal
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+    
+    % Adding noise to the M-QAM source signal
+    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+    signal_x = signal_d + noise;
+    
+    % NLMS algorithm
+    for kk = 1:(Samples - order - 1)
+        mu_normalized = mu/(norm(signal_x(kk:kk+order-1)));
+       % Error between the desired signal and the filtered signal.
+        error(kk) = signal_d(kk) - weights(:,kk)' * signal_x(kk:kk+order-1); 
+        % Recursive expression.
+        weights(:,kk+1) = weights(:,kk) + mu_normalized * error(kk) * signal_x(kk:kk+order-1);
+        mse(kk,1) =  mse(kk,1) + abs(signal_d(kk) - weights(:,kk+1)'*signal_x(kk:kk+order-1)).^2;
+    end
+end
+mse = mse/runs;
+
+% MSE Curve
+figure
+txt = ['\mu = 0.1'];
+plot(1:Samples, 10*log10(mse),'-','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+hold on;
+
+%% 0.5 Learning Step
+mu = 0.5;
+
+% Monter Carlo simulations
+mse = zeros(Samples,1);
+for rr = 1:runs
+    % Filter weights
+    weights = complex(zeros(order, Samples),0);
+    
+    % M-QAM source signal
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+    
+    % Adding noise to the M-QAM source signal
+    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
[…]

### 2022-06-21 Seminar/codes/symbol_error_rate.m

@@ -1,0 +1,202 @@
+%% Symbol Error Rate (SER) vs. SNR for different filter algorithms
+clc;
+close all;
+clear all;
+
+% System parameters
+Nh = 5;
+Nv = 5;
+Kh = 5;
+Kv = 5;
+order = 10;
+
+QAM = 2;
+mu = 0.1;
+runs = 5000;
+buffer = Nh*Nv;
+Samples = 10000;
+
+% SNR vector
+SNR = [0 5 10 15 20 25 30];
+
+%% ATLMS SER
+
+% Monter Carlo simulations
+ser = zeros(length(SNR),1);
+Kb = floor(Samples/(Kh + Kv));
+for ss = 1:length(SNR)
+    ss
+    for rr = 1:runs
+        rr
+        % Filter weights
+        weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
+        weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));
+
+        % M-QAM source signal
+        signal_d = randi([0,1],Samples,1);
+        signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+        % Adding noise to the M-QAM source signal
+        var_noise = 1/(10^(SNR(ss)/10));  
+        noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+        signal_x = signal_d + noise;
+        kh = 1;
+        kv = 1;
+        % ATLMS algorithm
+        for kk = 1:(Kh + Kv):(Kb*(Kh + Kv)) - 5*(Kh + Kv)
+            for kh = kk:(kk+Kh-1)
+                weights_v(:,kh+1) = weights_v(:,kh);
+                xmtx = signal_x(kh:kh+buffer-1);
+                uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kv));
+                error = signal_d(kh) - (tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh))')*xmtx;
+                mu_norm = mu/(norm(uh,2)^2);
+                weights_h(:,kh+1) = weights_h(:,kh) + mu_norm*uh*conj(error); 
+                weights = tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh));
+                if kh>250
+                    ser(ss,1) =  ser(ss,1) + (qamdemod(signal_d(kh),QAM)~=qamdemod(weights'*xmtx,QAM));
+                end
[…]

### 2022-06-21 Seminar/codes/tlms.m

@@ -1,51 +1,0 @@
-%% Tensor LMS Algorithm
-clc;
-close all;
-clear all;
-
-Nh = 5;
-Nv = 5;
-
-runs = 5;
-mu = 0.5;
-
-QAM = 2;
-snr = 30;
-var_noise = 1/(10^(snr/10));  
-
-buffer = Nh*Nv;
-Samples = 10000;
-mse = zeros(Samples,1);
-for rr = 1:runs
-    
-    weights_v = complex(randn(Nv,Samples),randn(Nv,Samples));
-    weights_h = complex(zeros(Nh,Samples),randn(Nh,Samples));
-    
-    signal_d = randi([0,1],Samples,1);
-    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-   
-    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-    signal_x = signal_d + noise;
-    
-    for kk = 1:(Samples - buffer - 1)
-        xmtx = signal_x(kk:kk+buffer-1);
-        uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kk));
-        uv = (reshape(xmtx,[Nh Nv]).')*conj(weights_h(:,kk));
-        error = signal_d(kk) - (tensor.mtx_prod_kron(weights_v(:,kk),weights_h(:,kk))')*xmtx;
-        mu_norm = mu/(norm(uh,2)^2 + norm(uv,2)^2);
-        weights_h(:,kk+1) = weights_h(:,kk) + mu_norm*uh*conj(error); 
-        weights_v(:,kk+1) = weights_v(:,kk) + mu_norm*uv*conj(error); 
-        weights = tensor.mtx_prod_kron(weights_v(:,kk),weights_h(:,kk));
-        mse(kk,1) =  mse(kk,1) + abs(signal_d(kk) - weights'*xmtx).^2;
-    end
-end
-mse = mse/runs;
-
-% MSE Curve
-figure
-plot(1:Samples, 10*log10(mse),'-','color', [0.3010 0.7450 0.9330], "linewidth", 1, "markersize", 8);
-title('TLMS Behavior');
-xlabel('Samples');
-ylabel('MSE');
-grid on;
-saveas(gcf,'tlms_mse.png')

### 2022-06-21 Seminar/codes/tlms_mse.m

@@ -1,0 +1,170 @@
+%% Tensor LMS Algorithm
+clc;
+close all;
+clear all;
+
+% System parameters
+Nh = 5;
+Nv = 5;
+QAM = 2;
+runs = 1000;
+buffer = Nh*Nv;
+Samples = 15000;
+
+% Noise energy
+snr = 30;
+var_noise = 1/(10^(snr/10));  
+
+%% 0.1 Learning Step
+mu = 0.1;
+
+% Monter Carlo simulations
+mse = zeros(Samples,1);
+for rr = 1:runs
+    % Filter weights
+    weights_v = complex(randn(Nv,Samples),randn(Nv,Samples));
+    weights_h = complex(randn(Nh,Samples),randn(Nh,Samples));
+    
+    % M-QAM source signal
+    signal_d = randi([0,1],Samples,1);
+    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
+   
+    % Adding noise to the M-QAM source signal
+    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
+    signal_x = signal_d + noise;
+    
+    % TLMS algorithm
+    for kk = 1:(Samples - buffer - 1)
+        xmtx = signal_x(kk:kk+buffer-1);
+        uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kk));
+        uv = (reshape(xmtx,[Nh Nv]).')*conj(weights_h(:,kk));
+        error = signal_d(kk) - (tensor.mtx_prod_kron(weights_v(:,kk),weights_h(:,kk))')*xmtx;
+        mu_norm = mu/(norm(uh,2)^2 + norm(uv,2)^2);
+        weights_h(:,kk+1) = weights_h(:,kk) + mu_norm*uh*conj(error); 
+        weights_v(:,kk+1) = weights_v(:,kk) + mu_norm*uv*conj(error); 
+        weights = tensor.mtx_prod_kron(weights_v(:,kk),weights_h(:,kk));
+        mse(kk,1) =  mse(kk,1) + abs(signal_d(kk) - weights'*xmtx).^2;
+    end
+end
+mse = mse/runs;
+
+% MSE Curve
+figure
+txt = ['\mu = 0.1'];
+plot(1:Samples, 10*log10(mse),'-','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+hold on;
+
+%% 0.5 Learning Step
+mu = 0.5;
[…]

### 2022-06-22 MATLAB/tensor.m
TTSVD parcialy implemented

@@ -1,5 +1,6 @@
 classdef tensor
     methods(Static)
+%addpath("~/MATLAB/tensorlab")
 %% Vectorize
 
 % This function computes the vec operator of a given matrix or tensor.   
@@ -71,6 +72,23 @@ function C = mtx_prod_kr(A,B)
             C(:,j) = tensor.mtx_prod_kron(A(:,j),B(:,j));
         end
     end
+end
+
+%% Tensor Kronecker Product
+
+% This function computes the Tensor Kronecker Product of two given tensors. 
+% Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+% Created: January 2022
+
+function C = ten_prod_kron(A,B)
+    
+    aux1 = num2cell([size(A)]);
+    aux2 = num2cell([size(B)]);
+
+    A = repelem(A,aux2{:});
+    B = repmat(B,aux1{:});
+    C = A.*B;
+    
 end
 
 %% Least-Squares Khatri-Rao Factorization (LSKRF)
@@ -450,6 +468,41 @@ function [Ahat,Bhat,Chat,error] = ALS(X,R)
         end
     end
 end
-    
+
+%% Tensor Train Single Value Decomposition (TT-SVD)
+
+% This function computes the TT-SVD of a fourth order tensor but can be extended.   
+% Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+% Created: June 2022
+
+function [G] = TTSVD(X,Ranks)
+    X_size = size(X);
+    % Step 1
+    X1 = tensor.unfold(X,1);
+    [U1,S1,V1] = svd(X1,'econ');
+    G1 = U1*sqrt(S1);
+    G1 = G1(:,1:Ranks(1));
+    G{1} = G1;
+    % Step 2
+    V1 = sqrt(S1)*V1';
+    V1 = V1(1:Ranks(1),:);
+    X2 = reshape(V1,[Ranks(1)*X_size(2) X_size(3)*X_size(4)]);
+    [U2,S2,V2] = svd(X2,'econ');
+    G2 = U2*sqrt(S2);
+    G2 = G2(:,1:Ranks(2));
+    G{2} = reshape(G2, [Ranks(1) X_size(2) Ranks(2)]);
+    % Step 3
+    V2 = sqrt(S2)*V2';
[…]

### 2022-06-22 Seminar/codes/atlms_mse.m

@@ -9,7 +9,7 @@ Nv = 5;
 Kh = 3;
 Kv = 3;
 QAM = 2;
-runs = 1000;
+runs = 2500;
 buffer = Nh*Nv;
 Samples = 15000;
 
@@ -24,6 +24,7 @@ mu = 0.1;
 mse = zeros(Samples,1);
 Kb = floor(Samples/(Kh + Kv));
 for rr = 1:runs
+	rr
     % Filter weights
     weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
     weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));

### 2022-06-22 Seminar/codes/atlms_sampling.m

@@ -7,7 +7,7 @@ clear all;
 Nh = 5;
 Nv = 5;
 QAM = 2;
-runs = 1000;
+runs = 2500;
 buffer = Nh*Nv;
 Samples = 15000;
 
@@ -25,6 +25,7 @@ mse = zeros(Samples,1);
 Kb = floor(Samples/(Kh + Kv));
 tic();
 for rr = 1:runs
+	rr
     % Filter weights
     weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
     weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));

### 2022-06-22 Seminar/codes/generate_curves.m

@@ -7,6 +7,9 @@ clc;
 close all;
 clear all;
 tlms_mse;
+clc;
+close all;
+clear all;
 lms_mse;
 clc;
 close all;

### 2022-06-22 Seminar/codes/modulation.m

@@ -6,16 +6,16 @@ clear all;
 % System parameters
 Nh = 5;
 Nv = 5;
-Kh = 5;
-Kv = 5;
+Kh = 10;
+Kv = 10;
 
 mu = 0.1;
-runs = 1;
+runs = 1000;
 buffer = Nh*Nv;
 Samples = 15000;
 
 % SNR vector
-SNR = [0 5 10 15 20 25 30];
+SNR = [0 10 20 30];
 
 %% ATLMS SER algorithm for 2-QAM
 QAM = 2;
@@ -71,15 +71,16 @@ for ss = 1:length(SNR)
 end
 ser = ser/(runs*Samples);
 
-%% ATLMS SER algorithm for 8-QAM
-QAM = 8;
-
 % SER Curve
 figure
 txt = ['ATLMS algorithm for 2-QAM'];
 semilogy(SNR, 10*log10(ser),'-','color', [0.3010 0.7450 0.9330], "linewidth", 3, "markersize", 8, "DisplayName", txt);
 hold on;
 
+%% ATLMS SER algorithm for 4-QAM
+QAM = 4;
+
+
 % Monter Carlo simulations
 ser = zeros(length(SNR),1);
 Kb = floor(Samples/(Kh + Kv));
@@ -131,66 +132,8 @@ for ss = 1:length(SNR)
 end
 ser = ser/(runs*Samples);
 
-txt = ['ATLMS algorithm for 8-QAM'];
+txt = ['ATLMS algorithm for 4-QAM'];
 semilogy(SNR, 10*log10(ser),'-','color', [0.4660 0.6740 0.1880], "linewidth", 3, "markersize", 8, "DisplayName", txt);
-hold on;
-
-%% ATLMS SER algorithm for 16-QAM
-QAM = 16;
-
-% Monter Carlo simulations
-ser = zeros(length(SNR),1);
-Kb = floor(Samples/(Kh + Kv));
-for ss = 1:length(SNR)
-    ss
-    for rr = 1:runs
-        rr
-        % Filter weights
-        weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
-        weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));
-
-        % M-QAM source signal
-        signal_d = randi([0,1],Samples,1);
-        signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-        % Adding noise to the M-QAM source signal
[…]

### 2022-06-22 Seminar/codes/nlms_mse.m

@@ -5,7 +5,7 @@ clear all;
 
 % System parameters
 QAM = 2;
-runs = 1000;
+runs = 2500;
 order = 1;
 Samples = 15000;
 
@@ -19,6 +19,7 @@ mu = 0.1;
 % Monter Carlo simulations
 mse = zeros(Samples,1);
 for rr = 1:runs
+	rr
     % Filter weights
     weights = complex(zeros(order, Samples),0);
     

### 2022-06-22 Seminar/codes/symbol_error_rate.m

@@ -6,13 +6,13 @@ clear all;
 % System parameters
 Nh = 5;
 Nv = 5;
-Kh = 5;
-Kv = 5;
-order = 10;
+Kh = 10;
+Kv = 10;
+order = 1;
 
 QAM = 2;
 mu = 0.1;
-runs = 5000;
+runs = 100;
 buffer = Nh*Nv;
 Samples = 10000;
 
@@ -51,7 +51,7 @@ for ss = 1:length(SNR)
                 mu_norm = mu/(norm(uh,2)^2);
                 weights_h(:,kh+1) = weights_h(:,kh) + mu_norm*uh*conj(error); 
                 weights = tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh));
-                if kh>250
+                if kh>100
                     ser(ss,1) =  ser(ss,1) + (qamdemod(signal_d(kh),QAM)~=qamdemod(weights'*xmtx,QAM));
                 end
             end
@@ -63,7 +63,7 @@ for ss = 1:length(SNR)
                 mu_norm = mu/(norm(uv,2)^2);
                 weights_v(:,kv+1) = weights_v(:,kv) + mu_norm*uv*conj(error); 
                 weights = tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh+1));
-                if kv>250
+                if kv>100
                     ser(ss,1) =  ser(ss,1) + (qamdemod(signal_d(kv),QAM)~=qamdemod(weights'*xmtx,QAM));
                 end
             end
@@ -107,7 +107,7 @@ for ss = 1:length(SNR)
             weights_h(:,kk+1) = weights_h(:,kk) + mu_norm*uh*conj(error); 
             weights_v(:,kk+1) = weights_v(:,kk) + mu_norm*uv*conj(error); 
             weights = tensor.mtx_prod_kron(weights_v(:,kk),weights_h(:,kk));
-            if kk>250
+            if kk>100
                 ser(ss,1) =  ser(ss,1) + (qamdemod(signal_d(kk),QAM)~=qamdemod(weights'*xmtx,QAM));
             end
         end
@@ -117,83 +117,8 @@ ser = ser/(runs*Samples);
 
 txt = ['TLMS algorithm'];
 semilogy(SNR, 10*log10(ser),'-','color', [0.8500 0.3250 0.0980], "linewidth", 3, "markersize", 8, "DisplayName", txt);
-hold on;
-
[…]

### 2022-06-22 Seminar/codes/tensor.m

@@ -73,6 +73,7 @@ function C = mtx_prod_kr(A,B)
     end
 end
 
+
 %% Least-Squares Khatri-Rao Factorization (LSKRF)
 
 % This function computes the LSKRF of a given matrix.   

### 2022-06-22 Seminar/codes/tlms_mse.m

@@ -7,7 +7,7 @@ clear all;
 Nh = 5;
 Nv = 5;
 QAM = 2;
-runs = 1000;
+runs = 2500;
 buffer = Nh*Nv;
 Samples = 15000;
 
@@ -21,6 +21,7 @@ mu = 0.1;
 % Monter Carlo simulations
 mse = zeros(Samples,1);
 for rr = 1:runs
+	rr
     % Filter weights
     weights_v = complex(randn(Nv,Samples),randn(Nv,Samples));
     weights_h = complex(randn(Nh,Samples),randn(Nh,Samples));

### 2022-06-22 MATLAB/homework_11.m
TKPSVD, Seminar files and HW12

@@ -42,7 +42,7 @@ for i = 2:aux
     end
 end
 
-disp('Checking the NMSE (dB) between the original matrix X and its reconstruction with MLSKRF:')
+disp('Checking the NMSE (dB) between the original tensor X and its reconstruction with MLSKRF:')
 Xhat = tensor.fold(Ahat*(tensor.mtx_prod_kr(Chat,Bhat).'),[ia ib ic],1);
 nmsex = (norm(tensor.unfold(X- Xhat,1),'fro')^2)/(norm(tensor.unfold(X,1),'fro')^2);
 nmsex = 20*log10(nmsex)

### 2022-06-22 MATLAB/homework_12.m

@@ -1,0 +1,155 @@
+%% ----- Homework 13 ----- %%
+clc;
+clear;
+close all;
+
+%% TKPSVD 
+R = 1;
+N = 3;
+
+A = zeros(80,R);
+B = zeros(20,R);
+C = zeros(8,R);
+tenX = zeros(100,16,8);
+for r = 1:R
+    tenA = randn(10,4,2);
+    %tenA = tenA./frob(tenA);
+    A(:,r)= tenA(:);
+    tenB = randn(5,2,2);
+    %tenB = tenB./frob(tenB);
+    B(:,r)= tenB(:);
+    tenC = randn(2,2,2);
+    %tenC = tenC./frob(tenC);
+    C(:,r)= tenC(:);
+    varr = tensor.ten_prod_kron(tenC,tenB);
+    tenX = tenX + tensor.ten_prod_kron(varr,tenA);
+end
+
+aux{1} = num2cell(size(tenA));
+aux{2} = num2cell(size(tenB));
+aux{3} = num2cell(size(tenC));
+tenSize = horzcat(aux{:});
+tenDim = cellfun(@(aux) prod(cell2mat(aux)), aux,'UniformOutput',false);
+
+tenX = tensor.ten_prod_kron(tenC,tenB);
+tenX = tensor.ten_prod_kron(tenX,tenA);
+
+[Ahat,Bhat,Chat] = tensor.TKPSVD(tenX,tenSize,tenDim,N,R);
+
+aux1 = aux{1};
+aux2 = aux{2};
+aux3 = aux{3};
+tenXhat = zeros(100,16,8);
+for r = 1:R
+    tenAhat_r = reshape(Ahat(:,r),aux1{:});
+    %tenAhat_r = tenAhat_r./frob(tenAhat_r);
+    tenBhat_r = reshape(Bhat(:,r),aux2{:});
+    %tenBhat_r = tenBhat_r./frob(tenBhat_r);
+    tenChat_r = reshape(Chat(:,r),aux3{:});
+    %tenChat_r = tenChat_r./frob(tenChat_r);
+    varr = tensor.ten_prod_kron(tenChat_r,tenBhat_r);
+    tenXhat = tenXhat + tensor.ten_prod_kron(varr,tenAhat_r);
+end
+
+disp('Checking the NMSE (dB) between the original tensor X and its reconstruction with TKPSVD:')
[…]

### 2022-06-23 Additional Problems/PARAFAC and Tensor Rank/manuscript.tex
TKPSVD, Seminar files and HW12

@@
 
-    \item Teste
+    \item We know that if we have the tensor defined as
+
+        \begin{align}
+            \mathcal{X} = \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{2},
+        \end{align}
+
+        then if we have $\boldsymbol{b}_{1} = \boldsymbol{b}_{2}$ and $\boldsymbol{c}_{1} = \boldsymbol{c}_{2}$ we can guarantee that $\mathcal{X}$ is rank one.
+We can begin this proof by using the associativity property of the outer product to write tensor $\mathcal{X}$ as
+
+        \begin{align}
+            \mathcal{X} &= \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{2}, \\
+            \mathcal{X} &= \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1}, \\
+            \mathcal{X} &= (\boldsymbol{a}_{1} + \boldsymbol{a}_{2}) \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1}.
+        \end{align}
+
+        By inspection of the expression above we can see that the elements that compose vectors $\boldsymbol{a}_{1}$ and $\boldsymbol{a}_{2}$
+        acts as weights in a linear combination of the matrix $\boldsymbol{b}_{1} \circ \boldsymbol{c}_{1}$.
+Thus, if we assume that the tensor is not rank one then we should at least one of the vectors equals to zero so we can obtain a sum of linearly independent terms that leads to a tensor rank greater than one.
+        However, this does not makes sense because if we have one of these vectors equals to zero then  we would not have a sum at all.
+Thus, by contradiction, we know that in the proposed scenario the vectors $\boldsymbol{a}_{1}$ and $\boldsymbol{a}_{2}$ must be collinear meaning that the tensor is indeed rank one.
+        In a similar fashion we can obtain a conclusion for the case
+        where we have $\boldsymbol{b}_{1} \neq \boldsymbol{b}_{2}$ and $\boldsymbol{c}_{1} = \boldsymbol{c}_{2}$ by writting the tensor as
+
+        \begin{align}
+            \mathcal{X} &= \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{2}, \\
+            \mathcal{X} &= \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{1}, \\
+            \mathcal{X} &= (\boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2}) \circ \boldsymbol{c}_{1}.
+        \end{align}
+
+        By inspecting the expression above by the same procedure as before we can once again reach the same conclusion that the only way to the tensor $\mathcal{X}$ to have a rank greater than one in this
+        scenario is if one of the vectors is zero, but that would be contradictory. Thus, we can guarantee once more that the tensor $\mathcal{X}$ will be rank one in this case.
+
+    \item
+
+    \item
+
+        \begin{enumerate}
+
+            \item
+
+            \item
+
+            \item
+
+            \item
+
+        \end{enumerate}
+
+    \item
+
+        \begin{enumerate}
+
+            \item
+
+            \item
+
+            \item
+
+        \end{enumerate}
 

### 2022-06-23 Additional Problems/PARAFAC and Tensor Rank/manuscript.tex
2nd list Q1 and Q2

--- 2022-06-15 Additional Problems/PARAFAC and Tensor Rank/manuscript.tex
@@
 
-    \item Teste
+    \item We know that if we have the tensor defined as
+
+        \begin{align}
+            \mathcal{X} = \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{2},
+        \end{align}
+
+        then if we have $\boldsymbol{b}_{1} = \boldsymbol{b}_{2}$ and $\boldsymbol{c}_{1} = \boldsymbol{c}_{2}$ we can guarantee that $\mathcal{X}$ is rank one.
+We can begin this proof by using the associativity property of the outer product to write tensor $\mathcal{X}$ as
+
+        \begin{align}
+            \mathcal{X} &= \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{2}, \\
+            \mathcal{X} &= \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1}, \\
+            \mathcal{X} &= (\boldsymbol{a}_{1} + \boldsymbol{a}_{2}) \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1},
+        \end{align}
+
+        and by inspecting above expression we can observe that independent of the vectors $\boldsymbol{a}_{1}$ and $\boldsymbol{a}_{2}$ being collinear we will have a rank one tensor defined as
+
+        \begin{align}
+            \mathcal{X} &= \boldsymbol{a}_{3} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1},
+        \end{align}
+
+        where $\boldsymbol{a}_{3} = \boldsymbol{a}_{1} + \boldsymbol{a}_{2}$.
+In a similar fashion, if we have $\boldsymbol{b}_{1} \neq \boldsymbol{b}_{2}$ and $\boldsymbol{c}_{1} = \boldsymbol{c}_{2}$ then we can rewrite the tensor as
+
+        \begin{align}
+            \mathcal{X} &= \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{2}, \\
+            \mathcal{X} &= \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{1}, \\
+            \mathcal{X} &= (\boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2}) \circ \boldsymbol{c}_{1},
+        \end{align}
+
+        but since we can guarantee that the vectors $\boldsymbol{b}_{1}$ and $\boldsymbol{b}_{2}$ are not collinear then we know that the sum in above expression cannot be further reduced.
+Thus, we will have a tensor
+        composed of the sum of two subtensors of rank one meaning that our tensor $\mathcal{X}$  will be a rank two tensor.
+
+    \item To show that the tensor rank is a property we will begin by writting the following multilinear transformations
+
+        \begin{align}
+            \mathcal{X} &= \mathcal{S} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{3} \boldsymbol{A}^{(3)}, \\
+            \mathcal{S} &= \mathcal{X} \times_{1} \boldsymbol{A}^{(1)^{\text{H}}} \cdots \times_{3} \boldsymbol{A}^{(3)^{\text{H}}}.
+        \end{align}
+
+        First we can begin by defining the core tensor $\mathcal{S}$ by its PARAFAC Decomposition as
+
+        \begin{align}
+            \mathcal{S} = \sum^{R}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{s}^{(3)}_{r},
+        \end{align}
+
+        and by returning to the original transformation we can rewrite it as
+
+        \begin{align}
+            \mathcal{X} &= \left(\sum^{R}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{s}^{(N)}_{r}\right) \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{3} \boldsymbol{A}^{(3)}, \\
+            \mathcal{X} &= \left(\sum^{R}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{s}^{(N)}_{r} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{3} \boldsymbol{A}^{(3)}\right), \\
+            \mathcal{X} &= \sum^{R}_{r = 1} \boldsymbol{A}^{(1)} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{A}^{(N)} \boldsymbol{s}^{(N)}_{r}.
+        \end{align}
+
+        Now considering the inverse multilinear transformation and that $\boldsymbol{A}^{(n)^{\text{H}}} \boldsymbol{A}^{(n)} = \boldsymbol{I}, \forall n \in \{1, \cdots, N\}$ we can rewrite tensor $\mathcal{S}$ as
+
+        \begin{align}
+            \mathcal{S} &= \mathcal{X} \times_{1} \boldsymbol{A}^{(1)^{\text{H}}} \cdots \times_{3} \boldsymbol{A}^{(3)^{\text{H}}}, \\
+            \mathcal{S} &= \left(\sum^{R}_{r = 1} \boldsymbol{A}^{(1)} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{A}^{(N)} \boldsymbol{s}^{(N)}_{r} \right) \times_{1} \boldsymbol{A}^{(1)^{\text{H}}} \cdots \times_{3} \boldsymbol{A}^{(3)^{\text{H}}}, \\
+            \mathcal{S} &= \left(\sum^{R}_{r = 1} \boldsymbol{A}^{(1)} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{A}^{(N)} \boldsymbol{s}^{(N)}_{r} \times_{1} \boldsymbol{A}^{(1)^{\text{H}}} \cdots \times_{3} \boldsymbol{A}^{(3)^{\text{H}}} \right), \\
+            \mathcal{S} &= \sum^{R}_{r = 1} \boldsymbol{A}^{(1)^{\text{H}}} \boldsymbol{A}^{(1)} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{A}^{(N)^{\text{H}}} \boldsymbol{A}^{(N)} \boldsymbol{s}^{(N)}_{r}, \\
+            \mathcal{S} &= \sum^{R}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{s}^{(3)}_{r}
+        \end{align}
+
+        and since the tensor rank is defined by the minimum number of rank one tensors that together compose the original tensor then by analysing above expressions we can observe that we have bounded tensors
+        $\mathcal{X}$ and $\mathcal{S}$ to the same number of elements that compose them. Thus, the tensor rank is indeed a property and
+
+        \begin{align}
+            \text{rank}\left(\mathcal{X}\right) = \text{rank}\left(\mathcal{S}\right).
+        \end{align}
+
+    \item
+
+        \begin{enumerate}
+
+            \item
+
+            \item
+
+            \item
+
+            \item
+
+        \end{enumerate}
+
+    \item
+
+        \begin{enumerate}
+
+            \item
+
+            \item
+
+            \item
+
+        \end{enumerate}
 

### 2022-06-23 Additional Problems/PARAFAC and Tensor Rank/manuscript.tex
2nd list Q3

@@
         \begin{align}
-            \mathcal{X} &= \mathcal{S} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{3} \boldsymbol{A}^{(3)}, \\
-            \mathcal{S} &= \mathcal{X} \times_{1} \boldsymbol{A}^{(1)^{\text{H}}} \cdots \times_{3} \boldsymbol{A}^{(3)^{\text{H}}}.
+            \mathcal{X} &= \mathcal{S} \times_{1} \boldsymbol{A}^{(1)} \cdots \times_{3} \boldsymbol{A}^{(3)} \in \mathbb{C}^{I_{1} \times \cdots \times I_{N}}, \\
+            \mathcal{S} &= \mathcal{X} \times_{1} \boldsymbol{A}^{(1)^{\text{H}}} \cdots \times_{3} \boldsymbol{A}^{(3)^{\text{H}}} \in \mathbb{C}^{I_{1} \times \cdots \times I_{N}}.
         \end{align}
@@
 
-    \item
+        Moreover, if we consider the case of dimension reduction where $\mathcal{S} \in \mathbb{C}^{R_{1} \times \cdots \times R_{N}}$ with $R_{n} << I_{n}, \forall n \in \{1, \cdots, N\}$ the if we can guarantee that
+        $\boldsymbol{A}^{(n)^{\dagger}} \boldsymbol{A}^{(n)} = \boldsymbol{I}, \forall n \in \{1, \cdots, N\}$ then we should once more have the same tensor rank for the case where the factor matrices are defined as $\boldsymbol{A}^{n} \in \mathbb{C}^{I_{n} \times R_{n}}, \forall \{1, \cdots, N\}$.
 
-        \begin{enumerate}
+    \item Proof that the following tensor has rank three if all the vector pairs are non collinear
 
-            \item
+        \begin{align}
+            \mathcal{X} = \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{1} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{2} \in \mathbb{C}^{I_{1} \times I_{2} \times I_{3}},
+        \end{align}
 
-            \item
+        First we need to show that above tensor have a multilinear transformation defined as
 
-            \item
+        \begin{align}
+            \mathcal{X} &= \mathcal{S} \times_{1} \boldsymbol{A} \times_{2} \boldsymbol{B} \times_{3} \boldsymbol{C} \in \mathbb{C}^{I_{1} \times I_{2} \times I_{N}},  
+        \end{align}
 
-            \item
+        where the unfoldings of the core tensor $\mathcal{S}$
 
-        \end{enumerate}
+        \begin{align}
+            \left[\boldsymbol{S}\right]_{(1)} = 
+            \begin{bmatrix}
+                1 & 0 & 0 & 1 \\
+                0 & 1 & 0 & 0
+            \end{bmatrix},  
+            \left[\boldsymbol{S}\right]_{(2)} = 
+            \begin{bmatrix}
+                1 & 0 & 0 & 0 \\
+                0 & 1 & 1 & 0
+            \end{bmatrix},  
+            \left[\boldsymbol{S}\right]_{(3)} = 
+            \begin{bmatrix}
+                1 & 0 & 0 & 1 \\
+                0 & 0 & 1 & 0
+            \end{bmatrix},  
+        \end{align}
+
+        thus we have that the tensor $\mathcal{X}$ can be written
+
+        \begin{align}
+            \left[\boldsymbol{X}\right]_{(1)} &= \boldsymbol{A} \left[\boldsymbol{S}\right]_{(1)} (\boldsymbol{C} \otimes \boldsymbol{B})^{\text{T}}, \\
+            \left[\boldsymbol{X}\right]_{(1)} &= 
+            \begin{bmatrix}
+                \boldsymbol{a}_{1} & \boldsymbol{a}_{2}
+            \end{bmatrix}
+            \begin{bmatrix}
+                1 & 0 & 0 & 1 \\
+                0 & 1 & 0 & 0
+            \end{bmatrix} 
+            \begin{bmatrix}
+                (\boldsymbol{c}_{1} \otimes \boldsymbol{b}_{1})^{\text{T}} & (\boldsymbol{c}_{1} \otimes \boldsymbol{b}_{2})^{\text{T}} & (\boldsymbol{c}_{2} \otimes \boldsymbol{b}_{1})^{\text{T}} & (\boldsymbol{c}_{2} \otimes \boldsymbol{b}_{2})^{\text{T}}
+            \end{bmatrix}, \\
+            \left[\boldsymbol{X}\right]_{(1)} &= 
+            \begin{bmatrix}
+                \boldsymbol{a}_{1} & \boldsymbol{a}_{2}
+            \end{bmatrix}
+            \begin{bmatrix}
+                (\boldsymbol{c}_{1} \otimes \boldsymbol{b}_{1})^{\text{T}} + (\boldsymbol{c}_{2} \otimes \boldsymbol{b}_{2})^{\text{T}} \\
+                (\boldsymbol{c}_{1} \otimes \boldsymbol{b}_{2})^{\text{T}}
+            \end{bmatrix}, \\
+            \left[\boldsymbol{X}\right]_{(1)} &= \boldsymbol{a}_{1} (\boldsymbol{c}_{1} \otimes \boldsymbol{b}_{1})^{\text{T}} + \boldsymbol{a}_{1} (\boldsymbol{c}_{2} \otimes \boldsymbol{b}_{2})^{\text{T}} + \boldsymbol{a}_{2} (\boldsymbol{c}_{1} \otimes \boldsymbol{b}_{2})^{\text{T}},
+        \end{align}
+
+        and by doing the folding we get
+
+        \begin{align}
+            \mathcal{X} &= \boldsymbol{a}_{1} (\boldsymbol{c}_{1} \otimes \boldsymbol{b}_{1})^{\text{T}} + \boldsymbol{a}_{1} (\boldsymbol{c}_{2} \otimes \boldsymbol{b}_{2})^{\text{T}} + \boldsymbol{a}_{2} (\boldsymbol{c}_{1} \otimes \boldsymbol{b}_{2})^{\text{T}}, \\
+            \mathcal{X} &= \boldsymbol{a}_{1} \circ \boldsymbol{b}_{1} \circ \boldsymbol{c}_{1} + \boldsymbol{a}_{1} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{2} + \boldsymbol{a}_{2} \circ \boldsymbol{b}_{2} \circ \boldsymbol{c}_{1}.
+        \end{align}
+
+        We also know from the previous problem that the tensor rank is indeed a property.
+Thus, the tensor $\mathcal{X}$ and the core tensor $\mathcal{S}$ of its multilinear transformation will have the same tensor rank.
+        Now, we only need to proof that either one of them are a tensor with rank three.
+The easiest way to do this is by working with the core tensor of the multilinear transformation, the tensor $\mathcal{S}$, and start a proof by contradiction.
 

### 2022-06-23 MATLAB/homework_12.m
Tensor Contraction and TTSVD fully implemented

@@ -54,8 +54,11 @@ end
 disp('Checking the NMSE (dB) between the original tensor X and its reconstruction with TKPSVD:')
 nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2);
 nmsex = 20*log10(nmsex)
+disp('Checking the NMSE (dB) between the original matrix A and its reconstruction with TKPSVD:')
 nmsea = 20*log10((norm(A- Ahat,'fro')^2)/(norm(A,'fro')^2))
+disp('Checking the NMSE (dB) between the original matrix B and its reconstruction with TKPSVD:')
 nmseb = 20*log10((norm(B- Bhat,'fro')^2)/(norm(B,'fro')^2))
+disp('Checking the NMSE (dB) between the original matrix C and its reconstruction with TKPSVD:')
 nmsec = 20*log10((norm(C- Chat,'fro')^2)/(norm(C,'fro')^2))
 
 %% Monte Carlo Simulation

### 2022-06-23 MATLAB/homework_13.m

@@ -3,7 +3,98 @@ clc;
 clear;
 close all;
 
-% I need to implement the tensor contraction to test the TTSVD.
-Ranks = [5 5 5];
-X = randn(5,5,5,5);
-[G] = tensor.TTSVD(X,Ranks);
+%% Tensor Train SVD for a fourth order tensor
+I1 = 5;
+I2 = 5;
+I3 = 5;
+I4 = 5;
+Ranks = [3 3 3];
+
+G1 = randn(I1,Ranks(1));
+G2 = randn(Ranks(1),I2,Ranks(2));
+G3 = randn(Ranks(2),I3,Ranks(3));
+G4 = randn(Ranks(3),I4);
+
+tenX = tensor.contraction(G1,2,G2,1);
+tenX = tensor.contraction(tenX,3,G3,1);
+tenX = tensor.contraction(tenX,4,G4,1);
+
+[G] = tensor.TTSVD(tenX,Ranks);
+
+tenXhat = tensor.contraction(G{1},2,G{2},1);
+tenXhat = tensor.contraction(tenXhat,3,G{3},1);
+tenXhat = tensor.contraction(tenXhat,4,G{4},1);
+
+disp('Checking the TTSVD NMSE (dB) from reconstruction using ranks = [3 3 3]:')
+nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2);
+nmsex = 20*log10(nmsex)
+
+Ranks = [2 2 2];
+[G] = tensor.TTSVD(tenX,Ranks);
+
+tenXhat = tensor.contraction(G{1},2,G{2},1);
+tenXhat = tensor.contraction(tenXhat,3,G{3},1);
+tenXhat = tensor.contraction(tenXhat,4,G{4},1);
+disp('Checking the TTSVD NMSE (dB) from reconstruction using ranks = [2 2 2]:')
+nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2);
+nmsex = 20*log10(nmsex)
+
+%% Monte Carlo Simulation
+I1 = 5;
+I2 = 5;
+I3 = 5;
+I4 = 5;
+Ranks  = [3 3 3];
+Ranks1 = [2 2 2];
+Ranks2 = [3 3 3];
+
+SNR = [0 5 10 15 20 25 30];
[…]

### 2022-06-23 MATLAB/tensor.m

@@ -496,9 +496,31 @@ function [Ahat,Bhat,Chat] = TKPSVD(tenX,tenSize,tenDim,N,R)
     [Ahat,Bhat,Chat,~] = tensor.ALS(tenXhat,R);
 end
 
+%% Tensor Contraction
+
+% This function computes the tensor contraction between a tensor and a matrix
+% or between two tensors.   
+% Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+% Created: June 2022
+
+function [tenZ] = contraction(tenX,n1,tenY,n2)
+    % Obtaining the unfolds
+    tenX_n = tensor.unfold(tenX,n1);
+    tenY_n = tensor.unfold(tenY,n2);
+    % Obtaining the unfold of the contracted tensor
+    tenZ_n = (tenX_n.')*tenY_n;
+    % Obtaining the fold of the contracted tensor
+    dim_x = size(tenX);
+    dim_x(n1) = [];
+    dim_y = size(tenY);
+    dim_y(n2) = [];
+    dim_z = [dim_x dim_y];
+    tenZ   = tensor.fold(tenZ_n,dim_z,1);
+end
+
 %% Tensor Train Single Value Decomposition (TT-SVD)
 
-% This function computes the TT-SVD of a fourth order tensor but can be extended.   
+% This function computes the TT-SVD of a fourth order tensor but can be extended later.   
 % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
 % Created: June 2022
 

### 2022-06-23 Report/manuscript.tex
Updating readme,report,codes and lists

\documentclass[a4paper,10pt]{article}

\usepackage{cite}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amstext,amsmath,amssymb}
\usepackage[shortlabels]{enumitem}

\setlength{\oddsidemargin}{0cm} %
\setlength{\evensidemargin}{0cm} %
\setlength{\topmargin}{0cm} %
\setlength{\textwidth}{16cm} %
\setlength{\textheight}{22.5cm} %

\pagestyle{empty}
\newcommand{\assunto}{PARAFAC and Tensor Rank}

\sloppy

\begin{document}

\input{front.tex}
\thispagestyle{empty}

\newpage

\thispagestyle{empty}

\newpage
\section*{Homework 0 \\ Kronecker Product Run Time}

\newpage
\section*{Homework 1 \\ Hadamard, Kronecker and Khatri-Rao Products}

\newpage
\section*{Homework 2 \\ Khatri-Rao Product Run Time}

\newpage
\section*{Homework 3 \\ Least-Squares Khatri-Rao Factorization (LSKRF)}

    \subsection*{Implementation LSKRF}

    \subsection*{Monte Carlo Experiment}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw3.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs for LSKRF algorithm.}
        \label{fig:hw3} 
    \end{figure}

\newpage
\section*{Homework 4 \\ Least Squares Kronecker Product Factorization (LSKronF)}

    \subsection*{Implementation LSKronF}

    \subsection*{Monte Carlo Experiment}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw4.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs for LSKronf algorithm.}
        \label{fig:hw4} 
    \end{figure}

\newpage
\section*{Homework 5 \\ Kronecker Product Singular Value Decomposition (KPSVD)}

    \subsection*{Implementation KPSVD}

    \subsection*{Validation of KPSVD}

\newpage
\section*{Homework 6 \\ Unfolding, folding, and n-mode product}

    \subsection*{Implementation unfolding, folding and n-mode product}

    \subsection*{Validation of unfolding, folding and n-mode product}

\newpage
\section*{Homework 7 \\ High Order Singular Value Decomposition (HOSVD)}

    \subsection*{Implementation HOSVD}

    \subsection*{Validation of HOSVD}

\newpage
\section*{Homework 8 \\ High Order Order Orthogonal Iteration (HOOI)}

    \subsection*{Implementation HOOI}

    \subsection*{Validation of HOOI}

\newpage
\section*{Homework 9 \\ Multidimensional Least-Squares Khatri-Rao Factorization
(MLS-KRF)}

    \subsection*{Implementation MLS-KRF}

    \subsection*{Monte Carlo Experiment}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw9.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs for MLS-KRF algorithm.}
        \label{fig:hw9} 
    \end{figure}

\newpage
\section*{Homework 10 \\ Multidimensional Least-Squares Kronecker Factorization
(MLS-KronF)}

    \subsection*{Implementation MLS-KronF}

    \subsection*{Monte Carlo Experiment}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw10.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs for MLS-KronF algorithm.}
        \label{fig:hw10} 
    \end{figure}

\newpage
\section*{Homework 11 \\ Alternating Least Squares (ALS) Algorithm}

    \subsection*{Implementation of ALS}

    \subsection*{Monte Carlo Experiment}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw11a1.png} \par 
        \caption{Convergence behavior of ALS algorithm.}
        \label{fig:hw11a1} 
    \end{figure}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw11a2.png} \par 
        \caption{Monter Carlo Experimento with 1000 runs for ALS algorithm.}
        \label{fig:hw11a2} 
    \end{figure}

\newpage
\section*{Homework 12 \\ Tensor Kronecker Product Single Value Decomposition (TKPSVD)}

    \subsection*{Implementation of TKPSVD}

    \subsection*{Monte Carlo Experiment}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw12.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs for TKPSVD algorithm.}
        \label{fig:hw12} 
    \end{figure}

\newpage
\section*{Homework 13 \\ Tensor Train Single Value Decomposition (TTSVD)}

    \subsection*{Implementation of TTSVD}

    \subsection*{Monte Carlo Experiment}

    \begin{figure}[ht!]
        \centering 
        \includegraphics[width=0.75\linewidth]{figs/hw13.png} \par 
        \caption{Monter Carlo Experiment with 1000 runs for TTSVD algorithm.}
        \label{fig:hw13} 
    \end{figure}

%\bibliographystyle{ieeetr}
%\bibliography{bibliography.bib}

\end{document}

### 2022-06-23 MATLAB/homework3.m

@@ -45,13 +45,7 @@ nmse  = nmse/1000;
 figure
 txt = ['I = ' num2str(I), ', J = ' num2str(J), ' and R = ' num2str(R)];
 plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
-title(['LSKRF performance under imperfect scenario'])
-xlabel('SNR (dB)')
-ylabel('NMSE (dB)')
-legend_copy = legend("location", "northwest");
-set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
-grid on;
-saveas(gcf,'hw3a1.png')
+hold on;
 
 I = 30;
 J = 10;
@@ -76,13 +70,13 @@ for snr = 1:length(SNR)
 end
 nmse  = nmse/1000;
 
-figure
 txt = ['I = ' num2str(I), ', J = ' num2str(J), ' and R = ' num2str(R)];
-plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+plot(SNR,nmse,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+hold off;
 title(['LSKRF performance under imperfect scenario'])
 xlabel('SNR (dB)')
 ylabel('NMSE (dB)')
 legend_copy = legend("location", "northwest");
 set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
 grid on;
-saveas(gcf,'hw3a2.png')
+saveas(gcf,'hw3.png')

### 2022-06-23 MATLAB/homework4.m

@@ -46,13 +46,7 @@ nmse  = nmse/1000;
 figure
 txt = ['I = ' num2str(I), ', J = ' num2str(J), ', P = ' num2str(P), ' and Q = ' num2str(Q)];
 plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
-title(['LSKronF performance under imperfect scenario'])
-xlabel('SNR (dB)')
-ylabel('NMSE (dB)')
-legend_copy = legend("location", "northwest");
-set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
-grid on;
-saveas(gcf,'hw4a1.png')
+hold on;
 
 I = 4;
 J = 8;
@@ -78,13 +72,13 @@ for snr = 1:length(SNR)
 end
 nmse  = nmse/1000;
 
-figure
 txt = ['I = ' num2str(I), ', J = ' num2str(J), ', P = ' num2str(P), ' and Q = ' num2str(Q)];
-plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+plot(SNR,nmse,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+hold off;
 title(['LSKronF performance under imperfect scenario'])
 xlabel('SNR (dB)')
 ylabel('NMSE (dB)')
 legend_copy = legend("location", "northwest");
 set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
 grid on;
-saveas(gcf,'hw4a2.png')
+saveas(gcf,'hw4.png')

### 2022-06-23 MATLAB/homework9.m

@@ -62,4 +62,4 @@ ylabel('NMSE (dB)')
 legend_copy = legend("location", "northwest");
 set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
 grid on;
-saveas(gcf,'hw9a1.png')
+saveas(gcf,'hw9.png')

### 2022-06-23 MATLAB/homework_11.m

@@ -50,7 +50,7 @@ disp('Checking the NMSE (dB) between the original matrix A and its estimation:')
 nmsea = (norm(A - Ahat,'fro')^2)/(norm(A,'fro')^2);
 nmsea = 20*log10(nmsea)
 disp('Checking the NMSE (dB) between the original matrix B and its estimation:')
-nmseb = (norm(B - Bhat,'fro')^2)/(norm(B,'fro')^2);
+nmseb = (norm(B - Bhat,'fro')^2)/(norm(B,[0.3010 0.7450 0.9330]'fro')^2);
 nmseb = 20*log10(nmseb)
 disp('Checking the NMSE (dB) between the original matrix C and its estimation:')
 nmsec = (norm(C - Chat,'fro')^2)/(norm(C,'fro')^2);

### 2022-06-23 MATLAB/homework_12.m

@@ -88,7 +88,7 @@ for snr = 1:length(SNR)
             %tenC = tenC./frob(tenC);
             C(:,r)= tenC(:);
             varr = tensor.ten_prod_kron(tenC,tenB);
-            tenX = tenX + tensor.ten_prod_kron(varr,tenA);
+            tenX = tenX + tefigurensor.ten_prod_kron(varr,tenA);
         end
 
         aux{1} = num2cell(size(tenA));

### 2022-06-23 Report/manuscript.tex
Updating readme,report,codes and lists

@@
 
+    \subsection*{Run Time Perfomance of Sequential Kronecker Products}
+
+    \begin{figure}[ht!]
+        \centering 
+        \includegraphics[width=0.75\linewidth]{figs/hw0a1.png} \par 
+        \caption{Monter Carlo Experiment with 5000.}
+        \label{fig:hw0a1} 
+    \end{figure}
+
+    \begin{figure}[ht!]
+        \centering 
+        \includegraphics[width=0.75\linewidth]{figs/hw0a2.png} \par 
+        \caption{Monter Carlo Experiment with 10000 runs.}
+        \label{fig:hw0a2} 
+    \end{figure}
+
+    \subsection*{Show that $\text{eig}(\boldsymbol{A} \otimes \boldsymbol{B}) = \text{eig}(\boldsymbol{A}) \otimes \text{eig}(\boldsymbol{B})$}
+
 \newpage
@@
 
+    \subsection*{Run Time Perfomance of Hadamard Product}
+
+    \begin{figure}[ht!]
+        \centering 
+        \includegraphics[width=0.75\linewidth]{figs/hw1a1.png} \par 
+        \caption{Monter Carlo Experiment with 1000 runs.}
+        \label{fig:hw1a1} 
+    \end{figure}
+
+    \subsection*{Run Time Perfomance of Kronecker Product}
+
+    \begin{figure}[ht!]
+        \centering 
+        \includegraphics[width=0.75\linewidth]{figs/hw1a2.png} \par 
+        \caption{Monter Carlo Experiment with 1000 runs.}
+        \label{fig:hw1a2} 
+    \end{figure}
+
+    \subsection*{Run Time Perfomance of Khatri-Rao Product}
+
+    \begin{figure}[ht!]
+        \centering 
+        \includegraphics[width=0.75\linewidth]{figs/hw1a3.png} \par 
+        \caption{Monter Carlo Experiment with 1000 runs.}
+        \label{fig:hw1a3} 
+    \end{figure}
+
 \newpage
 \section*{Homework 2 \\ Khatri-Rao Product Run Time}
+
+    \subsection*{Run Time Performance of Khatri-Rao Product for Different Implementations}
+
+    \begin{figure}[ht!]
+        \centering 
+        \includegraphics[width=0.75\linewidth]{figs/hw2a1.png} \par 
+        \caption{Monter Carlo Experiment with 250 runs and R = 2.}
+        \label{fig:hw2a1} 
+    \end{figure}
+
+    \begin{figure}[ht!]
+        \centering 
+        \includegraphics[width=0.75\linewidth]{figs/hw2a2.png} \par 
+        \caption{Monter Carlo Experiment with 250 runs and R = 4.}
+        \label{fig:hw2a2} 
+    \end{figure}
+
+    \subsection*{Run Time Perfomance of Sequential Khatri-Rao Products}
+
+    \begin{figure}[ht!]
+        \centering 
+        \includegraphics[width=0.75\linewidth]{figs/hw2a3.png} \par 
+        \caption{Monter Carlo Experiment with 250 runs.}
+        \label{fig:hw2a3} 
+    \end{figure}
 

### 2022-06-24 Report/manuscript.tex
Updating report

@@
 
+    In here I will briefly analyze the run time performance of the inverse operator while also using the Kronecker Product.
+In the first case the number of products is fixed while the number of columns is varying.
+    In the second case we have a varying number of products for a fixed number of columns.
+In both cases is possible to see that is preferable to first invert the matrices before applying the Kronecker operator.
+
     \begin{figure}[ht!]
@@
     \subsection*{Show that $\text{eig}(\boldsymbol{A} \otimes \boldsymbol{B}) = \text{eig}(\boldsymbol{A}) \otimes \text{eig}(\boldsymbol{B})$}
+
+    By using the eigenvalue decomposition (eig) of two matrices and apply the Kronecker Product to them it is possible to reach the intended result
+
+    \begin{align}
+        \boldsymbol{A} \otimes \boldsymbol{B} &= (\boldsymbol{C}_{1} \boldsymbol{\Lambda_{1}} \boldsymbol{C}^{-1}_{1}) \otimes (\boldsymbol{C}_{2} \boldsymbol{\Lambda_{2}} \boldsymbol{C}^{-1}_{2}), \\
+        \boldsymbol{A} \otimes \boldsymbol{B} &= (\boldsymbol{C}_{1} \boldsymbol{\Lambda_{1}} \otimes \boldsymbol{C}_{2} \boldsymbol{\Lambda_{2}}) (\boldsymbol{C}^{-1}_{2} \otimes \boldsymbol{C}^{-1}_{2}), \\
+        \boldsymbol{A} \otimes \boldsymbol{B} &= (\boldsymbol{C}_{1} \otimes \boldsymbol{C}_{2}) (\boldsymbol{\Lambda_{1}} \otimes \boldsymbol{\Lambda_{2}}) (\boldsymbol{C}^{-1}_{2} \otimes \boldsymbol{C}^{-1}_{2}), \\
+        \text{eig}(\boldsymbol{A} \otimes \boldsymbol{B}) &= (\boldsymbol{\Lambda_{1}} \otimes \boldsymbol{\Lambda_{2}}) = \text{eig}(\boldsymbol{A}) \otimes \text{eig}(\boldsymbol{B}) 
+    \end{align}
 
@@
 
+    In Figures \ref{fig:hw2a1} and \ref{fig:hw2a2} we can see the processing time for the considered methods to compute the pseudoinverse of a Khatri-Rao product for the cases
+    where we have two and four columns in each matrix.
+To draw the curves it was implemented a Monte Carlo Experiment with only 250 runs for each value $N$ of rows with $N \in \{2, 4, 8, 16, 32, 64\}$.
+    For both cases we can see a clear advantage in using the third method as the dimmensions of the matrices increases.
+In a similar maner, we can also observe that the second method is a bit better than the first however
+    not as good as the third.
+To see a better behavior for these methods it should be necessary to increase the number of rows to better analyse the advantages of each one, however due to technical constraints
+    I could not increase as much as I wanted.
+
+    \begin{align}
+        (\boldsymbol{A} \diamond \boldsymbol{B})^{\dagger} &= \text{pinv}(\boldsymbol{A} \diamond \boldsymbol{B}), \\
+        (\boldsymbol{A} \diamond \boldsymbol{B})^{\dagger} &= [(\boldsymbol{A} \diamond \boldsymbol{B})^{\text{T}} (\boldsymbol{A} \diamond \boldsymbol{B})]^{-1} (\boldsymbol{A} \diamond \boldsymbol{B})^{\text{T}}, \\
+        (\boldsymbol{A} \diamond \boldsymbol{B})^{\dagger} &= [(\boldsymbol{A}^{\text{T}}\boldsymbol{A})(\boldsymbol{B}^{\text{T}}\boldsymbol{B})]^{-1} (\boldsymbol{A} \diamond \boldsymbol{B})^{\text{T}},
+    \end{align}
+
     \begin{figure}[ht!]
@@
 
+    \begin{align}
+        \left(\hat{\boldsymbol{A}}, \hat{\boldsymbol{B}}\right) = \underset{\boldsymbol{A}, \boldsymbol{B}}{\text{min}} \left|\left| \boldsymbol{X} - \boldsymbol{A} \diamond \boldsymbol{B} \right|\right|^2_{\text{F}},
+    \end{align}
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|l|l|}
+        \hline
+        NMSE($\boldsymbol{X}, \boldsymbol{\hat{X}}$) & NMSE($\boldsymbol{A}, \boldsymbol{\hat{A}}$) & NMSE($\boldsymbol{B}, \boldsymbol{\hat{B}}$) \\ \hline
+        -623.4093 & +11.5658 & +7.8479 \\ \hline
+        \end{tabular}
+    \end{table}
+
     \subsection*{Monte Carlo Experiment}
@@
     \subsection*{Implementation LSKronF}
+
+    \begin{align}
+        \left(\hat{\boldsymbol{A}}, \hat{\boldsymbol{B}}\right) = \underset{\boldsymbol{A}, \boldsymbol{B}}{\text{min}} \left|\left| \boldsymbol{X} - \boldsymbol{A} \otimes \boldsymbol{B} \right|\right|^2_{\text{F}},
+    \end{align}
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|l|l|}
+        \hline
+        NMSE($\boldsymbol{X}, \boldsymbol{\hat{X}}$) & NMSE($\boldsymbol{A}, \boldsymbol{\hat{A}}$) & NMSE($\boldsymbol{B}, \boldsymbol{\hat{B}}$) \\ \hline
+        -619.2196 & +13.5472 & +9.5922 \\ \hline
+        \end{tabular}
+    \end{table}
 
@@
 
+    \begin{align}
+        \boldsymbol{X} = \sum^{r_{kp}}_{k = 1} \sigma_{k} \boldsymbol{U}_{k} \otimes \boldsymbol{V}_{k},
+    \end{align}
+
+    In the example is considered that the original matrix has a full rank equals to 9, then two approximations using the KPSVD are provided: One using the full-rank approximation and other using a r-rank approximation $(r < 9)$.
+    The NMSE between some approximations and its original matrix are provided in the sequence
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|l|l|l|}
+        \hline
+        Full Rank & Rank = $7$ & Rank = $5$ & Rank = $3$ & Rank = $1$ \\ \hline
+        -604.8023 & -51.3722 & -26.7589 & -16.9054 & -6.3068 \\ \hline
+        \end{tabular}
+    \end{table}
+
     \subsection*{Validation of KPSVD}
@@
     \subsection*{Implementation unfolding, folding and n-mode product}
+
+    \begin{align}
+        [\mathcal{X}]_{n} &= \text{unfold}(\mathcal{X}, [I_{1} \cdots I_{N} ], n) \in \mathbb{C}^{I_{n} \times I_{1} \cdots I_{n-1} I_{n+1} \cdots I_{N}}, \\
+        \mathcal{X} &= \text{fold}([\mathcal{X}]_{n}, [I_{1} \cdots I_{N} ], n) \in \mathbb{C}^{I_{1} \times \cdots \times I_{N}}, \\
+        \mathcal{Y} &= \mathcal{X} \times_{1} \boldsymbol{U}_{1} \times_{2} \cdots \times_{N} \boldsymbol{U}_{N},
+    \end{align}
 
@@
 
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|l|l|l|}
+        \hline
+        NMSE($\mathcal{X}, \mathcal{\hat{X}}$) & NMSE($\mathcal{S}, \mathcal{\hat{S}}$) & NMSE($\boldsymbol{U}_{1}, \boldsymbol{\hat{U}}_{1}$) & NMSE($\boldsymbol{U}_{2}, \boldsymbol{\hat{U}}_{2}$) & NMSE($\boldsymbol{U}_{3}, \boldsymbol{\hat{U}}_{3}$) \\ \hline
+        -611.2162 & +7.7656 & +2.6667 & +2.0000 & +1.6063 \\ \hline
+        \end{tabular}
+    \end{table}
+
     \subsection*{Validation of HOSVD}
+
+    The multilinear rank advantage is maximized when it comes to process sparce tensors since the dimmensions can be greatly reduced without losing of too much relevant information by analysing the profile of its multiples unfoldings.
+
+    \begin{align}
+        \mathcal{X} &\in \mathbb{C}^{8 \times 4 \times 10} \to \hat{\mathcal{X}} \in \mathbb{C}^{R_{1} \times R_{2} \times R_{3}}, \\ 
+        \mathcal{X} &\in \mathbb{C}^{5 \times 5 \times 5} \to \hat{\mathcal{Y}} \in \mathbb{C}^{P_{1} \times P_{2} \times P_{3}},
+    \end{align}
 
@@
 
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|l|l|l|}
+        \hline
+        NMSE($\mathcal{X}, \mathcal{\hat{X}}$) & NMSE($\mathcal{S}, \mathcal{\hat{S}}$) & NMSE($\boldsymbol{U}_{1}, \boldsymbol{\hat{U}}_{1}$) & NMSE($\boldsymbol{U}_{2}, \boldsymbol{\hat{U}}_{2}$) & NMSE($\boldsymbol{U}_{3}, \boldsymbol{\hat{U}}_{3}$) \\ \hline
+        -607.9515 & +7.2483 & +2.6667 & +3.9622 & +1.16160 \\ \hline
+        \end{tabular}
+    \end{table}
+
     \subsection*{Validation of HOOI}
+
+    The multilinear rank advantage is maximized when it comes to process sparce tensors since the dimmensions can be greatly reduced without losing of too much relevant information by analysing the profile of its multiples unfoldings.
+
+    \begin{align}
+        \mathcal{X} &\in \mathbb{C}^{8 \times 4 \times 10} \to \hat{\mathcal{X}} \in \mathbb{C}^{R_{1} \times R_{2} \times R_{3}}, \\ 
+        \mathcal{X} &\in \mathbb{C}^{5 \times 5 \times 5} \to \hat{\mathcal{Y}} \in \mathbb{C}^{P_{1} \times P_{2} \times P_{3}},
+    \end{align}
 
@@
     \subsection*{Implementation MLS-KRF}
+
+    \begin{align}
+        \left(\hat{\boldsymbol{A}}^{(1)}, \cdots, \hat{\boldsymbol{A}}^{(N)}\right) = \underset{\boldsymbol{A}^{(1)}, \cdots, \boldsymbol{A}^{(N)}}{\text{min}} \left|\left| \boldsymbol{X} - \boldsymbol{A}^{(1)} \diamond \cdots \diamond \boldsymbol{A}^{(N)} \right|\right|^2_{\text{F}},
+    \end{align}
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|l|l|}
+        \hline
+        NMSE($\boldsymbol{X}, \boldsymbol{\hat{X}}$) & NMSE($\boldsymbol{A}_{1}, \boldsymbol{\hat{A}}_{1}$) & NMSE($\boldsymbol{A}_{2}, \boldsymbol{\hat{A}}_{2}$) & NMSE($\boldsymbol{A}_{3}, \boldsymbol{\hat{A}}_{3}$) \\ \hline
+        -606.2255 & +3.1432 & +5.0165 & +4.7297 \\ \hline
+        \end{tabular}
+    \end{table}
 
@@
 
+    \begin{align}
+        \left(\hat{\boldsymbol{A}}^{(1)}, \cdots, \hat{\boldsymbol{A}}^{(N)}\right) = \underset{\boldsymbol{A}^{(1)}, \cdots, \boldsymbol{A}^{(N)}}{\text{min}} \left|\left| \boldsymbol{X} - \boldsymbol{A}^{(1)} \otimes \cdots \otimes \boldsymbol{A}^{(N)} \right|\right|^2_{\text{F}},
+    \end{align}
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|l|l|}
+        \hline
+        NNMSE($\boldsymbol{X}, \boldsymbol{\hat{X}}$) & NMSE($\boldsymbol{A}_{1}, \boldsymbol{\hat{A}}_{1}$) & NMSE($\boldsymbol{A}_{2}, \boldsymbol{\hat{A}}_{2}$) & NMSE($\boldsymbol{A}_{3}, \boldsymbol{\hat{A}}_{3}$) \\ \hline
+        -605.1941 & +11.9214 & +11.5548 & +6.0950 \\ \hline
+        \end{tabular}
+    \end{table}
+
     \subsection*{Monte Carlo Experiment}
@@
     \subsection*{Implementation of ALS}
+
+    \begin{align}
+        \left(\hat{\boldsymbol{A}}, \hat{\boldsymbol{B}}, \hat{\boldsymbol{C}}\right) = \underset{\boldsymbol{A}, \boldsymbol{B}, \boldsymbol{C}}{\text{min}} \left| \left| \mathcal{X} - \sum^{R}_{r = 1} \boldsymbol{a}_{r} \circ \boldsymbol{b}_{r} \circ \boldsymbol{c}_{r} \right| \right|^{2}_{\text{F}},
+    \end{align}
 
@@
 
+    \begin{align}
+        \mathcal{X} = \sum^{R}_{j = 1} \sigma_{i} \mathcal{A}^{(d)}_{j} \otimes \mathcal{A}^{(d - 1)}_{j}  \otimes \cdots \otimes \mathcal{A}^{(1)}_{j},  
+    \end{align}
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|l|l|}
+        \hline
+        NMSE($\mathcal{X}, \mathcal{\hat{X}}$) & NMSE($\mathcal{A}^{(1)}, \mathcal{\hat{A}}^{(1)}$) & NMSE($\mathcal{A}^{(2)}, \mathcal{\hat{A}}^{(2)}$) & NMSE($\mathcal{A}^{(3)}, \mathcal{\hat{A}}^{(3)}$) \\ \hline
+        -625.5192 & +37.0803 & +0.1706 & +32.5731 \\ \hline
+        \end{tabular}
+    \end{table}
+
     \subsection*{Monte Carlo Experiment}
@@
 
+    \begin{align}
+        \mathcal{X} = \boldsymbol{G}_{1} \bullet^{1}_{2} \mathcal{G}_{2} \bullet^{1}_{3} \mathcal{G}_{3} \bullet^{1}_{4} \boldsymbol{G}_{4},
+    \end{align}
+
+    \begin{align}
+        \left(\hat{\boldsymbol{G}_{1}}, \hat{\mathcal{G}_{2}}, \hat{\mathcal{G}_{3}}, \hat{\boldsymbol{G}_{4}}\right) = \underset{\boldsymbol{A}, \boldsymbol{B}, \boldsymbol{C}}{\text{min}} \left| \left| \mathcal{X} - \boldsymbol{G}_{1} \bullet^{1}_{2} \mathcal{G}_{2} \bullet^{1}_{3} \mathcal{G}_{3} \bullet^{1}_{4} \boldsymbol{G}_{4} \right| \right|_{\text{F}},
+    \end{align}
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|}
+        \hline
+        NMSE($\mathcal{X}, \mathcal{\hat{X}}$) with $R = (3,3,3)$ & NMSE($\mathcal{X}, \mathcal{\hat{X}}$) with $R = (2,2,2)$ \\ \hline 
+        -606.0326 & -25.1084 \\ \hline
+        \end{tabular}
+    \end{table}
+
     \subsection*{Monte Carlo Experiment}

### 2022-06-24 MATLAB/homework_12.m

@@ -88,7 +88,7 @@ for snr = 1:length(SNR)
             %tenC = tenC./frob(tenC);
             C(:,r)= tenC(:);
             varr = tensor.ten_prod_kron(tenC,tenB);
-            tenX = tenX + tefigurensor.ten_prod_kron(varr,tenA);
+            tenX = tenX + tensor.ten_prod_kron(varr,tenA);
         end
 
         aux{1} = num2cell(size(tenA));

### 2022-06-24 Report/manuscript.tex
Updating report

@@
 \usepackage{cite}
-\usepackage{graphicx}
+\usepackage{graphicx,color}
 \usepackage{fancyhdr}
@@
 \usepackage[shortlabels]{enumitem}
+
+\usepackage{subcaption}
+\usepackage{mwe}
 
@@
 \sloppy
+\definecolor{lightgray}{gray}{0.5}
+\setlength{\parindent}{0pt}
 
@@
         \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw0a1.png} \par 
+        \includegraphics[width=0.65\linewidth]{figs/hw0a1.png} \par 
         \caption{Monter Carlo Experiment with 5000.}
@@
         \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw0a2.png} \par 
+        \includegraphics[width=0.65\linewidth]{figs/hw0a2.png} \par 
         \caption{Monter Carlo Experiment with 10000 runs.}
@@
 
+    \newpage
     \subsection*{Show that $\text{eig}(\boldsymbol{A} \otimes \boldsymbol{B}) = \text{eig}(\boldsymbol{A}) \otimes \text{eig}(\boldsymbol{B})$}
@@
 
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% ----- Homework 0 ----- %%
+        clc;
+        clear;
+        close all;
+        N = [1 2 3 4 5 6 7 8];
+        time1 = zeros(length(N),1);
+        time2 = zeros(length(N),1);
+        for nn = 1:length(N)
+            for mc = 1:5000
+                A = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
+                B = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
+                tic;
+                inv(tensor.mtx_prod_kron(A,B));
+                aux = toc;
+                time1(nn,1) = time1(nn,1) + aux;
+                tic;
+                tensor.mtx_prod_kron(inv(A),inv(B));
+                aux = toc;
+                time2(nn,1) = time2(nn,1) + aux;
+            end
+        end
+        time1 = time1/5000;
+        time2 = time2/5000;
+        figure
+        txt = ['(\bf A_{N \times N} \otimes B_{N \times N})^{-1}'];
+        semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['\bf A^{-1}_{N \times N} \otimes B^{-1}_{N \times N}'];
+        semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['Performance of inverse operation'])
+        xlabel('Number of columns')
+        ylabel('Time (s)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw0a1.png')
+        N = 2;
+        K = [1 2 3 4 5 6 7 8 9 10];
+        time1 = zeros(length(K),1);
+        time2 = zeros(length(K),1);
+        for kk = 1:length(K)
+            for mc = 1:1000
+                tic;
+                for ii = 1:K(kk)    
+                    if ii == 1
+                        A1 = randn(N,N) + 1j*randn(N,N); 
+                        continue
+                    else
+                        A2 = randn(N,N) + 1j*randn(N,N);
+                        A1 = tensor.mtx_prod_kron(A1,A2);
+                    end    
+                end
+                inv(A1);
+                aux = toc;
+                time1(kk,1) = time1(kk,1) + aux;
+
+                tic;
+                for ii = 1:K(kk)    
+                    if ii == 1
+                        A1 = randn(N,N) + 1j*randn(N,N); 
+                        continue
+                    else
+                        A2 = randn(N,N) + 1j*randn(N,N);
+                        A1 = tensor.mtx_prod_kron(inv(A1),inv(A2));
+                    end    
+                end
+                aux = toc;
+                time2(kk,1) = time2(kk,1) + aux;
+            end
+        end
+        time1 = time1/1000;
+        time2 = time2/1000;
+        figure
+        txt = ['\bf (\otimes^{K}_{i = 1}A^{(i)}_{4 \times 4})^{-1}'];
+        semilogy(K,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['\bf \otimes^{K}_{i = 1}(A^{(i)}_{4 \times 4})^{-1}'];
+        semilogy(K,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['Multiple Kronecker products performance'])
+        xlabel('Number of products')
+        ylabel('Time (s)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw0a2.png')
+    \end{verbatim}
+
 \newpage
@@
 
+    In Figure \ref{fig:hw1a1}, \ref{fig:hw1a2} and \ref{fig:hw1a3} I compare my implemention of Hadarmard, Kronecker and Khatri-Rao Products with the ones availables in the TensorLab package.
+    As we can the only case where my function have shown an almost equal performance to the benchmark was the one where I do the Kronecker Product. The other two functions are far from the ideal
+    performance offered by the TensorLab package. This could probably explained because I did not take full advantage of the vectorization that MATLAB offers when I was creating those two algorithms.
+
     \subsection*{Run Time Perfomance of Hadamard Product}
@@
         \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw1a1.png} \par 
+        \includegraphics[width=0.65\linewidth]{figs/hw1a1.png} \par 
         \caption{Monter Carlo Experiment with 1000 runs.}
@@
         \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw1a2.png} \par 
+        \includegraphics[width=0.65\linewidth]{figs/hw1a2.png} \par 
         \caption{Monter Carlo Experiment with 1000 runs.}
@@
         \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw1a3.png} \par 
+        \includegraphics[width=0.65\linewidth]{figs/hw1a3.png} \par 
         \caption{Monter Carlo Experiment with 1000 runs.}
@@
     \end{figure}
+
+    \newpage
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Hadamard Product
+
+        % This function computes the Hadarmard Product of two given matrices.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: January 2022
+
+        function C = mtx_prod_had(A,B)
+
+            [ia,ja] = size(A);
+            [ib,jb] = size(B);
+
+            if (ia ~= ib) || (ja~=jb)
+                disp('Invalid Matrices!')
+                return;
+            else
+                C = A.*B;
+                %C = zeros(ia,ja);
+                %for i = 1:ia 
+                    %for j = 1:ja
+                        %C(i,j) = A(i,j)*B(i,j);
+                    %end
+                %end
+            end
+        end
+
+        %% Kronecker Product
+
+        % This function computes the Kronecker Product of two given matrices. 
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: January 2022
+
+        function C = mtx_prod_kron(A,B)
+
+            [ia,ja] = size(A);
+            [ib,jb] = size(B);
+
+            A = repelem(A,ib,jb);
+            B = repmat(B,[ia ja]);
+            C = A.*B;
+
+        end
+
+        %% Khatri-Rao Product
+
+        % This function computes the Khatri-Rao Product of two given matrices. 
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: January 2022
+
+        function C = mtx_prod_kr(A,B)
+            [ia,ja] = size(A);
+            [ib,jb] = size(B);
+
+            if (ja~=jb)
+                disp('Invalid Matrices!')
+                return;
+            else
+                C = zeros(ia*ib,ja);
+                for j = 1:ja
+                    C(:,j) = tensor.mtx_prod_kron(A(:,j),B(:,j));
+                end
+            end
+        end
+
+        %% ----- Homework 1 ----- %%
+        clc;
+        clear;
+        close all;
+
+        N = [2 4 8 16 32 64 128];
+        time1 = zeros(length(N),1);
+        time2 = zeros(length(N),1);
+        for nn = 1:length(N)
+            for mc = 1:1000
+                A = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
+                B = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
+                tic;
+                A.*B;
+                aux = toc;
+                time1(nn,1) = time1(nn,1) + aux;
+                tic;
+                tensor.mtx_prod_had(A,B);
+                aux = toc;
+                time2(nn,1) = time2(nn,1) + aux;
+            end
+        end
+        time1 = time1/1000;
+        time2 = time2/1000;
+
+        figure
+        txt = ['Native Function'];
+        semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['Author Function'];
+        semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['Hadamard product performance'])
+        xlabel('Number of columns')
+        ylabel('Time (s)')
+        legend_copy = legend("location", "southeast");
+        set(legend_copy,'Interpreter','tex','location','southeast',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw1a1.png')
+
+        N = [2 4 8 16 32 64];
+        time1 = zeros(length(N),1);
+        time2 = zeros(length(N),1);
+        for nn = 1:length(N)
+            for mc = 1:1000
+                A = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
+                B = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
+                tic;
+                kron(A,B);
+                aux = toc;
+                time1(nn,1) = time1(nn,1) + aux;
+                tic;
+                tensor.mtx_prod_kron(A,B);
+                aux = toc;
+                time2(nn,1) = time2(nn,1) + aux;
+            end
+        end
+        time1 = time1/1000;
+        time2 = time2/1000;
+
+        figure
+        txt = ['Native Function'];
+        semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['Author Function'];
+        semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['Kronecker product performance'])
+        xlabel('Number of columns')
+        ylabel('Time (s)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw1a2.png')
+
+        N = [2 4 8 16 32 64];
+        time1 = zeros(length(N),1);
+        time2 = zeros(length(N),1);
+        for nn = 1:length(N)
+            for mc = 1:1000
+                A = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
+                B = randn(N(nn),N(nn)) + 1j*randn(N(nn),N(nn));
+                tic;
+                kr(A,B);
+                aux = toc;
+                time1(nn,1) = time1(nn,1) + aux;
+                tic;
+                tensor.mtx_prod_kr(A,B);
+                aux = toc;
+                time2(nn,1) = time2(nn,1) + aux;
+            end
+        end
+        time1 = time1/1000;
+        time2 = time2/1000;
+
+        figure
+        txt = ['Native Function'];
+        semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['Author Function'];
+        semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['Khatri-Rao product performance'])
+        xlabel('Number of columns')
+        ylabel('Time (s)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw1a3.png')
+    \end{verbatim}
 
@@
 To see a better behavior for these methods it should be necessary to increase the number of rows to better analyse the advantages of each one, however due to technical constraints
-    I could not increase as much as I wanted.
+    I could not increase as much as I wanted. In the sequence we can see the definition of each implemented method.
 
@@
 
+    In Figure \ref{fig:hw2a3} we analyze the behavior of the Khatri-Rao product when sequential products are taken.
+As we can see it is an exponencial curve since after every product we will have matrices with analyse
+    increasing dimmensions. Thus, when we do need to use consecutive Khatri-Rao products we should seek a way to simplify the operation by using algebraic manipulations.
+
     \begin{figure}[ht!]
@@
     \newpage
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% ----- Homework 2 ----- %%
+        clc;
+        clear;
+        close all;
+
+        R = 2;
+        I = [2 4 8 16 32 64];
+        time1 = zeros(length(I),1);
+        time2 = zeros(length(I),1);
+        time3 = zeros(length(I),1);
+        for ii = 1:length(I)
+            for mc = 1:250
+                A = randn(I(ii),I(ii)) + 1j*randn(I(ii),I(ii));
+                B = randn(I(ii),I(ii)) + 1j*randn(I(ii),I(ii));
+                tic;
+                pinv(tensor.mtx_prod_kr(A,B));
+                aux = toc;
+                time1(ii,1) = time1(ii,1) + aux;
+                tic;
+                (tensor.mtx_prod_kr(A,B).'*tensor.mtx_prod_kr(A,B))...
+                    \(tensor.mtx_prod_kr(A,B).');
+                aux = toc;
+                time2(ii,1) = time2(ii,1) + aux;
+                tic;
+                tensor.mtx_prod_had((A.'*A),(B.'*B))\(tensor.mtx_prod_kr(A,B).');
+                aux = toc;
+                time3(ii,1) = time3(ii,1) + aux;
+            end
+        end
+        time1 = time1/250;
+        time2 = time2/250;
+        time3 = time3/250;
+
+        figure
+        txt = ['1st Method'];
+        plot(I,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['2nd Method'];
+        plot(I,time2,'-d','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['3rd Method'];
+        plot(I,time3,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['Khatri-Rao product performance considering 2 columns'])
+        xlabel('Number of rows')
+        ylabel('Time (s)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw2a1.png')
+
+        R = 4;
+        I = [2 4 8 16 32 64];
+        time1 = zeros(length(I),1);
+        time2 = zeros(length(I),1);
+        time3 = zeros(length(I),1);
+        for ii = 1:length(I)
+            for mc = 1:250
+                A = randn(I(ii),I(ii)) + 1j*randn(I(ii),I(ii));
+                B = randn(I(ii),I(ii)) + 1j*randn(I(ii),I(ii));
+                tic;
+                pinv(tensor.mtx_prod_kr(A,B));
+                aux = toc;
+                time1(ii,1) = time1(ii,1) + aux;
+                tic;
+                (tensor.mtx_prod_kr(A,B).'*tensor.mtx_prod_kr(A,B))...
+                    \(tensor.mtx_prod_kr(A,B).');
+                aux = toc;
+                time2(ii,1) = time2(ii,1) + aux;
+                tic;
+                tensor.mtx_prod_had((A.'*A),(B.'*B))\(tensor.mtx_prod_kr(A,B).');
+                aux = toc;
+                time3(ii,1) = time3(ii,1) + aux;
+            end
+        end
+        time1 = time1/250;
+        time2 = time2/250;
+        time3 = time3/250;
+
+        figure
+        txt = ['1st Method'];
+        plot(I,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['2nd Method'];
+        plot(I,time2,'-d','color', [0.8500 0.3250 0.0980], "linewidth",...
+            2, "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['3rd Method'];
+        plot(I,time3,'-d','color', [0.4660 0.6740 0.1880], "linewidth",...
+            2, "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['Khatri-Rao product performance considering 4 columns'])
+        xlabel('Number of rows')
+        ylabel('Time (s)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw2a2.png')
+
+        I = 4;
+        R = 2;
+        N = [2 4 6 8];
+        time1 = zeros(length(N),1);
+        time2 = zeros(length(N),1);
+        for nn = 1:length(N)
+            for mc = 1:250 
+                tic;
+                for ii = 1:N(nn)
+                    if ii == 1
+                        A1 = randn(I,R) + 1j*randn(I,R); 
+                        continue
+                    else
+                        A2 = randn(I,R) + 1j*randn(I,R);
+                        A1 = tensor.mtx_prod_kron(A1,A2);
+                    end    
+                end
+                aux = toc;
+                time1(nn,1) = time1(nn,1) + aux;
+            end
+        end
+        time1 = time1/250;
+
+        figure
+        txt = ['\bf \diamond^{N}_{n = 1} (A^{(n)}_{4 \times 2})'];
+        semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        title(['Multiple Khatri-Rao products performance'])
+        xlabel('Number of Products')
+        ylabel('Time (s)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northwest',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw2a3.png')
+    \end{verbatim}
+
+\newpage
 \section*{Homework 3 \\ Least-Squares Khatri-Rao Factorization (LSKRF)}
@@
     \subsection*{Implementation LSKRF}
+
+    The LSKRF algorithm aims to solve the following estimation problem
 
@@
     \end{align}
+
+    and by implementing the algorithm it was possible to reach the following table of NMSE (dB) values using the validation files
 
@@
 
+    as we can see the estimation of the matrix $\boldsymbol{X}$ is perfect, but the estimated factor matrices are far from the original ones. This is simply explained by 
+    the scale ambiguity intrinsic to the LSKRF. This could be eliminated if we assume previous knowledge of either the structure of the factor matrices or some of their elements.
+
     \subsection*{Monte Carlo Experiment}
+
+    In Figure \ref{fig:hw3} the Monte Carlo Experiment is used to draw the curves for two different scenarios: $(I,J,R) = (10,10,4)$ and $(I,J,R) = (30,10,4)$. 
+    As we can observe the best performance is the one where the algorithm have fewer elements to estimate. This is to be expected since the noise will have a lot less
+    components that could potentially harm the performance of the LSKRF.
 
@@
     \newpage
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Least-Squares Khatri-Rao Factorization (LSKRF)
+
+        % This function computes the LSKRF of a given matrix.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: February 2022
+
+        function [Ahat,Bhat] = LSKRF(C,ia,ib)
+            [~, jc] = size(C);
+
+            Ahat = complex(zeros(ia,jc),0);
+            Bhat = complex(zeros(ib,jc),0);
+
+            for j = 1:jc
+                Cp = C(:,j);
+                Cp = reshape(Cp, [ib ia]);
+                [U,S,V] = svd(Cp);
+                Ahat(:,j) = sqrt(S(1,1)).*conj(V(:,1));
+                Bhat(:,j) = sqrt(S(1,1)).*U(:,1);
+            end
+        end
+
+        %% ----- Homework 3 ----- %%
+        clc;
+        clear;
+        close all;
+
+        A = randn(4,2) + 1j*randn(4,2);
+        B = randn(6,2) + 1j*randn(6,2);
+        X = tensor.mtx_prod_kr(A,B);
+        [Ahat,Bhat] = tensor.LSKRF(X,4,6);
+        Xhat = tensor.mtx_prod_kr(Ahat,Bhat);
+
+        disp('Checking the NMSE (dB) between the original matrix X and its'... 
+            'reconstruction with LSKRF:')
+        nmsex = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+        nmsex = 20*log10(nmsex)
+        disp('Checking the NMSE (dB) between the original matrix A and its'...
+            'estimation:')
+        nmsea = (norm(A- Ahat,'fro')^2)/(norm(A,'fro')^2);
+        nmsea = 20*log10(nmsea)
+        disp('Checking the NMSE (dB) between the original matrix B and its'... 
+            'estimation:')
+        nmseb = (norm(B- Bhat,'fro')^2)/(norm(B,'fro')^2);
+        nmseb = 20*log10(nmseb)
+
+        I = 10;
+        J = 10;
+        R =  4;
+        SNR = [0 5 10 15 20 25 30];
+        nmse = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            for mc = 1:1000
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise/2)*(randn(I*J,R) + 1j*randn(I*J,R));
+
+                A = randn(I,R) + 1j*randn(I,R);
+                B = randn(J,R) + 1j*randn(J,R);
+                X = tensor.mtx_prod_kr(A,B);
+                X_noisy = X + noise;
+
+                [Ahat,Bhat] = tensor.LSKRF(X_noisy,I,J);
+                Xhat = tensor.mtx_prod_kr(Ahat,Bhat);
+                aux = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse(snr,1) = nmse(snr,1) + 20*log10(aux);
+            end
+        end
+        nmse  = nmse/1000;
+
+        figure
+        txt = ['I = ' num2str(I), ', J = ' num2str(J), ' and R = ' num2str(R)];
+        plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+
+        I = 30;
+        J = 10;
+        R =  4;
+        SNR = [0 5 10 15 20 25 30];
+        nmse = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            for mc = 1:1000
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise/2)*(randn(I*J,R) + 1j*randn(I*J,R));
+
+                A = randn(I,R) + 1j*randn(I,R);
+                B = randn(J,R) + 1j*randn(J,R);
+                X = tensor.mtx_prod_kr(A,B);
+                X = X + noise;
+
+                [Ahat,Bhat] = tensor.LSKRF(X,I,J);
+                Xhat = tensor.mtx_prod_kr(Ahat,Bhat);
+                aux = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse(snr,1) = nmse(snr,1) + 20*log10(aux);
+            end
+        end
+        nmse  = nmse/1000;
+
+        txt = ['I = ' num2str(I), ', J = ' num2str(J), ' and R = ' num2str(R)];
+        plot(SNR,nmse,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['LSKRF performance under imperfect scenario'])
+        xlabel('SNR (dB)')
+        ylabel('NMSE (dB)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw3.png')
+    \end{verbatim}
+
+\newpage
 \section*{Homework 4 \\ Least Squares Kronecker Product Factorization (LSKronF)}
@@
     \subsection*{Implementation LSKronF}
+
+    The LSKronF algorithm aims to solve the following estimation problem
 
@@
 
+    as we can see the estimation of the matrix $\boldsymbol{X}$ is perfect, but the estimated factor matrices are far from the original ones. This is simply explained by 
+    the scale ambiguity intrinsic to the LSKronF. This could be eliminated if we assume previous knowledge of either the structure of the factor matrices or some of their elements.
+
     \subsection*{Monte Carlo Experiment}
+
+    In Figure \ref{fig:hw4} the Monte Carlo Experiment is used to draw the curves for two different scenarios: $(I,J,P,Q) = (2,4,3,5)$ and $(I,J,P,Q) = (4,8,3,5)$. 
+    As we can observe the best performance is the one where the algorithm have fewer elements to estimate. This is to be expected since the noise will have a lot less
+    components that could potentially harm the performance of the LSKronF.
 
@@
     \newpage
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Least-Square Kronecker Product Factorization (LSKronF)
+
+        % This function computes the LSKronF of a given matrix.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: February 2022
+
+        function [Ahat,Bhat] = LSKronF(C,ia,ja,ib,jb)
+            [ic,jc] = size(C);
+
+            I = (ic/ia) + zeros(1,ia);
+            J = (jc/ja) + zeros(1,ja);
+            blocks_of_C = mat2cell(C,I,J);
+
+            k = 1;
+            Chat = complex(zeros(ib*jb,ia*ja),0);
+            for j = 1:ja
+                for i = 1:ia
+                    vec_of_block = cell2mat(blocks_of_C(i,j));
+                    vec_of_block = vec_of_block(:);
+                    Chat(:,k) = vec_of_block;
+                    k = k + 1;
+                end
+            end
+
+            [U,S,V] = svd(Chat);
+            ahat = sqrt(S(1,1)).*conj(V(:,1));
+            bhat = sqrt(S(1,1)).*U(:,1);
+            Ahat = reshape(ahat,[ia ja]);
+            Bhat = reshape(bhat, [ib jb]);
+        end
+
+        %% ----- Homework 4 ----- %%
+        clc;
+        clear;
+        close all;
+
+        A = randn(4,2) + 1j*randn(4,2);
+        B = randn(6,3) + 1j*randn(6,3);
+        X = tensor.mtx_prod_kron(A,B);
+        [Ahat,Bhat] = tensor.LSKronF(X,4,2,6,3);
+        Xhat = tensor.mtx_prod_kron(Ahat,Bhat);
+
+        disp('Checking the NMSE (dB) between the original matrix X and its'...
+            'reconstruction with LSKronF:')
+        nmsex = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+        nmsex = 20*log10(nmsex)
+        disp('Checking the NMSE (dB) between the original matrix A and its'...
+            'estimation:')
+        nmsea = (norm(A- Ahat,'fro')^2)/(norm(A,'fro')^2);
+        nmsea = 20*log10(nmsea)
+        disp('Checking the NMSE (dB) between the original matrix B and its'...
+            'estimation:')
+        nmseb = (norm(B- Bhat,'fro')^2)/(norm(B,'fro')^2);
+        nmseb = 20*log10(nmseb)
+
+        I = 2;
+        J = 4;
+        P = 3;
+        Q = 5;
+        SNR = [0 5 10 15 20 25 30];
+        nmse = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            for mc = 1:1000
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise/2)*(randn(I*J,P*Q) + 1j*randn(I*J,P*Q));
+
+                A = randn(I,P) + 1j*randn(I,P);
+                B = randn(J,Q) + 1j*randn(J,Q);
+                X = tensor.mtx_prod_kron(A,B);
+                X_noisy = X + noise;
+
+                [Ahat,Bhat] = tensor.LSKronF(X_noisy,I,P,J,Q);
+                Xhat = tensor.mtx_prod_kron(Ahat,Bhat);
+                aux = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse(snr,1) = nmse(snr,1) + 20*log10(aux);
+            end
+        end
+        nmse  = nmse/1000;
+
+        figure
+        txt = ['I = ' num2str(I), ', J = ' num2str(J), ', P = ' num2str(P),...
+            ' and Q = ' num2str(Q)];
+        plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+
+        I = 4;
+        J = 8;
+        P = 3;
+        Q = 5;
+        SNR = [0 5 10 15 20 25 30];
+        nmse = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            for mc = 1:1000
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise/2)*(randn(I*J,P*Q) + 1j*randn(I*J,P*Q));
+
+                A = randn(I,P) + 1j*randn(I,P);
+                B = randn(J,Q) + 1j*randn(J,Q);
+                X = tensor.mtx_prod_kron(A,B);
+                X = X + noise;
+
+                [Ahat,Bhat] = tensor.LSKronF(X,I,P,J,Q);
+                Xhat = tensor.mtx_prod_kron(Ahat,Bhat);
+                aux = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse(snr,1) = nmse(snr,1) + 20*log10(aux);
+            end
+        end
+        nmse  = nmse/1000;
+
+        txt = ['I = ' num2str(I), ', J = ' num2str(J), ', P = ' num2str(P),...
+            ' and Q = ' num2str(Q)];
+        plot(SNR,nmse,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['LSKronF performance under imperfect scenario'])
+        xlabel('SNR (dB)')
+        ylabel('NMSE (dB)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw4.png')
+    \end{verbatim}
+
+\newpage
 \section*{Homework 5 \\ Kronecker Product Singular Value Decomposition (KPSVD)}
 
-    \subsection*{Implementation KPSVD}
+    \subsection*{Implementation and Validation of KPSVD}
+
+    The KPSVD algorithm aims to solve the following estimation problem
 
@@
 
-    In the example is considered that the original matrix has a full rank equals to 9, then two approximations using the KPSVD are provided: One using the full-rank approximation and other using a r-rank approximation $(r < 9)$.
-    The NMSE between some approximations and its original matrix are provided in the sequence
+    Since a validation file was not available I decided to create my own validation by generating a full-rank matrix with $R = 9$ and in sequence two approximations using my KPSVD implementation are provided: \
+    One using the full-rank approximation and other using a r-rank approximation with $r \in \{1,3,5,7\}$.
+The NMSE (dB) between the original matriz $\boldsymbol{X}$ and its low-rank approximations are
+    shown in the following table
 
@@
         \hline
-        Full Rank & Rank = $7$ & Rank = $5$ & Rank = $3$ & Rank = $1$ \\ \hline
+        r = 9 & r = $7$ & r = $5$ & r = $3$ & r = $1$ \\ \hline
         -604.8023 & -51.3722 & -26.7589 & -16.9054 & -6.3068 \\ \hline
@@
 
-    \subsection*{Validation of KPSVD}
+    and as we can observe the low-rank approximations are not good enought mainly because we are working with a full-rank matrix. Thus, it would be expected to obtain a better
+    performance for low-rank approximations of the matrix $\boldsymbol{X}$ if the matrix would to be rank defficient.
+
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Kronecker Product Single Value Decomposition (KPSVD)
+
+        % This function computes the LSKRF of a given matrix.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: March 2022
+
+        function [U,S,V,rkp] = KPSVD(X,ia,ja,ib,jb)
+            [ix,jx] = size(X);
+
+            I = (ix/ia) + zeros(1,ia);
+            J = (jx/ja) + zeros(1,ja);
+            blocks_of_X = mat2cell(X,I,J);
+
+            k = 1;
+            Xhat = complex(zeros(ib*jb,ia*ja),0);
+            for j = 1:ja
+                for i = 1:ia
+                    vec_of_block = cell2mat(blocks_of_X(i,j));
+                    vec_of_block = vec_of_block(:);
+                    Xhat(:,k) = vec_of_block;
+                    k = k + 1;
+                end
+            end
+            [U,S,V] = svd(Xhat');
+            rkp = sum(sum(S>0));
+        end
+
+        %% ----- Homework 5 ----- %%
+        clc;        % This function computes the LSKRF of a given matrix.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: March 2022
+
+        function [U,S,V,rkp] = KPSVD(X,ia,ja,ib,jb)
+            [ix,jx] = size(X);
+
+            I = (ix/ia) + zeros(1,ia);
+            J = (jx/ja) + zeros(1,ja);
+            blocks_of_X = mat2cell(X,I,J);
+
+            k = 1;
+            Xhat = complex(zeros(ib*jb,ia*ja),0);
+            for j = 1:ja
+                for i = 1:ia
+                    vec_of_block = cell2mat(blocks_of_X(i,j));
+                    vec_of_block = vec_of_block(:);
+                    Xhat(:,k) = vec_of_block;
+                    k = k + 1;
+                end
+            end
+            [U,S,V] = svd(Xhat');
+            rkp = sum(sum(S>0));
+        end
+
+        r1 = 3;
+        c1 = 3;
+        r2 = 3;
+        c2 = 3;
+        rank_of_A = 3;
+
+        % Using the outer product between vectors to control the rank of a matrix.
+        A = complex(zeros(r1*r2,c1*c2),0);
+        for i = 1:rank_of_A
+            aux1 = randn(r1*r2,1)+ 1i*randn(r1*r2,1); 
+            aux2 = randn(1,c1*c2)+ 1i*randn(1,c1*c2); 
+            A = A + aux1*aux2; 
+        end
+        [U,S,V,rkp] = tensor.KPSVD(A,r1,c1,r2,c2);
+
+        % Reconstructing A with full rank.
+        Ahat = complex(zeros(r1*r2,c1*c2),0);
+        for r = 1:rkp
+            aux1 = U(:,r);
+            aux2 = conj(V(:,r));
+            Uk{r} = reshape(aux1,[r1 c1]);
+            Vk{r}  = reshape(aux2, [r2 c2]); 
+            Ahat = Ahat + S(r,r)*tensor.mtx_prod_kron(Uk{r},Vk{r});
+        end 
+        disp('Checking the NMSE (dB) between the original matrix A and its'... 
+            'reconstruction with KPSVD using full rank:')
+        Ahat = conj(Ahat);
+        nmse = (norm(A - Ahat,'fro')^2)/(norm(A,'fro')^2);
+        nmse = 20*log10(nmse)
+
+        % Reconstructing A with deficient rank.
+        Ahat = complex(zeros(r1*r2,c1*c2),0);
+        for r = 1:3
+            aux1 = U(:,r);
+            aux2 = conj(V(:,r));
+            Uk{r} = reshape(aux1,[r1 c1]);
+            Vk{r}  = reshape(aux2, [r2 c2]); 
+            Ahat = Ahat + S(r,r)*tensor.mtx_prod_kron(Uk{r},Vk{r});
+        end  
+        disp('Checking the NMSE (dB) between the original matrix A and its'...
+            'reconstruction with KPSVD using deficient rank:')
+        Ahat = conj(Ahat);
+        nmse = (norm(A - Ahat,'fro')^2)/(norm(A,'fro')^2);
+        nmse = 20*log10(nmse)
+    \end{verbatim}
 
@@
 
-    \subsection*{Implementation unfolding, folding and n-mode product}
+    \subsection*{Implementation and Validation of unfolding, folding and n-mode product}
+
+    The unfolding, folding and n-mode product operations were implemented according the following prototype
 
@@
 
-    \subsection*{Validation of unfolding, folding and n-mode product}
+    and in sequence the provided files were used to validade the algorithms. As it will be possible to see by running the corresponde homework file ('homerwork6.m') it was 
+    possible to validade all the algorithms. Nonentheless, all the three algorithms are generalized for $N$th order tensors and TensorLab was used to verify that.
+
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Unfolding
+
+        % This function computes the unfolding of a given tensor in its matrix.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: April 2022
+
+        function [A] = unfold(ten,mode)
+            dim = size(ten);
+            order = 1:numel(dim);
+            order(mode) = [];
+            order = [mode order];
+            A = reshape(permute(ten,order), dim(mode), prod(dim)/dim(mode));
+        end
+
+        %% Folding
+
+        % This function computes the folding of a given matrix into its tensor.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: April 2022
+
+        % It's interesting to see how the dimmensions get swapped by the unfolding
+        % so the understanding of the code is clear.
+        function [ten] = fold(A,dim,mode)
+            order = 1:numel(dim);
+            order(mode) = [];
+            order = [mode order];
+            dim = dim(order);
+            ten = reshape(A,dim);
+
+            if mode == 1
+                ten = permute(ten,order);
+            else
+                order = 1:numel(dim);
+                for i = 2:mode
+                    order([i-1 i]) = order([i i-1]);
+                end
+                ten = permute(ten,order);
+            end
+        end
+
+        %% N-mode Product
+
+        % This function computes n-mode product of a set of matrices and a tensor.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: April 2022
+
+        function [ten] = n_mod_prod(ten,matrices,modes)
+            dim = size(ten);
+            number = numel(matrices);
+            if nargin < 3
+            modes = 1:number; 
+            end
+
+            for i = modes
+                ten = cell2mat(matrices(i))*tensor.unfold(ten,i);
+                [aux,~] = size(cell2mat(matrices(i)));
+                dim(i) = aux;
+                ten = tensor.fold(ten,[dim],i);
+            end
+        end
+
+        %% ----- Homework 6 ----- %%
+        clc;
+        clear;
+        close all;
+
+        % Tensor for testing
+        disp('Generic Tensor:');
+        load('homework6_unfolding_folding.mat')
+        dimension = size(tenX);
+
+        % Kolda example for testing
+        % load('homework6_kolda_example.mat')
+        % tenX = xxx;
+        % dimension = size(tenX);
+
+        % Unfolding
+        disp('X1./unfold(tenX,1):');
+        tenX_1 = tensor.unfold(tenX,1);
+        X1./tensor.unfold(tenX,1)
+        disp('X2./unfold(tenX,2):');
+        tenX_2 = tensor.unfold(tenX,2);
+        X2./tensor.unfold(tenX,2)
+        disp('X3./unfold(tenX,3):');
+        tenX_3 = tensor.unfold(tenX,3);
+        X3./tensor.unfold(tenX,3)
+
+        % Folding
+        disp('tenX./fold(unfold(tenX,1),1):');
+        tenX./tensor.fold(tenX_1,dimension,1)
+        disp('tenX./fold(unfold(tenX,2),2):');
+        tenX./tensor.fold(tenX_2,dimension,2)
+        disp('tenX./fold(unfold(tenX,3),3):');
+        tenX./tensor.fold(tenX_3,dimension,3)
+
+        % N-mode product
+        load('homework6_n_mode.mat')
+        tenY_test = tensor.n_mod_prod(tenX,{Z},[1]);
+        disp('Checking the NMSE (dB) between the original tensor Y and the one'... 
+            'after the N-mode product:')
+        nmsey = (norm(tensor.unfold(tenY- tenY_test,1),'fro')^2)...
+            /(norm(tensor.unfold(tenY,1),'fro')^2);
+        nmsey = 20*log10(nmsey)
+    \end{verbatim}
 
@@
     \newpage
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Full High Order Single Value Decomposition (HOSVD)
+
+        % This function computes the Truncated HOSVD of a given tensor.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: April 2022
+
+        function [S,U] = HOSVD_full(ten)
+            number = numel(size(ten));
+            for i = 1:number
+            [aux,~,~] = svd(tensor.unfold(ten,i)); 
+            %[aux,~,~] = svd(tens2mat(ten,i)); 
+            U{i} = aux;
+            end
+            % Core tensor uses the hermitian operator.
+            Ut = cellfun(@(x) x', U,'UniformOutput',false); 
+            S = tensor.n_mod_prod(ten,Ut);
+            % The normal factors should be transposed.
+            U = cellfun(@(x) x, U,'UniformOutput',false);  
+        end
+
+        %% Truncated High Order Single Value Decomposition (HOSVD)
+
+        % This function computes the Truncated HOSVD of a given tensor.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: April 2022
+
+        function [S,U] = HOSVD_truncated(ten,ranks)
+            if nargin < 2
+                number = numel(size(ten));
+                for i = 1:number
+                [aux,eig,~] = svd(tensor.unfold(ten,i)); 
+                [aa,~] = size(eig(eig > eps));
+                aux = aux(:,1:aa);
+                U{i} = aux;
+                end
+                % Core tensor uses the hermitian operator.
+                Ut = cellfun(@(x) x', U,'UniformOutput',false); 
+                S = tensor.n_mod_prod(ten,Ut);
+                % The normal factors should be transposed.
+                U = cellfun(@(x) x, U,'UniformOutput',false);
+            else
+                number = numel(size(ten));
+                for i = 1:number
+                [aux,~,~] = svd(tensor.unfold(ten,i)); 
+                aux = aux(:,1:ranks(i));
+                U{i} = aux;
+                end
+                % Core tensor uses the hermitian operator.
+                Ut = cellfun(@(x) x',U,'UniformOutput',false); 
+                S = tensor.n_mod_prod(ten,Ut);
+                % The normal factors should be transposed.
+                U = cellfun(@(x) x,U,'UniformOutput',false);
+            end    
+        end
+
+        %% ----- Homework 7 ----- %%
+        clc;
+        clear;
+        close all;
+
+        % Full HOSVD
+        load('homework7_HOSVD.mat');
+        [tenS_hat,U_hat] = tensor.HOSVD_full(tenX);
+        tenX_hat = tensor.n_mod_prod(tenS_hat,U_hat);
+
+        % Checking the orthogonality
+        disp('Checking the orthogonality propertie between the subtensors'...
+            'formed from the core tensor:')
+        reshape(tenS_hat(:,:,1),[],1)'*reshape(tenS_hat(:,:,4),[],1)
+
+        disp('Checking the NMSE (dB) between the original tensor X and its'... '
+            reconstruction:')
+        nmsex = (norm(tensor.unfold(tenX - tenX_hat,1),'fro')^2)...
+            /(norm(tensor.unfold(tenX,1),'fro')^2);
+        nmsex = 20*log10(nmsex)
+        disp('Checking the NMSE (dB) between the original core tensor S and its'... 
+            'reconstruction:')
+        nmses = (norm(tensor.unfold(tenS - tenS_hat,1),'fro')^2)...
+            /(norm(tensor.unfold(tenS,1),'fro')^2);
+        nmses = 20*log10(nmses)
+
+        disp('Checking the NMSE (dB) between the original matrices and its'... 
+            'estimations:')
+        nmseU1 = (norm(U1 - U_hat{1},'fro')^2)/(norm(U1,'fro')^2)
+        nmseU2 = (norm(U2 - U_hat{2},'fro')^2)/(norm(U2,'fro')^2)
+        nmseU3 = (norm(U3 - U_hat{3},'fro')^2)/(norm(U3,'fro')^2)
+
+        % Truncated HOSVD and Denoising
+        X = randn(8,4,10) + 1i*randn(8,4,10);
+        Y = randn(5,5,5) + 1i*randn(5,5,5);
+
+        [S1,U1] = tensor.HOSVD_truncated(X);
+        multilinear_rank1 = size(S1);
+        [S2,U2] = tensor.HOSVD_truncated(Y);
+        multilinear_rank2 = size(S2);
+
+        Xhat = tensor.n_mod_prod(S1,U1);
+        Yhat = tensor.n_mod_prod(S2,U2);
+
+        disp('Checking the NMSE (dB) between the original noisy tensor X and'... 
+            'its reconstruction:')
+        nmsex = (norm(tensor.unfold(X- Xhat,1),'fro')^2)...
+            /(norm(tensor.unfold(X,1),'fro')^2);
+        nmsex = 20*log10(nmsex)
+        disp('Checking the NMSE (dB) between the original noisy tensor Y'...
+            'and its reconstruction:')
+        nmsey = (norm(tensor.unfold(Y- Yhat,1),'fro')^2)...
+            /(norm(tensor.unfold(Y,1),'fro')^2);
+        nmsey = 20*log10(nmsey)
+
+        disp('The multilinear rank for the tensor X is:')
+        size(S1)
+        disp('The multilinear rank for the tensor Y is:')
+        size(S2)
+    \end{verbatim}
+
+\newpage
 \section*{Homework 8 \\ High Order Order Orthogonal Iteration (HOOI)}
@@
     \newpage
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% High Order Orthogonal Iteration (HOOI)
+
+        % This function computes the HOOI of a given tensor.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: May 2022
+
+        function [S,U,k] = HOOI_full(ten)
+            max_iter = 10;
+            [~, U] = tensor.HOSVD_full(ten);
+            number = numel(size(ten));
+            for k = 1:max_iter
+                for i = 1:number
+                    modes = 1:number;
+                    modes(i) = []; % It will skip this mode in the n_mod_prod.
+                    Un = tensor.n_mod_prod(ten,U,modes);
+                    [aux,~,~] = svd(tensor.unfold(Un,i));
+                    U{i} = aux;
+                end
+            end
+            % The conjugate transpose
+            Ut = cellfun(@(x) x', U ,'UniformOutput',false);
+            S = tensor.n_mod_prod(ten,Ut); 
+        end
+
+        %% Truncated High Order Orthogonal Iteration (HOOI)
+
+        % This function computes the Truncated HOOI of a given tensor.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: May 2022
+
+        function [S,U] = HOOI_truncated(ten,ranks)
+            if nargin < 2
+                max_iter = 10;
+                [~, U] = tensor.HOSVD_full(ten);
+                number = numel(size(ten));
+                for k = 1:max_iter
+                    for i = 1:number
+                        modes = 1:number;
+                        modes(i) = []; % It will skip this mode in the n_mod_prod.
+                        Un = tensor.n_mod_prod(ten,U,modes);
+                        [aux,eig,~] = svd(tensor.unfold(Un,i));
+                        [aa,~] = size(eig(eig > eps));
+                        U{i} = aux(:,1:aa);
+                    end
+                end
+                % The conjugate transpose
+                Ut = cellfun(@(x) x', U ,'UniformOutput',false);
+                S = tensor.n_mod_prod(ten,Ut); 
+            else
+                max_iter = 10;
+                [~, U] = tensor.HOSVD_full(ten);
+                number = numel(size(ten));
+                for k = 1:max_iter
+                    for i = 1:number
+                        modes = 1:number;
+                        modes(i) = []; % It will skip this mode in the n_mod_prod.
+                        Un = tensor.n_mod_prod(ten,U,modes);
+                        [aux,~,~] = svd(tensor.unfold(Un,i));
+                        U{i} = aux(:,1:ranks(i));
+                    end
+                end
+                % The conjugate transpose
+                Ut = cellfun(@(x) x', U ,'UniformOutput',false);
+                S = tensor.n_mod_prod(ten,Ut); 
+            end    
+        end
+
+        %% ----- Homework 8 ----- %%
+        clc;
+        clear;
+        close all;
+
+        % Full HOSVD
+        load('homework8_HOOI.mat');
+        [tenS_hat,U_hat] = tensor.HOOI_full(tenX);
+        tenX_hat = tensor.n_mod_prod(tenS_hat,U_hat);
+
+        % Checking the orthogonality
+        disp('Checking the orthogonality propertie between the subtensors'...
+            'formed from the core tensor:')
+        reshape(tenS_hat(:,:,1),[],1)'*reshape(tenS_hat(:,:,4),[],1)
+
+        disp('Checking the NMSE (dB) between the original tensor X and'...
+            'its reconstruction:')
+        nmsex = (norm(tensor.unfold(tenX - tenX_hat,1),'fro')^2)...
+            /(norm(tensor.unfold(tenX,1),'fro')^2);
+        nmsex = 20*log10(nmsex)
+        disp('Checking the NMSE (dB) between the original core tensor S'...
+            'and its reconstruction:')
+        nmses = (norm(tensor.unfold(tenS - tenS_hat,1),'fro')^2)...
+            /(norm(tensor.unfold(tenS,1),'fro')^2);
+        nmses = 20*log10(nmses)
+
+        disp('Checking the NMSE (dB) between the original matrices and'...
+            'its estimations:')
+        nmseU1 = (norm(U1 - U_hat{1},'fro')^2)/(norm(U1,'fro')^2)
+        nmseU2 = (norm(U2 - U_hat{2},'fro')^2)/(norm(U2,'fro')^2)
+        nmseU3 = (norm(U3 - U_hat{3},'fro')^2)/(norm(U3,'fro')^2)
+
+        % Truncated HOSVD and Denoising
+        X = randn(8,4,10) + 1i*randn(8,4,10);
+        Y = randn(5,5,5) + 1i*randn(5,5,5);
+
+        [S1,U1] = tensor.HOOI_truncated(X);
+        multilinear_rank1 = size(S1);
+        [S2,U2] = tensor.HOOI_truncated(Y);
+        multilinear_rank2 = size(S2);
+
+        Xhat = tensor.n_mod_prod(S1,U1);
+        Yhat = tensor.n_mod_prod(S2,U2);
+
+        disp('Checking the NMSE (dB) between the original noisy tensor X and'...
+            its reconstruction:')
+        nmsex = (norm(tensor.unfold(X- Xhat,1),'fro')^2)...
+            /(norm(tensor.unfold(X,1),'fro')^2);
+        nmsex = 20*log10(nmsex)
+        disp('Checking the NMSE (dB) between the original noisy tensor Y'...
+            'and its reconstruction:')
+        nmsey = (norm(tensor.unfold(Y- Yhat,1),'fro')^2)...
+            /(norm(tensor.unfold(Y,1),'fro')^2);
+        nmsey = 20*log10(nmsey)
+
+        disp('The multilinear rank for the tensor X is:')
+        size(S1)
+        disp('The multilinear rank for the tensor Y is:')
+        size(S2)
+    \end{verbatim}
+
+\newpage
 \section*{Homework 9 \\ Multidimensional Least-Squares Khatri-Rao Factorization
@@
     \subsection*{Implementation MLS-KRF}
+
+    The MLS-KRF algorithm aims to solve the following estimation problem
 
@@
 
+    as we can see the estimation of the matrix $\boldsymbol{X}$ is perfect, but the estimated factor matrices are far from the original ones. This is simply explained by 
+    the scale ambiguity intrinsic to the MLS-KRF. This could be eliminated if we assume previous knowledge of either the structure of the factor matrices or some of their elements.
+    It is also important to say that the produced algorithm was generalized for a random number of factors.
+
     \subsection*{Monte Carlo Experiment}
 
+    In Figure \ref{fig:hw9} the Monte Carlo Experiment is used to draw the curve for the scenario $(I_{1},I_{2},I_{3},R) = (2,3,4,4)$.
+    As we can observe in this simple channel model the MLSKRF reaches a decent performance. Of course that this is only possible because the original matrix $\boldsymbol{X}$ has
+    a strong Khatri-Rao structure, but if by some reason the channel or the noise could disrupt this structure (as in the low-snr scenario that we can analyze in the same figure) 
+    then the performance could be an impediment for certain applications.
+
     \begin{figure}[ht!]
         \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw9.png} \par 
+        \includegraphics[width=0.65\linewidth]{figs/hw9.png} \par 
         \caption{Monter Carlo Experiment with 1000 runs for MLS-KRF algorithm.}
@@
     \newpage
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Multidimensional Least-Squares Khatri-Rao Factorization (MLS-KRF)
+
+        % This function computes the MLS-KRF of a given matrix.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: March 2022
+
+        % The dimensions should be inserted in the order that the products are
+        % performed.
+        function [A] = MLSKRF(X,N,dim)
+            [~,R] = size(X); 
+            for r = 1:R
+                xr = X(:,r);
+                tenXr = reshape(xr,flip(dim));
+
+                % Aplicar SVDs consecutivas em estrategia recursiva? Como lidar com
+                % o nd  array nesse caso?
+                [Sr,Ur] = tensor.HOSVD_full(tenXr);
+                for n = 1:N
+                    Ar{r,n} = (Sr(1)^(1/N))*Ur{N - n + 1}(:,1);
+                end
+            end
+
+            for n = 1:N
+            aux = cell2mat(Ar(:,n)); 
+            A{n} = reshape(aux,[dim(n) R]);
+            end
+        end
+
+        %% ----- Homework 9 ----- %%
+        clc;
+        clear;
+        close all;
+
+        load('homework9_MLSKRF.mat')
+
+        N = 3;
+        dim = [5 4 8];
+        [Matrices] = tensor.MLSKRF(X,N,dim); 
+        Xhat = tensor.mtx_prod_kr(Matrices{1},Matrices{2});
+        Xhat = tensor.mtx_prod_kr(Xhat,Matrices{3});
+
+        disp(['Checking the NMSE (dB) between the original matrix X and its'...
+            'reconstruction with MLSKRF:'])
+        nmsex = (norm(X - Xhat,'fro')^2)/(norm(X,'fro')^2);
+        nmsex = 20*log10(nmsex)
+        disp(['Checking the NMSE (dB) between the original matrix A and its'...
+            'estimation:'])
+        nmsea = (norm(A - Matrices{1},'fro')^2)/(norm(A,'fro')^2);
+        nmsea = 20*log10(nmsea)
+        disp(['Checking the NMSE (dB) between the original matrix B and its'...
+            'estimation:'])
+        nmseb = (norm(B - Matrices{2},'fro')^2)/(norm(B,'fro')^2);
+        nmseb = 20*log10(nmseb)
+        disp(['Checking the NMSE (dB) between the original matrix C and its'...
+            'estimation:'])
+        nmsec = (norm(C - Matrices{3},'fro')^2)/(norm(C,'fro')^2);
+        nmsec = 20*log10(nmsec)
+
+        %% Monte Carlo Experiment
+        N = 3;
+        R  = 4;
+        I = 2;
+        J = 3;
+        K = 4;
+        dim = [I J K];
+        SNR = [0 5 10 15 20 25 30];
+        nmse = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            for mc = 1:1000
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise/2)*(randn(I*J*K,R) + 1j*randn(I*J*K,R));
+
+                A = randn(I,R) + 1j*randn(I,R);
+                B = randn(J,R) + 1j*randn(J,R);
+                C = randn(K,R) + 1j*randn(K,R);
+                X = tensor.mtx_prod_kr(A,B);
+                X = tensor.mtx_prod_kr(X,C);
+                X_noisy = X + noise;
+
+                [Matrices] = tensor.MLSKRF(X_noisy,N,dim);
+                Xhat = tensor.mtx_prod_kr(Matrices{1},Matrices{2});
+                Xhat = tensor.mtx_prod_kr(Xhat,Matrices{3});
+                aux = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse(snr,1) = nmse(snr,1) + 20*log10(aux);
+            end
+        end
+        nmse  = nmse/1000;
+
+        figure
+        txt = ['I1 = ' num2str(I), ', I2 = ' num2str(J), ', I3 = ' num2str(K),...
+            ' and R = ' num2str(R)];
+        plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        title(['MLSKRF performance under imperfect scenario'])
+        xlabel('SNR (dB)')
+        ylabel('NMSE (dB)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw9.png')
+    \end{verbatim}
+
+\newpage
 \section*{Homework 10 \\ Multidimensional Least-Squares Kronecker Factorization
@@
     \subsection*{Implementation MLS-KronF}
+
+    The MLS-KronF algorithm aims to solve the following estimation problem
 
@@
 
+    as we can see the estimation of the matrix $\boldsymbol{X}$ is perfect, but the estimated factor matrices are far from the original ones. This is simply explained by 
+    the scale ambiguity intrinsic to the MLS-KronF. This could be eliminated if we assume previous knowledge of either the structure of the factor matrices or some of their elements.
+    It is also important to say that the produced algorithm was generalized for a random number of factors.
+
     \subsection*{Monte Carlo Experiment}
 
-    \begin{figure}[ht!]
-        \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw10.png} \par 
-        \caption{Monter Carlo Experiment with 1000 runs for MLS-KronF algorithm.}
-        \label{fig:hw10} 
-    \end{figure}
+    In Figures \ref{fig:hw10a1}, \ref{fig:hw10a2}, \ref{fig:hw10a3} and \ref{fig:hw10a4} the Monte Carlo Experiment is used to draw the curves for the scenarios 
+    $(I_{1},I_{2},I_{3}) = (J_{1},J_{2},J_{3}) = \{(2,2,2), (5,5,5), (2,3,4)\}$ and $(I_{1},I_{2},I_{3}) = (2,3,4), (J_{1},J_{2},J_{3}) = (5,6,7)$ for both the HOSVD and HOOI initializations. 
+    As we can observe in  this simple channel model the MLSKronF reaches a decent performance. Of course that this is only possible because the original matrix $\boldsymbol{X}$ has a strong 
+    Kronecker structure, but if by some reason the channel or the noise could disrupt this structure (as it can be seen in the low-snr scenarios) then the performance could be an impediment for certain applications.
+    Its also interesting to note that all for all the scenarios it was not possible to verify any significant difference between the two methods of initialization of the MLSKronF.
+
+    \begin{figure*}
+        \centering
+        \begin{subfigure}[b]{0.475\textwidth}
+            \centering
+            \includegraphics[width=\textwidth]{figs/hw10a1.png} 
+            \caption[]%
+            {{\small Scenario 1}}    
+            \label{fig:hw10a1} 
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.475\textwidth}  
+            \centering 
+            \includegraphics[width=\textwidth]{figs/hw10a1.png} 
+            \caption[]%
+            {{\small Scenario 2}}    
+            \label{fig:hw10a2} 
+        \end{subfigure}
+        \vskip\baselineskip
+        \begin{subfigure}[b]{0.475\textwidth}   
+            \centering 
+            \includegraphics[width=\textwidth]{figs/hw10a3.png} 
+            \caption[]%
+            {{\small Scenario 3}}    
+            \label{fig:hw10a3} 
+        \end{subfigure}
+        \hfill
+        \begin{subfigure}[b]{0.475\textwidth}   
+            \centering 
+            \includegraphics[width=\textwidth]{figs/hw10a4.png} 
+            \caption[]%
+            {{\small Scenario 4}}    
+            \label{fig:hw10a4} 
+        \end{subfigure}
+        \caption[Monter Carlo Experiment with 1000 runs for MLS-KronF algorithm.]
+        {\small Monter Carlo Experiment with 1000 runs for MLS-KronF algorithm.} 
+        \label{fig:mean and std of nets}
+    \end{figure*}
+
+    \newpage
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Multidimensional Least-Squares Kronecker Factorization (MLS-KronF)
+
+        % This function computes the MLS-KronF of a given matrix.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: March 2022
+
+        % It is interesting to note that this process could easily be applied to a
+        % random number of matrices in a iterative form considering groups of 3 objects.
+        % init controls the initialization: 1 for HOSVD and 2 for HOOI.
+        function [Ahat] = MLSKronF(X,rows,columns,init)
+            % 3rd structure
+            %[ix,jx] = size(X);
+
+            % 2nd structure
+            I = rows(2)*rows(3) + zeros(1,rows(1));
+            J = columns(2)*columns(3) + zeros(1,columns(1));
+            blocks_of_X = mat2cell(X,I,J);
+
+            % 1st structure
+            Z = 1;
+            for j = 1:columns(1)
+                for i = 1:rows(1)
+                aux = cell2mat(blocks_of_X(i,j));
+                I = rows(3) + zeros(1,rows(2));
+                J = columns(3) + zeros(1,columns(2));
+                blocks_of_aux = mat2cell(aux,I,J);
+                for jj = 1:columns(2)
+                        for ii = 1:rows(2)
+                            vec_of_block = cell2mat(blocks_of_aux(ii,jj));
+                            vec_of_block = vec_of_block(:);
+                            mtx_1st(:,ii,jj) = vec_of_block;
+                        end
+                end
+                    Xhat(:,Z) = reshape(mtx_1st,[],1);
+                    Z = Z + 1;
+                end 
+            end
+
+            tenXhat = reshape(Xhat,[rows(3)*columns(3), rows(2)*columns(2), rows(1)*columns(1)]);
+            if init == '1'
+                [S,U] = tensor.HOSVD_full(tenXhat);
+            elseif init == '2'
+                [S,U] = tensor.HOOI_full(tenXhat);
+            end
+            rows = flip(rows);
+            columns = flip(columns);
+            for u = 1:length(U)
+                index = length(U) - u + 1;
+                aux = (S(1)^(1/length(U)))*U{u}(:,1);
+                Ahat{index} = reshape(aux,[rows(u) columns(u)]);
+            end
+        end
+
+        %% ----- Homework 10 ----- %%
+        clc;
+        clear;
+        close all;
+
+        load('homework_10_MLSKronF.mat')
+
+        rows = [4 4 6];
+        columns = [3 2 5];
+
+        %% Initialization by HOSVD
+        [Matrices] = tensor.MLSKronF(X,rows,columns,'1');
+        aux1 = tensor.mtx_prod_kron(Matrices{1},Matrices{2});
+        Xhat = tensor.mtx_prod_kron(aux1,Matrices{3});
+        disp(['Checking the NMSE (dB) between the original matrix X and its'...
+            'reconstruction with MLSKronF:'])
+        nmse1 = (norm(X - Xhat,'fro')^2)/(norm(X,'fro')^2);
+        nmse1 = 20*log10(nmse1)
+        disp(['Checking the NMSE (dB) between the original matrix A and its'...
+            'estimation:'])
+        nmsea = (norm(A - Matrices{1},'fro')^2)/(norm(A,'fro')^2);
+        nmsea = 20*log10(nmsea)
+        disp(['Checking the NMSE (dB) between the original matrix B and its'...
+            'estimation:'])
+        nmseb = (norm(B - Matrices{2},'fro')^2)/(norm(B,'fro')^2);
+        nmseb = 20*log10(nmseb)
+        disp(['Checking the NMSE (dB) between the original matrix C and its'...
+            'estimation:'])
+        nmsec = (norm(C - Matrices{3},'fro')^2)/(norm(C,'fro')^2);
+        nmsec = 20*log10(nmsec)
+
+        %% Initialization by HOOI
+        [Matrices] = tensor.MLSKronF(X,rows,columns,'2');
+        aux1 = tensor.mtx_prod_kron(Matrices{1},Matrices{2});
+        Xhat = tensor.mtx_prod_kron(aux1,Matrices{3});
+        disp(['Checking the NMSE (dB) between the original matrix X and its'...
+            'reconstruction with MLSKronF:'])
+        nmse1 = (norm(X - Xhat,'fro')^2)/(norm(X,'fro')^2);
+        nmse1 = 20*log10(nmse1)
+        disp(['Checking the NMSE (dB) between the original matrix A and its'...
+            'estimation:'])
+        nmsea = (norm(A - Matrices{1},'fro')^2)/(norm(A,'fro')^2);
+        nmsea = 20*log10(nmsea)
+        disp(['Checking the NMSE (dB) between the original matrix B and its'...
+            'estimation:'])
+        nmseb = (norm(B - Matrices{2},'fro')^2)/(norm(B,'fro')^2);
+        nmseb = 20*log10(nmseb)
+        disp(['Checking the NMSE (dB) between the original matrix C and its'...
+            'estimation:'])
+        nmsec = (norm(C - Matrices{3},'fro')^2)/(norm(C,'fro')^2);
+        nmsec = 20*log10(nmsec)
+
+        %% Monte Carlo Experiment
+        ia = 2;
+        ib = 2;
+        ic = 2;
+        ja = 2;
+        jb = 2;
+        jc = 2;
+        rows = [ia ib ic];
+        columns = [ja jb jc];
+        SNR = [0 5 10 15 20 25 30];
+        nmse1 = zeros(length(SNR),1);
+        nmse2 = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            for mc = 1:1000
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise/2)*(randn(ia*ib*ic,ja*jb*jc) ...
+                    + 1j*randn(ia*ib*ic,ja*jb*jc));
+
+                A = randn(ia,ja) + 1i*randn(ia,ja);
+                B = randn(ib,jb) + 1i*randn(ib,jb);
+                C = randn(ic,jc) + 1i*randn(ic,jc);
+                X = tensor.mtx_prod_kron(A,B);
+                X = tensor.mtx_prod_kron(X,C);
+                X_noisy = X + noise;
+
+                % HOSVD
+                [Matrices] = tensor.MLSKronF(X_noisy,rows,columns,'1');
+                aux1 = tensor.mtx_prod_kron(Matrices{1},Matrices{2});
+                Xhat = tensor.mtx_prod_kron(aux1,Matrices{3});
+                aux1 = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse1(snr,1) = nmse1(snr,1) + 20*log10(aux1);
+                % HOOI
+                [Matrices] = tensor.MLSKronF(X_noisy,rows,columns,'2');
+                aux2 = tensor.mtx_prod_kron(Matrices{1},Matrices{2});
+                Xhat = tensor.mtx_prod_kron(aux2,Matrices{3});
+                aux2 = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse2(snr,1) = nmse2(snr,1) + 20*log10(aux2);
+            end
+        end
+        nmse1  = nmse1/1000;
+        nmse2  = nmse2/1000;
+
+        figure
+        txt = ['HOSVD Start'];
+        plot(SNR,nmse1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['HOOI Start'];
+        plot(SNR,nmse2,'-x','color', [0 0.4470 0.7410], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['MLSKronF NMSE vs. SNR: (2,2,2,2,2,2)'])
+        xlabel('SNR (dB)')
+        ylabel('NMSE (dB)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw10a1.png')
+
+        ia = 5;
+        ib = 5;
+        ic = 5;
+        ja = 5;
+        jb = 5;
+        jc = 5;
+        rows = [ia ib ic];
+        columns = [ja jb jc];
+        SNR = [0 5 10 15 20 25 30];
+        nmse1 = zeros(length(SNR),1);
+        nmse2 = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            for mc = 1:1000
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise/2)*(randn(ia*ib*ic,ja*jb*jc) ...
+                    + 1j*randn(ia*ib*ic,ja*jb*jc));
+
+                A = randn(ia,ja) + 1i*randn(ia,ja);
+                B = randn(ib,jb) + 1i*randn(ib,jb);
+                C = randn(ic,jc) + 1i*randn(ic,jc);
+                X = tensor.mtx_prod_kron(A,B);
+                X = tensor.mtx_prod_kron(X,C);
+                X_noisy = X + noise;
+
+                % HOSVD
+                [Matrices] = tensor.MLSKronF(X_noisy,rows,columns,'1');
+                aux1 = tensor.mtx_prod_kron(Matrices{1},Matrices{2});
+                Xhat = tensor.mtx_prod_kron(aux1,Matrices{3});
+                aux1 = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse1(snr,1) = nmse1(snr,1) + 20*log10(aux1);
+                % HOOI
+                [Matrices] = tensor.MLSKronF(X_noisy,rows,columns,'2');
+                aux2 = tensor.mtx_prod_kron(Matrices{1},Matrices{2});
+                Xhat = tensor.mtx_prod_kron(aux2,Matrices{3});
+                aux2 = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse2(snr,1) = nmse2(snr,1) + 20*log10(aux2);
+            end
+        end
+        nmse1  = nmse1/1000;
+        nmse2  = nmse2/1000;
+
+        figure
+        txt = ['HOSVD Start'];
+        plot(SNR,nmse1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['HOOI Start'];
+        plot(SNR,nmse2,'-x','color', [0 0.4470 0.7410], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['MLSKronF NMSE vs. SNR: (5,5,5,5,5,5)'])
+        xlabel('SNR (dB)')
+        ylabel('NMSE (dB)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw10a2.png')
+
+        ia = 2;
+        ib = 3;
+        ic = 4;
+        ja = 2;
+        jb = 3;
+        jc = 4;
+        rows = [ia ib ic];
+        columns = [ja jb jc];
+        SNR = [0 5 10 15 20 25 30];
+        nmse1 = zeros(length(SNR),1);
+        nmse2 = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            for mc = 1:1000
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise/2)*(randn(ia*ib*ic,ja*jb*jc) ...
+                    + 1j*randn(ia*ib*ic,ja*jb*jc));
+
+                A = randn(ia,ja) + 1i*randn(ia,ja);
+                B = randn(ib,jb) + 1i*randn(ib,jb);
+                C = randn(ic,jc) + 1i*randn(ic,jc);
+                X = tensor.mtx_prod_kron(A,B);
+                X = tensor.mtx_prod_kron(X,C);
+                X_noisy = X + noise;
+
+                % HOSVD
+                [Matrices] = tensor.MLSKronF(X_noisy,rows,columns,'1');
+                aux1 = tensor.mtx_prod_kron(Matrices{1},Matrices{2});
+                Xhat = tensor.mtx_prod_kron(aux1,Matrices{3});
+                aux1 = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse1(snr,1) = nmse1(snr,1) + 20*log10(aux1);
+                % HOOI
+                [Matrices] = tensor.MLSKronF(X_noisy,rows,columns,'2');
+                aux2 = tensor.mtx_prod_kron(Matrices{1},Matrices{2});
+                Xhat = tensor.mtx_prod_kron(aux2,Matrices{3});
+                aux2 = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse2(snr,1) = nmse2(snr,1) + 20*log10(aux2);
+            end
+        end
+        nmse1  = nmse1/1000;
+        nmse2  = nmse2/1000;
+
+        figure
+        txt = ['HOSVD Start'];
+        plot(SNR,nmse1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['HOOI Start'];
+        plot(SNR,nmse2,'-x','color', [0 0.4470 0.7410], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['MLSKronF NMSE vs. SNR: (2,3,4,2,3,4)'])
+        xlabel('SNR (dB)')
+        ylabel('NMSE (dB)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw10a3.png')
+
+        ia = 2;
+        ib = 3;
+        ic = 4;
+        ja = 5;
+        jb = 6;
+        jc = 7;
+        rows = [ia ib ic];
+        columns = [ja jb jc];
+        SNR = [0 5 10 15 20 25 30];
+        nmse1 = zeros(length(SNR),1);
+        nmse2 = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            for mc = 1:1000
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise/2)*(randn(ia*ib*ic,ja*jb*jc) ...
+                    + 1j*randn(ia*ib*ic,ja*jb*jc));
+
+                A = randn(ia,ja) + 1i*randn(ia,ja);
+                B = randn(ib,jb) + 1i*randn(ib,jb);
+                C = randn(ic,jc) + 1i*randn(ic,jc);
+                X = tensor.mtx_prod_kron(A,B);
+                X = tensor.mtx_prod_kron(X,C);
+                X_noisy = X + noise;
+
+                % HOSVD
+                [Matrices] = tensor.MLSKronF(X_noisy,rows,columns,'1');
+                aux1 = tensor.mtx_prod_kron(Matrices{1},Matrices{2});
+                Xhat = tensor.mtx_prod_kron(aux1,Matrices{3});
+                aux1 = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse1(snr,1) = nmse1(snr,1) + 20*log10(aux1);
+                % HOOI
+                [Matrices] = tensor.MLSKronF(X_noisy,rows,columns,'2');
+                aux2 = tensor.mtx_prod_kron(Matrices{1},Matrices{2});
+                Xhat = tensor.mtx_prod_kron(aux2,Matrices{3});
+                aux2 = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
+                nmse2(snr,1) = nmse2(snr,1) + 20*log10(aux2);
+            end
+        end
+        nmse1  = nmse1/1000;
+        nmse2  = nmse2/1000;
+
+        figure
+        txt = ['HOSVD Start'];
+        plot(SNR,nmse1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['HOOI Start'];
+        plot(SNR,nmse2,'-x','color', [0 0.4470 0.7410], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['MLSKronF NMSE vs. SNR: (2,3,4,5,6,7)'])
+        xlabel('SNR (dB)')
+        ylabel('NMSE (dB)')
+        legend_copy = legend("location", "northwest");
+        set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw10a4.png')
+    \end{verbatim}
 
@@
     \newpage
-\section*{Homework 12 \\ Tensor Kronecker Product Single Value Decomposition (TKPSVD)}
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Alternate Least-Square (ALS)
+
+        % This function computes the ALS of a given tensor.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: April 2022
+
+        function [Ahat,Bhat,Chat,error] = ALS(X,R)
+            I = zeros(R,R,R); 
+            for i = 1:R
+                I(i,i,i) = 1; 
+            end
+            [ia,ib,ic] = size(X);
+
+            mode_1 = tensor.unfold(X,1);
+            mode_2 = tensor.unfold(X,2);
+            mode_3 = tensor.unfold(X,3);
+
+            Ahat = randn(ia,R) + 1j*randn(ia,R);
+            Bhat = randn(ib,R) + 1j*randn(ib,R);
+            Chat = randn(ic,R) + 1j*randn(ic,R);
+
+            aux = 1000;
+            error = zeros(1,aux);
+            error(1) = ((norm((mode_1 - Ahat*(tensor.mtx_prod_kr(Chat,Bhat).')),'fro'))^2)/((norm(mode_1,'fro')^2));
+            for i = 2:aux
+                Bhat = mode_2*pinv((tensor.mtx_prod_kr(Chat,Ahat)).');
+                Chat = mode_3*pinv((tensor.mtx_prod_kr(Bhat,Ahat)).');
+                Ahat = mode_1*pinv((tensor.mtx_prod_kr(Chat,Bhat)).');
+                error(i) = ((norm((mode_1 - Ahat*(tensor.mtx_prod_kr(Chat,Bhat).')),'fro'))^2)/((norm(mode_1,'fro')^2));
+                if abs(error(i) - error(i-1)) < eps
+                    error = error(1:i);
+                    break;
+                else
+                    continue;
+                end
+            end
+        end
+
+        %% ----- Homework 11 ----- %%
+        clc;
+        clear;
+        close all;
+
+        % Random tensor example
+        % I = 8;
+        % J = 4;
+        % K = 5;
+        % R = 3;
+        % A = randn(I,R) + 1j*randn(I,R);
+        % B = randn(J,R) + 1j*randn(J,R);
+        % C = randn(K,R) + 1j*randn(K,R);
+        % X = tensor.fold(A*(tensor.mtx_prod_kr(C,B).'),[I J K],1);
+
+        load('homework_11_CPD.mat')
+        X = tenX;
+        R = 3;
+
+        [ia,ib,ic] = size(X);
+        mode_1 = tensor.unfold(X,1);
+        mode_2 = tensor.unfold(X,2);
+        mode_3 = tensor.unfold(X,3);
+
+        Ahat = randn(ia,R) + 1j*randn(ia,R);
+        Bhat = randn(ib,R) + 1j*randn(ib,R);
+        Chat = randn(ic,R) + 1j*randn(ic,R);
+
+        aux = 10000;
+        error = zeros(1,aux);
+        error(1) = ((norm((mode_1 - Ahat*(tensor.mtx_prod_kr(Chat,Bhat).'))...
+            ,'fro'))^2)/((norm(mode_1,'fro')^2));
+        for i = 2:aux
+            Bhat = mode_2*pinv((tensor.mtx_prod_kr(Chat,Ahat)).');
+            Chat = mode_3*pinv((tensor.mtx_prod_kr(Bhat,Ahat)).');
+            Ahat = mode_1*pinv((tensor.mtx_prod_kr(Chat,Bhat)).');
+            error(i) = ((norm((mode_1 - Ahat*(tensor.mtx_prod_kr(Chat,Bhat).'))...
+                ,'fro'))^2)/((norm(mode_1,'fro')^2));
+            if abs(error(i) - error(i-1)) < eps
+                error = error(1:i);
+                break;
+            else
+                continue;
+            end
+        end
+
+        disp('NMSE (dB) between the original tensor X and its'...
+            'reconstruction with MLSKRF:')
+        Xhat = tensor.fold(Ahat*(tensor.mtx_prod_kr(Chat,Bhat).'),[ia ib ic],1);
+        nmsex = (norm(tensor.unfold(X- Xhat,1),'fro')^2)...
+            /(norm(tensor.unfold(X,1),'fro')^2);
+        nmsex = 20*log10(nmsex)
+        disp('NMSE (dB) between the original matrix A and its estimation:')
+        nmsea = (norm(A - Ahat,'fro')^2)/(norm(A,'fro')^2);
+        nmsea = 20*log10(nmsea)
+        disp('NMSE (dB) between the original matrix B and its estimation:')
+        nmseb = (norm(B - Bhat,'fro')^2)/(norm(B,[0.3010 0.7450 0.9330]'fro')^2);
+        nmseb = 20*log10(nmseb)
+        disp('NMSE (dB) between the original matrix C and its estimation:')
+        nmsec = (norm(C - Chat,'fro')^2)/(norm(C,'fro')^2);
+        nmsec = 20*log10(nmsec)
+
+        figure
+        txt = ['\bf Convergence between iterations'];
+        plot(1:i,20*log10(error),'-','color', [0.3010 0.7450 0.9330],...
+            "linewidth", 2, "markersize", 8, "DisplayName", txt);
+        title(['ALS convergence: I = ' num2str(ia), ', J = ' num2str(ib),...
+            ', K = ' num2str(ic), ' and R = ' num2str(R)])
+        xlabel('Iterations')
+        ylabel('Error (dB)')
+        legend_copy = legend("location", "southwest");
+        set(legend_copy,'Interpreter','tex','location','southwest',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw11a1.png')
+
+        %% ALS in the presence of noisy signals
+
+        I = 8;
+        J = 4;
+        K = 5;
+        R = 3;
+        SNR = [0 5 10 15 20 25 30];
+        nmse1 = zeros(length(SNR),1);
+        nmse2 = zeros(length(SNR),1);
+        nmse3 = zeros(length(SNR),1);
+        nmse4 = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            for mc = 1:1000
+                A = randn(I,R) + 1j*randn(I,R);
+                B = randn(J,R) + 1j*randn(J,R);
+                C = randn(K,R) + 1j*randn(K,R);
+                X = tensor.fold(A*(tensor.mtx_prod_kr(C,B).'),[I J K],1);
+
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise/2)*(randn(I,J,K) + 1j*randn(I,J,K));
+
+                X = X + noise;
+
+                [ia,ib,ic] = size(X);
+                mode_1 = tensor.unfold(X,1);
+                mode_2 = tensor.unfold(X,2);
+                mode_3 = tensor.unfold(X,3);
+                Ahat = randn(ia,R) + 1j*randn(ia,R);
+                Bhat = randn(ib,R) + 1j*randn(ib,R);
+                Chat = randn(ic,R) + 1j*randn(ic,R);
+                aux = 1000;
+                error = zeros(1,aux);
+                error(1) = ((norm((mode_1 - Ahat*(tensor.mtx_prod_kr(Chat...
+                    ,Bhat).')),'fro'))^2)/((norm(mode_1,'fro')^2));
+                for i = 2:aux
+                    Bhat = mode_2*pinv((tensor.mtx_prod_kr(Chat,Ahat)).');
+                    Chat = mode_3*pinv((tensor.mtx_prod_kr(Bhat,Ahat)).');
+                    Ahat = mode_1*pinv((tensor.mtx_prod_kr(Chat,Bhat)).');
+                    error(i) = ((norm((mode_1 - Ahat*(tensor.mtx_prod_kr(Chat...
+                        ,Bhat).')),'fro'))^2)/((norm(mode_1,'fro')^2));
+                    if abs(error(i) - error(i-1)) < 1e-6
+                        error = error(1:i);
+                        break;
+                    else
+                        continue;
+                    end
+                end
+                Xhat = tensor.fold(Ahat*(tensor.mtx_prod_kr(Chat,Bhat).')...
+                    ,[I J K],1);
+
+                aux1 = (norm(A- Ahat,'fro')^2)/(norm(A,'fro')^2);
+                nmse1(snr,1) = nmse1(snr,1) + 20*log10(aux1);
+                aux2 = (norm(B- Bhat,'fro')^2)/(norm(B,'fro')^2);
+                nmse2(snr,1) = nmse2(snr,1) + 20*log10(aux2);
+                aux3 = (norm(C- Chat,'fro')^2)/(norm(C,'fro')^2);
+                nmse3(snr,1) = nmse3(snr,1) + 20*log10(aux3);
+                aux4 = (norm(tensor.unfold(X- Xhat,1),'fro')^2)...
+                    /(norm(tensor.unfold(X,1),'fro')^2);
+                nmse4(snr,1) = nmse4(snr,1) + 20*log10(aux4);
+            end
+        end
+        nmse1  = nmse1/1000;
+        nmse2  = nmse2/1000;
+        nmse3  = nmse3/1000;
+        nmse4  = nmse4/1000;
+
+        figure
+        txt = ['\bf A'];
+        plot(SNR,nmse1,'--d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['\bf B'];
+        plot(SNR,nmse2,'--d','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['\bf C'];
+        plot(SNR,nmse3,'--d','color', [0.4660 0.6740 0.1880], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['Reconstruction'];
+        plot(SNR,nmse4,'-o','color', [0 0.4470 0.7410], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['ALS performance: I = ' num2str(I), ', J = ' num2str(J),...
+            ', K = ' num2str(K), ' and R = ' num2str(R)])
+        xlabel('SNR (dB)')
+        ylabel('NMSE (dB)')
+        legend_copy = legend("location", "southwest");
+        set(legend_copy,'Interpreter','tex','location','southwest',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw11a2.png')
+    \end{verbatim}
+
+\newpage
+\section*{Homework 12 \\ Tensor Kronecker Product SVD (TKPSVD)}
 
@@
     \newpage
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Tensor Kronecker Product
+
+        % This function computes the Tensor Kronecker Product of two given tensors. 
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: June 2022
+
+        function C = ten_prod_kron(A,B)
+
+            aux1 = num2cell([size(A)]);
+            aux2 = num2cell([size(B)]);
+
+            A = repelem(A,aux2{:});
+            B = repmat(B,aux1{:});
+            C = A.*B;
+
+        end
+
+        %% Tensor Kronecker Product Single Value Decomposition (TKPSVD)
+
+        % This function computes the TKPSVD of a tensor.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: June 2022
+
+        function [Ahat,Bhat,Chat] = TKPSVD(tenX,tenSize,tenDim,N,R)
+            % First reorder
+            var = 1:length(tenSize);
+            for n = 1:N
+                tenXhatreorder{n} = cell2mat(tenSize(var(n:N:length(tenSize))));
+            end
+            tenXhatreorder = cell2mat(tenXhatreorder);
+            tenXhat = reshape(tenX,tenXhatreorder);
+            % Second reorder
+            var = 1:length(tenSize);
+            for n = 1:N
+                tenXhatpermute{n} = var(n:N:length(tenSize));
+            end
+            tenXhatpermute = cell2mat(tenXhatpermute);
+            tenXhat = permute(tenXhat,tenXhatpermute);
+            % Third reorder
+            tenXhat = reshape(tenXhat,tenDim{:});
+            % ALS estimation
+            [Ahat,Bhat,Chat,~] = tensor.ALS(tenXhat,R);
+        end
+
+        %% ----- Homework 12 ----- %%
+        clc;
+        clear;
+        close all;
+
+        %% TKPSVD 
+        R = 1;
+        N = 3;
+
+        A = zeros(80,R);
+        B = zeros(20,R);
+        C = zeros(8,R);
+        tenX = zeros(100,16,8);
+        for r = 1:R
+            tenA = randn(10,4,2);
+            %tenA = tenA./frob(tenA);
+            A(:,r)= tenA(:);
+            tenB = randn(5,2,2);
+            %tenB = tenB./frob(tenB);
+            B(:,r)= tenB(:);
+            tenC = randn(2,2,2);
+            %tenC = tenC./frob(tenC);
+            C(:,r)= tenC(:);
+            varr = tensor.ten_prod_kron(tenC,tenB);
+            tenX = tenX + tensor.ten_prod_kron(varr,tenA);
+        end
+
+        aux{1} = num2cell(size(tenA));
+        aux{2} = num2cell(size(tenB));
+        aux{3} = num2cell(size(tenC));
+        tenSize = horzcat(aux{:});
+        tenDim = cellfun(@(aux) prod(cell2mat(aux)), aux,'UniformOutput',false);
+
+        tenX = tensor.ten_prod_kron(tenC,tenB);
+        tenX = tensor.ten_prod_kron(tenX,tenA);
+
+        [Ahat,Bhat,Chat] = tensor.TKPSVD(tenX,tenSize,tenDim,N,R);
+
+        aux1 = aux{1};
+        aux2 = aux{2};
+        aux3 = aux{3};
+        tenXhat = zeros(100,16,8);
+        for r = 1:R
+            tenAhat_r = reshape(Ahat(:,r),aux1{:});
+            %tenAhat_r = tenAhat_r./frob(tenAhat_r);
+            tenBhat_r = reshape(Bhat(:,r),aux2{:});
+            %tenBhat_r = tenBhat_r./frob(tenBhat_r);
+            tenChat_r = reshape(Chat(:,r),aux3{:});
+            %tenChat_r = tenChat_r./frob(tenChat_r);
+            varr = tensor.ten_prod_kron(tenChat_r,tenBhat_r);
+            tenXhat = tenXhat + tensor.ten_prod_kron(varr,tenAhat_r);
+        end
+
+        disp('Checking the NMSE (dB) between the original tensor X and its'...
+            'reconstruction with TKPSVD:')
+        nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)...
+            /(norm(tensor.unfold(tenX,1),'fro')^2);
+        nmsex = 20*log10(nmsex)
+        disp('Checking the NMSE (dB) between the original matrix A and its'...
+            'reconstruction with TKPSVD:')
+        nmsea = 20*log10((norm(A- Ahat,'fro')^2)/(norm(A,'fro')^2))
+        disp('Checking the NMSE (dB) between the original matrix B and its'...
+            'reconstruction with TKPSVD:')
+        nmseb = 20*log10((norm(B- Bhat,'fro')^2)/(norm(B,'fro')^2))
+        disp('Checking the NMSE (dB) between the original matrix C and its'...
+            'reconstruction with TKPSVD:')
+        nmsec = 20*log10((norm(C- Chat,'fro')^2)/(norm(C,'fro')^2))
+
+        %% Monte Carlo Simulation
+
+        R = 2;
+        N = 3;
+        SNR = [0 5 10 15 20 25 30];
+        nmse1 = zeros(length(SNR),1);
+        nmse2 = zeros(length(SNR),1);
+        nmse3 = zeros(length(SNR),1);
+        nmse4 = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            snr
+            for mc = 1:1000
+                A = zeros(80,R);
+                B = zeros(20,R);
+                C = zeros(8,R);
+                tenX = zeros(100,16,8);
+                for r = 1:R
+                    tenA = randn(10,4,2);
+                    %tenA = tenA./frob(tenA);
+                    A(:,r)= tenA(:);
+                    tenB = randn(5,2,2);
+                    %tenB = tenB./frob(tenB);
+                    B(:,r)= tenB(:);
+                    tenC = randn(2,2,2);
+                    %tenC = tenC./frob(tenC);
+                    C(:,r)= tenC(:);
+                    varr = tensor.ten_prod_kron(tenC,tenB);
+                    tenX = tenX + tensor.ten_prod_kron(varr,tenA);
+                end
+
+                aux{1} = num2cell(size(tenA));
+                aux{2} = num2cell(size(tenB));
+                aux{3} = num2cell(size(tenC));
+                tenSize = horzcat(aux{:});
+                tenDim = cellfun(@(aux) prod(cell2mat(aux)), aux,...
+                    'UniformOutput',false);
+
+                tenX = tensor.ten_prod_kron(tenC,tenB);
+                tenX = tensor.ten_prod_kron(tenX,tenA);
+
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise)*(randn(size(tenX)));
+                tenX_noisy = tenX + noise;
+
+                [Ahat,Bhat,Chat] = tensor.TKPSVD(tenX_noisy,tenSize,tenDim,N,R);
+
+                aux1 = aux{1};
+                aux2 = aux{2};
+                aux3 = aux{3};
+                tenXhat = zeros(100,16,8);
+                for r = 1:R
+                    tenAhat_r = reshape(Ahat(:,r),aux1{:});
+                    %tenAhat_r = tenAhat_r./frob(tenAhat_r);
+                    tenBhat_r = reshape(Bhat(:,r),aux2{:});
+                    %tenBhat_r = tenBhat_r./frob(tenBhat_r);
+                    tenChat_r = reshape(Chat(:,r),aux3{:});
+                    %tenChat_r = tenChat_r./frob(tenChat_r);
+                    varr = tensor.ten_prod_kron(tenChat_r,tenBhat_r);
+                    tenXhat = tenXhat + tensor.ten_prod_kron(varr,tenAhat_r);
+                end
+
+                var1 = (norm(A - Ahat,'fro')^2)/(norm(A,'fro')^2);
+                nmse1(snr,1) = nmse1(snr,1) + 20*log10(var1);
+                var2 = (norm(B - Bhat,'fro')^2)/(norm(B,'fro')^2);
+                nmse2(snr,1) = nmse2(snr,1) + 20*log10(var2);
+                var3 = (norm(C - Chat,'fro')^2)/(norm(C,'fro')^2);
+                nmse3(snr,1) = nmse3(snr,1) + 20*log10(var3);
+                nmse4(snr,1) = nmse4(snr,1) + 20*log10((norm(tensor.unfold(tenX...
+                    - tenXhat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2));
+
+            end
+        end
+        nmse1  = nmse1/1000;
+        nmse2  = nmse2/1000;
+        nmse3  = nmse3/1000;
+        nmse4  = nmse4/1000;
+
+        figure
+        txt = ['\bf A'];
+        plot(SNR,nmse1,'--d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['\bf B'];
+        plot(SNR,nmse2,'--d','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['\bf C'];
+        plot(SNR,nmse3,'--d','color', [0.4660 0.6740 0.1880], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['Reconstruction'];
+        plot(SNR,nmse4,'-o','color', [0 0.4470 0.7410], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['TKPSVD performance under imperfect scenario'])
+        xlabel('SNR (dB)')
+        ylabel('NMSE (dB)')
+        legend_copy = legend("location", "southwest");
+        set(legend_copy,'Interpreter','tex','location','northeast',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw12.png')
+    \end{verbatim}
+
+\newpage
 \section*{Homework 13 \\ Tensor Train Single Value Decomposition (TTSVD)}
@@
 
+    \newpage
+    \subsection*{Produced Algorithm}
+
+    \begin{verbatim}
+        %% Tensor Contraction
+
+        % This function computes the tensor contraction between a tensor and a matrix
+        % or between two tensors.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: June 2022
+
+        function [tenZ] = contraction(tenX,n1,tenY,n2)
+            % Obtaining the unfolds
+            tenX_n = tensor.unfold(tenX,n1);
+            tenY_n = tensor.unfold(tenY,n2);
+            % Obtaining the unfold of the contracted tensor
+            tenZ_n = (tenX_n.')*tenY_n;
+            % Obtaining the fold of the contracted tensor
+            dim_x = size(tenX);
+            dim_x(n1) = [];
+            dim_y = size(tenY);
+            dim_y(n2) = [];
+            dim_z = [dim_x dim_y];
+            tenZ   = tensor.fold(tenZ_n,dim_z,1);
+        end
+
+        %% Tensor Train Single Value Decomposition (TT-SVD)
+
+        % This function computes the TT-SVD of a fourth order tensor but can be extended later.   
+        % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
+        % Created: June 2022
+
+        function [G] = TTSVD(tenX,Ranks)
+            X_size = size(tenX);
+            % Step 1
+            X1 = tensor.unfold(tenX,1);
+            [U1,S1,V1] = svd(X1,'econ');
+            G1 = U1*sqrt(S1);
+            G1 = G1(:,1:Ranks(1));
+            G{1} = G1;
+            % Step 2
+            V1 = sqrt(S1)*V1';
+            V1 = V1(1:Ranks(1),:);
+            X2 = reshape(V1,[Ranks(1)*X_size(2) X_size(3)*X_size(4)]);
+            [U2,S2,V2] = svd(X2,'econ');
+            G2 = U2*sqrt(S2);
+            G2 = G2(:,1:Ranks(2));
+            G{2} = reshape(G2, [Ranks(1) X_size(2) Ranks(2)]);
+            % Step 3
+            V2 = sqrt(S2)*V2';
+            V2 = V2(1:Ranks(2),:);
+            X3 = reshape(V2,[Ranks(2)*X_size(3) X_size(4)]);
+            [U3,S3,V3] = svd(X3,'econ');
+            G3 = U3*sqrt(S3);
+            G3 = G3(:,1:Ranks(3));
+            G{3} = reshape(G3, [Ranks(2) X_size(3) Ranks(3)]);
+            V3 = sqrt(S3)*V3';
+            V3 = V3(1:Ranks(3),:);
+            G{4} = V3;
+
+            %% ----- Homework 13 ----- %%
+        clc;
+        clear;
+        close all;
+
+        %% Tensor Train SVD for a fourth order tensor
+        I1 = 5;
+        I2 = 5;
+        I3 = 5;
+        I4 = 5;
+        Ranks = [3 3 3];
+
+        G1 = randn(I1,Ranks(1));
+        G2 = randn(Ranks(1),I2,Ranks(2));
+        G3 = randn(Ranks(2),I3,Ranks(3));
+        G4 = randn(Ranks(3),I4);
+
+        tenX = tensor.contraction(G1,2,G2,1);
+        tenX = tensor.contraction(tenX,3,G3,1);
+        tenX = tensor.contraction(tenX,4,G4,1);
+
+        [G] = tensor.TTSVD(tenX,Ranks);
+
+        tenXhat = tensor.contraction(G{1},2,G{2},1);
+        tenXhat = tensor.contraction(tenXhat,3,G{3},1);
+        tenXhat = tensor.contraction(tenXhat,4,G{4},1);
+
+        disp('Checking the TTSVD NMSE (dB) from reconstruction using'... 
+            'ranks = [3 3 3]:')
+        nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)...
+            /(norm(tensor.unfold(tenX,1),'fro')^2);
+        nmsex = 20*log10(nmsex)
+
+        Ranks = [2 2 2];
+        [G] = tensor.TTSVD(tenX,Ranks);
+
+        tenXhat = tensor.contraction(G{1},2,G{2},1);
+        tenXhat = tensor.contraction(tenXhat,3,G{3},1);
+        tenXhat = tensor.contraction(tenXhat,4,G{4},1);
+        disp('Checking the TTSVD NMSE (dB) from reconstruction using'... 
+            'ranks = [2 2 2]:')
+        nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)...
+            /(norm(tensor.unfold(tenX,1),'fro')^2);
+        nmsex = 20*log10(nmsex)
+
+        %% Monte Carlo Simulation
+        I1 = 5;
+        I2 = 5;
+        I3 = 5;
+        I4 = 5;
+        Ranks  = [3 3 3];
+        Ranks1 = [2 2 2];
+        Ranks2 = [3 3 3];
+
+        SNR = [0 5 10 15 20 25 30];
+        nmse1 = zeros(length(SNR),1);
+        nmse2 = zeros(length(SNR),1);
+        for snr = 1:length(SNR)
+            snr
+            for mc = 1:1000
+                G1 = randn(I1,Ranks(1));
+                G2 = randn(Ranks(1),I2,Ranks(2));
+                G3 = randn(Ranks(2),I3,Ranks(3));
+                G4 = randn(Ranks(3),I4);
+
+                tenX = tensor.contraction(G1,2,G2,1);
+                tenX = tensor.contraction(tenX,3,G3,1);
+                tenX = tensor.contraction(tenX,4,G4,1);
+
+                var_noise = 1/(10^(SNR(snr)/10));
+                noise = sqrt(var_noise)*(randn(size(tenX)));
+                tenX_noisy = tenX + noise;
+
+                [GR1] = tensor.TTSVD(tenX_noisy,Ranks1);
+                tenXhat = tensor.contraction(GR1{1},2,GR1{2},1);
+                tenXhat = tensor.contraction(tenXhat,3,GR1{3},1);
+                tenXhat = tensor.contraction(tenXhat,4,GR1{4},1);
+                nmse1(snr,1) = nmse1(snr,1) + 20*log10((norm(tensor.unfold(tenX...
+                    - tenXhat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2));
+
+                [GR2] = tensor.TTSVD(tenX_noisy,Ranks2);
+                tenXhat = tensor.contraction(GR2{1},2,GR2{2},1);
+                tenXhat = tensor.contraction(tenXhat,3,GR2{3},1);
+                tenXhat = tensor.contraction(tenXhat,4,GR2{4},1);
+                nmse2(snr,1) = nmse2(snr,1) + 20*log10((norm(tensor.unfold(tenX... 
+                    - tenXhat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2));
+
+            end
+        end
+        nmse1  = nmse1/1000;
+        nmse2  = nmse2/1000;
+
+        figure
+        txt = ['Ranks = [2 2 2]'];
+        plot(SNR,nmse1,'--d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold on;
+        txt = ['Ranks = [3 3 3]'];
+        plot(SNR,nmse2,'-o','color', [0 0.4470 0.7410], "linewidth", 2,...
+            "markersize", 8, "DisplayName", txt);
+        hold off;
+        title(['TTSVD performance under imperfect scenario'])
+        xlabel('SNR (dB)')
+        ylabel('NMSE (dB)')
+        legend_copy = legend("location", "southwest");
+        set(legend_copy,'Interpreter','tex',"fontsize", 12)
+        grid on;
+        saveas(gcf,'hw13.png')
+    \end{verbatim}
+
 %\bibliographystyle{ieeetr}

### 2022-06-24 MATLAB/homework0.m

@@ -25,10 +25,12 @@ time2 = time2/5000;
 
 figure
 txt = ['(\bf A_{N \times N} \otimes B_{N \times N})^{-1}'];
-semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold on;
 txt = ['\bf A^{-1}_{N \times N} \otimes B^{-1}_{N \times N}'];
-semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold off;
 title(['Performance of inverse operation'])
 xlabel('Number of columns')
@@ -77,10 +79,12 @@ time2 = time2/1000;
 
 figure
 txt = ['\bf (\otimes^{K}_{i = 1}A^{(i)}_{4 \times 4})^{-1}'];
-semilogy(K,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+semilogy(K,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold on;
 txt = ['\bf \otimes^{K}_{i = 1}(A^{(i)}_{4 \times 4})^{-1}'];
-semilogy(K,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+semilogy(K,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold off;
 title(['Multiple Kronecker products performance'])
 xlabel('Number of products')

### 2022-06-24 MATLAB/homework1.m

@@ -25,10 +25,12 @@ time2 = time2/1000;
 
 figure
 txt = ['Native Function'];
-semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold on;
 txt = ['Author Function'];
-semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold off;
 title(['Hadamard product performance'])
 xlabel('Number of columns')
@@ -60,10 +62,12 @@ time2 = time2/1000;
 
 figure
 txt = ['Native Function'];
-semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold on;
 txt = ['Author Function'];
-semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold off;
 title(['Kronecker product performance'])
 xlabel('Number of columns')
@@ -95,10 +99,12 @@ time2 = time2/1000;
 
 figure
 txt = ['Native Function'];
-semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+semilogy(N,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold on;
 txt = ['Author Function'];
-semilogy(N,time2,'-o','color', [0.8500 0.3250 0.0980], "linewidth", 2, "markersize", 8, "DisplayName", txt);
[…]

### 2022-06-24 MATLAB/homework2.m

@@ -17,7 +17,8 @@ for ii = 1:length(I)
         aux = toc;
         time1(ii,1) = time1(ii,1) + aux;
         tic;
-        (tensor.mtx_prod_kr(A,B).'*tensor.mtx_prod_kr(A,B))\(tensor.mtx_prod_kr(A,B).');
+        (tensor.mtx_prod_kr(A,B).'*tensor.mtx_prod_kr(A,B))...
+            \(tensor.mtx_prod_kr(A,B).');
         aux = toc;
         time2(ii,1) = time2(ii,1) + aux;
         tic;
@@ -32,13 +33,16 @@ time3 = time3/250;
 
 figure
 txt = ['1st Method'];
-plot(I,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+plot(I,time1,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold on;
 txt = ['2nd Method'];
-plot(I,time2,'-d','color', [0.8500 0.3250 0.0980], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+plot(I,time2,'-d','color', [0.8500 0.3250 0.0980], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold on;
 txt = ['3rd Method'];
-plot(I,time3,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+plot(I,time3,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold off;
 title(['Khatri-Rao product performance considering 2 columns'])
 xlabel('Number of rows')
@@ -62,7 +66,8 @@ for ii = 1:length(I)
         aux = toc;
         time1(ii,1) = time1(ii,1) + aux;
         tic;
-        (tensor.mtx_prod_kr(A,B).'*tensor.mtx_prod_kr(A,B))\(tensor.mtx_prod_kr(A,B).');
+        (tensor.mtx_prod_kr(A,B).'*tensor.mtx_prod_kr(A,B))...
+            \(tensor.mtx_prod_kr(A,B).');
         aux = toc;
         time2(ii,1) = time2(ii,1) + aux;
         tic;
@@ -77,13 +82,16 @@ time3 = time3/250;
 
[…]

### 2022-06-24 MATLAB/homework3.m

@@ -9,13 +9,16 @@ X = tensor.mtx_prod_kr(A,B);
 [Ahat,Bhat] = tensor.LSKRF(X,4,6);
 Xhat = tensor.mtx_prod_kr(Ahat,Bhat);
 
-disp('Checking the NMSE (dB) between the original matrix X and its reconstruction with LSKRF:')
+disp('Checking the NMSE (dB) between the original matrix X and its'... 
+    'reconstruction with LSKRF:')
 nmsex = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
 nmsex = 20*log10(nmsex)
-disp('Checking the NMSE (dB) between the original matrix A and its estimation:')
+disp('Checking the NMSE (dB) between the original matrix A and its'...
+    'estimation:')
 nmsea = (norm(A- Ahat,'fro')^2)/(norm(A,'fro')^2);
 nmsea = 20*log10(nmsea)
-disp('Checking the NMSE (dB) between the original matrix B and its estimation:')
+disp('Checking the NMSE (dB) between the original matrix B and its'... 
+    'estimation:')
 nmseb = (norm(B- Bhat,'fro')^2)/(norm(B,'fro')^2);
 nmseb = 20*log10(nmseb)
 
@@ -44,7 +47,8 @@ nmse  = nmse/1000;
 
 figure
 txt = ['I = ' num2str(I), ', J = ' num2str(J), ' and R = ' num2str(R)];
-plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold on;
 
 I = 30;
@@ -71,7 +75,8 @@ end
 nmse  = nmse/1000;
 
 txt = ['I = ' num2str(I), ', J = ' num2str(J), ' and R = ' num2str(R)];
-plot(SNR,nmse,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+plot(SNR,nmse,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold off;
 title(['LSKRF performance under imperfect scenario'])
 xlabel('SNR (dB)')

### 2022-06-24 MATLAB/homework4.m

@@ -9,13 +9,16 @@ X = tensor.mtx_prod_kron(A,B);
 [Ahat,Bhat] = tensor.LSKronF(X,4,2,6,3);
 Xhat = tensor.mtx_prod_kron(Ahat,Bhat);
 
-disp('Checking the NMSE (dB) between the original matrix X and its reconstruction with LSKronF:')
+disp('Checking the NMSE (dB) between the original matrix X and its'...
+    'reconstruction with LSKronF:')
 nmsex = (norm(X- Xhat,'fro')^2)/(norm(X,'fro')^2);
 nmsex = 20*log10(nmsex)
-disp('Checking the NMSE (dB) between the original matrix A and its estimation:')
+disp('Checking the NMSE (dB) between the original matrix A and its'...
+    'estimation:')
 nmsea = (norm(A- Ahat,'fro')^2)/(norm(A,'fro')^2);
 nmsea = 20*log10(nmsea)
-disp('Checking the NMSE (dB) between the original matrix B and its estimation:')
+disp('Checking the NMSE (dB) between the original matrix B and its'...
+    'estimation:')
 nmseb = (norm(B- Bhat,'fro')^2)/(norm(B,'fro')^2);
 nmseb = 20*log10(nmseb)
 
@@ -44,8 +47,10 @@ end
 nmse  = nmse/1000;
 
 figure
-txt = ['I = ' num2str(I), ', J = ' num2str(J), ', P = ' num2str(P), ' and Q = ' num2str(Q)];
-plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+txt = ['I = ' num2str(I), ', J = ' num2str(J), ', P = ' num2str(P),...
+    ' and Q = ' num2str(Q)];
+plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
 hold on;
 
 I = 4;
@@ -72,8 +77,10 @@ for snr = 1:length(SNR)
 end
 nmse  = nmse/1000;
 
-txt = ['I = ' num2str(I), ', J = ' num2str(J), ', P = ' num2str(P), ' and Q = ' num2str(Q)];
-plot(SNR,nmse,'-d','color', [0.4660 0.6740 0.1880], "linewidth", 2, "markersize", 8, "DisplayName", txt);
[…]

### 2022-06-24 MATLAB/homework5.m

@@ -27,7 +27,8 @@ for r = 1:rkp
     Vk{r}  = reshape(aux2, [r2 c2]); 
     Ahat = Ahat + S(r,r)*tensor.mtx_prod_kron(Uk{r},Vk{r});
 end 
-disp('Checking the NMSE (dB) between the original matrix A and its reconstruction with KPSVD using full rank:')
+disp('Checking the NMSE (dB) between the original matrix A and its'... 
+    'reconstruction with KPSVD using full rank:')
 Ahat = conj(Ahat);
 nmse = (norm(A - Ahat,'fro')^2)/(norm(A,'fro')^2);
 nmse = 20*log10(nmse)
@@ -41,7 +42,8 @@ for r = 1:3
     Vk{r}  = reshape(aux2, [r2 c2]); 
     Ahat = Ahat + S(r,r)*tensor.mtx_prod_kron(Uk{r},Vk{r});
 end  
-disp('Checking the NMSE (dB) between the original matrix A and its reconstruction with KPSVD using deficient rank:')
+disp('Checking the NMSE (dB) between the original matrix A and its'...
+    'reconstruction with KPSVD using deficient rank:')
 Ahat = conj(Ahat);
 nmse = (norm(A - Ahat,'fro')^2)/(norm(A,'fro')^2);
 nmse = 20*log10(nmse)

### 2022-06-24 MATLAB/homework6.m

@@ -35,6 +35,8 @@ tenX./tensor.fold(tenX_3,dimension,3)
 % N-mode product
 load('homework6_n_mode.mat')
 tenY_test = tensor.n_mod_prod(tenX,{Z},[1]);
-disp('Checking the NMSE (dB) between the original tensor Y and the one after the N-mode product:')
-nmsey = (norm(tensor.unfold(tenY- tenY_test,1),'fro')^2)/(norm(tensor.unfold(tenY,1),'fro')^2);
+disp('Checking the NMSE (dB) between the original tensor Y and the one'... 
+    'after the N-mode product:')
+nmsey = (norm(tensor.unfold(tenY- tenY_test,1),'fro')^2)...
+    /(norm(tensor.unfold(tenY,1),'fro')^2);
 nmsey = 20*log10(nmsey)

### 2022-06-24 MATLAB/homework7.m

@@ -9,17 +9,23 @@ load('homework7_HOSVD.mat');
 tenX_hat = tensor.n_mod_prod(tenS_hat,U_hat);
 
 % Checking the orthogonality
-disp('Checking the orthogonality propertie between the subtensors formed from the core tensor:')
+disp('Checking the orthogonality propertie between the subtensors'...
+    'formed from the core tensor:')
 reshape(tenS_hat(:,:,1),[],1)'*reshape(tenS_hat(:,:,4),[],1)
 
-disp('Checking the NMSE (dB) between the original tensor X and its reconstruction:')
-nmsex = (norm(tensor.unfold(tenX - tenX_hat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2);
+disp('Checking the NMSE (dB) between the original tensor X and its'... '
+    reconstruction:')
+nmsex = (norm(tensor.unfold(tenX - tenX_hat,1),'fro')^2)...
+    /(norm(tensor.unfold(tenX,1),'fro')^2);
 nmsex = 20*log10(nmsex)
-disp('Checking the NMSE (dB) between the original core tensor S and its reconstruction:')
-nmses = (norm(tensor.unfold(tenS - tenS_hat,1),'fro')^2)/(norm(tensor.unfold(tenS,1),'fro')^2);
+disp('Checking the NMSE (dB) between the original core tensor S and its'... 
+    'reconstruction:')
+nmses = (norm(tensor.unfold(tenS - tenS_hat,1),'fro')^2)...
+    /(norm(tensor.unfold(tenS,1),'fro')^2);
 nmses = 20*log10(nmses)
 
-disp('Checking the NMSE (dB) between the original matrices and its estimations:')
+disp('Checking the NMSE (dB) between the original matrices and its'... 
+    'estimations:')
 nmseU1 = (norm(U1 - U_hat{1},'fro')^2)/(norm(U1,'fro')^2)
 nmseU2 = (norm(U2 - U_hat{2},'fro')^2)/(norm(U2,'fro')^2)
 nmseU3 = (norm(U3 - U_hat{3},'fro')^2)/(norm(U3,'fro')^2)
@@ -36,11 +42,15 @@ multilinear_rank2 = size(S2);
 Xhat = tensor.n_mod_prod(S1,U1);
 Yhat = tensor.n_mod_prod(S2,U2);
 
[…]

### 2022-06-24 MATLAB/homework8.m

@@ -9,17 +9,23 @@ load('homework8_HOOI.mat');
 tenX_hat = tensor.n_mod_prod(tenS_hat,U_hat);
 
 % Checking the orthogonality
-disp('Checking the orthogonality propertie between the subtensors formed from the core tensor:')
+disp('Checking the orthogonality propertie between the subtensors'...
+    'formed from the core tensor:')
 reshape(tenS_hat(:,:,1),[],1)'*reshape(tenS_hat(:,:,4),[],1)
 
-disp('Checking the NMSE (dB) between the original tensor X and its reconstruction:')
-nmsex = (norm(tensor.unfold(tenX - tenX_hat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2);
+disp('Checking the NMSE (dB) between the original tensor X and'...
+    'its reconstruction:')
+nmsex = (norm(tensor.unfold(tenX - tenX_hat,1),'fro')^2)...
+    /(norm(tensor.unfold(tenX,1),'fro')^2);
 nmsex = 20*log10(nmsex)
-disp('Checking the NMSE (dB) between the original core tensor S and its reconstruction:')
-nmses = (norm(tensor.unfold(tenS - tenS_hat,1),'fro')^2)/(norm(tensor.unfold(tenS,1),'fro')^2);
+disp('Checking the NMSE (dB) between the original core tensor S'...
+    'and its reconstruction:')
+nmses = (norm(tensor.unfold(tenS - tenS_hat,1),'fro')^2)...
+    /(norm(tensor.unfold(tenS,1),'fro')^2);
 nmses = 20*log10(nmses)
 
-disp('Checking the NMSE (dB) between the original matrices and its estimations:')
+disp('Checking the NMSE (dB) between the original matrices and'...
+    'its estimations:')
 nmseU1 = (norm(U1 - U_hat{1},'fro')^2)/(norm(U1,'fro')^2)
 nmseU2 = (norm(U2 - U_hat{2},'fro')^2)/(norm(U2,'fro')^2)
 nmseU3 = (norm(U3 - U_hat{3},'fro')^2)/(norm(U3,'fro')^2)
@@ -36,11 +42,15 @@ multilinear_rank2 = size(S2);
 Xhat = tensor.n_mod_prod(S1,U1);
 Yhat = tensor.n_mod_prod(S2,U2);
 
[…]

### 2022-06-24 MATLAB/homework9.m

@@ -11,19 +11,24 @@ dim = [5 4 8];
 Xhat = tensor.mtx_prod_kr(Matrices{1},Matrices{2});
 Xhat = tensor.mtx_prod_kr(Xhat,Matrices{3});
 
-disp('Checking the NMSE (dB) between the original matrix X and its reconstruction with MLSKRF:')
+disp(['Checking the NMSE (dB) between the original matrix X and its'...
+    'reconstruction with MLSKRF:'])
 nmsex = (norm(X - Xhat,'fro')^2)/(norm(X,'fro')^2);
 nmsex = 20*log10(nmsex)
-disp('Checking the NMSE (dB) between the original matrix A and its estimation:')
+disp(['Checking the NMSE (dB) between the original matrix A and its'...
+    'estimation:'])
 nmsea = (norm(A - Matrices{1},'fro')^2)/(norm(A,'fro')^2);
 nmsea = 20*log10(nmsea)
-disp('Checking the NMSE (dB) between the original matrix B and its estimation:')
+disp(['Checking the NMSE (dB) between the original matrix B and its'...
+    'estimation:'])
 nmseb = (norm(B - Matrices{2},'fro')^2)/(norm(B,'fro')^2);
 nmseb = 20*log10(nmseb)
-disp('Checking the NMSE (dB) between the original matrix C and its estimation:')
+disp(['Checking the NMSE (dB) between the original matrix C and its'...
+    'estimation:'])
 nmsec = (norm(C - Matrices{3},'fro')^2)/(norm(C,'fro')^2);
 nmsec = 20*log10(nmsec)
 
+%% Monte Carlo Experiment
 N = 3;
 R  = 4;
 I = 2;
@@ -54,8 +59,10 @@ end
 nmse  = nmse/1000;
 
 figure
-txt = ['I1 = ' num2str(I), ', I2 = ' num2str(J), ', I3 = ' num2str(K), ' and R = ' num2str(R)];
-plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
+txt = ['I1 = ' num2str(I), ', I2 = ' num2str(J), ', I3 = ' num2str(K),...
+    ' and R = ' num2str(R)];
+plot(SNR,nmse,'-d','color', [0.3010 0.7450 0.9330], "linewidth", 2,...
+    "markersize", 8, "DisplayName", txt);
[…]

### 2022-06-24 MATLAB/homework_11.m

@@ -28,12 +28,14 @@ Chat = randn(ic,R) + 1j*randn(ic,R);
 
 aux = 10000;
 error = zeros(1,aux);
-error(1) = ((norm((mode_1 - Ahat*(tensor.mtx_prod_kr(Chat,Bhat).')),'fro'))^2)/((norm(mode_1,'fro')^2));
+error(1) = ((norm((mode_1 - Ahat*(tensor.mtx_prod_kr(Chat,Bhat).'))...
+    ,'fro'))^2)/((norm(mode_1,'fro')^2));
 for i = 2:aux
     Bhat = mode_2*pinv((tensor.mtx_prod_kr(Chat,Ahat)).');
     Chat = mode_3*pinv((tensor.mtx_prod_kr(Bhat,Ahat)).');
     Ahat = mode_1*pinv((tensor.mtx_prod_kr(Chat,Bhat)).');
-    error(i) = ((norm((mode_1 - Ahat*(tensor.mtx_prod_kr(Chat,Bhat).')),'fro'))^2)/((norm(mode_1,'fro')^2));
+    error(i) = ((norm((mode_1 - Ahat*(tensor.mtx_prod_kr(Chat,Bhat).'))...
+        ,'fro'))^2)/((norm(mode_1,'fro')^2));
     if abs(error(i) - error(i-1)) < eps
         error = error(1:i);
         break;
@@ -42,24 +44,28 @@ for i = 2:aux
     end
 end
 
-disp('Checking the NMSE (dB) between the original tensor X and its reconstruction with MLSKRF:')
+disp('NMSE (dB) between the original tensor X and its'...
+    'reconstruction with MLSKRF:')
 Xhat = tensor.fold(Ahat*(tensor.mtx_prod_kr(Chat,Bhat).'),[ia ib ic],1);
-nmsex = (norm(tensor.unfold(X- Xhat,1),'fro')^2)/(norm(tensor.unfold(X,1),'fro')^2);
+nmsex = (norm(tensor.unfold(X- Xhat,1),'fro')^2)...
+    /(norm(tensor.unfold(X,1),'fro')^2);
 nmsex = 20*log10(nmsex)
-disp('Checking the NMSE (dB) between the original matrix A and its estimation:')
+disp('NMSE (dB) between the original matrix A and its estimation:')
 nmsea = (norm(A - Ahat,'fro')^2)/(norm(A,'fro')^2);
 nmsea = 20*log10(nmsea)
-disp('Checking the NMSE (dB) between the original matrix B and its estimation:')
[…]

### 2022-06-24 MATLAB/homework_12.m

@@ -1,4 +1,4 @@
-%% ----- Homework 13 ----- %%
+%% ----- Homework 12 ----- %%
 clc;
 clear;
 close all;
@@ -51,14 +51,19 @@ for r = 1:R
     tenXhat = tenXhat + tensor.ten_prod_kron(varr,tenAhat_r);
 end
 
-disp('Checking the NMSE (dB) between the original tensor X and its reconstruction with TKPSVD:')
-nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2);
+disp('Checking the NMSE (dB) between the original tensor X and its'...
+    'reconstruction with TKPSVD:')
+nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)...
+    /(norm(tensor.unfold(tenX,1),'fro')^2);
 nmsex = 20*log10(nmsex)
-disp('Checking the NMSE (dB) between the original matrix A and its reconstruction with TKPSVD:')
+disp('Checking the NMSE (dB) between the original matrix A and its'...
+    'reconstruction with TKPSVD:')
 nmsea = 20*log10((norm(A- Ahat,'fro')^2)/(norm(A,'fro')^2))
-disp('Checking the NMSE (dB) between the original matrix B and its reconstruction with TKPSVD:')
+disp('Checking the NMSE (dB) between the original matrix B and its'...
+    'reconstruction with TKPSVD:')
 nmseb = 20*log10((norm(B- Bhat,'fro')^2)/(norm(B,'fro')^2))
-disp('Checking the NMSE (dB) between the original matrix C and its reconstruction with TKPSVD:')
+disp('Checking the NMSE (dB) between the original matrix C and its'...
+    'reconstruction with TKPSVD:')
 nmsec = 20*log10((norm(C- Chat,'fro')^2)/(norm(C,'fro')^2))
 
 %% Monte Carlo Simulation
@@ -95,7 +100,8 @@ for snr = 1:length(SNR)
         aux{2} = num2cell(size(tenB));
         aux{3} = num2cell(size(tenC));
         tenSize = horzcat(aux{:});
-        tenDim = cellfun(@(aux) prod(cell2mat(aux)), aux,'UniformOutput',false);
[…]

### 2022-06-24 MATLAB/homework_13.m

@@ -25,8 +25,10 @@ tenXhat = tensor.contraction(G{1},2,G{2},1);
 tenXhat = tensor.contraction(tenXhat,3,G{3},1);
 tenXhat = tensor.contraction(tenXhat,4,G{4},1);
 
-disp('Checking the TTSVD NMSE (dB) from reconstruction using ranks = [3 3 3]:')
-nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2);
+disp('Checking the TTSVD NMSE (dB) from reconstruction using'... 
+    'ranks = [3 3 3]:')
+nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)...
+    /(norm(tensor.unfold(tenX,1),'fro')^2);
 nmsex = 20*log10(nmsex)
 
 Ranks = [2 2 2];
@@ -35,8 +37,10 @@ Ranks = [2 2 2];
 tenXhat = tensor.contraction(G{1},2,G{2},1);
 tenXhat = tensor.contraction(tenXhat,3,G{3},1);
 tenXhat = tensor.contraction(tenXhat,4,G{4},1);
-disp('Checking the TTSVD NMSE (dB) from reconstruction using ranks = [2 2 2]:')
-nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2);
+disp('Checking the TTSVD NMSE (dB) from reconstruction using'... 
+    'ranks = [2 2 2]:')
+nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)...
+    /(norm(tensor.unfold(tenX,1),'fro')^2);
 nmsex = 20*log10(nmsex)
 
 %% Monte Carlo Simulation
@@ -71,13 +75,15 @@ for snr = 1:length(SNR)
         tenXhat = tensor.contraction(GR1{1},2,GR1{2},1);
         tenXhat = tensor.contraction(tenXhat,3,GR1{3},1);
         tenXhat = tensor.contraction(tenXhat,4,GR1{4},1);
-        nmse1(snr,1) = nmse1(snr,1) + 20*log10((norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)/(norm(tensor.unfold(tenX,1),'fro')^2));
[…]

### 2022-06-24 MATLAB/tensor.m

@@ -1,6 +1,6 @@
+%% Tensor Algebra Using MATLAB
 classdef tensor
     methods(Static)
-%addpath("~/MATLAB/tensorlab")
 %% Vectorize
 
 % This function computes the vec operator of a given matrix or tensor.   
@@ -373,7 +373,8 @@ end
  
 % It is interesting to note that this process could easily be applied to a
 % random number of matrices in a iterative form considering groups of 3 objects.
-function [Ahat] = MLSKronF(X,rows,columns)
+% init controls the initialization: 1 for HOSVD and 2 for HOOI.
+function [Ahat] = MLSKronF(X,rows,columns,init)
     % 3rd structure
     %[ix,jx] = size(X);
     
@@ -403,8 +404,11 @@ function [Ahat] = MLSKronF(X,rows,columns)
     end
     
     tenXhat = reshape(Xhat,[rows(3)*columns(3), rows(2)*columns(2), rows(1)*columns(1)]);
-    [S,U] = tensor.HOSVD_full(tenXhat);
-    
+    if init == '1'
+        [S,U] = tensor.HOSVD_full(tenXhat);
+    elseif init == '2'
+        [S,U] = tensor.HOOI_full(tenXhat);
+    end
     rows = flip(rows);
     columns = flip(columns);
     for u = 1:length(U)

### 2022-06-24 Additional Problems/PARAFAC and Tensor Rank/manuscript.tex
Updating L2 Q3

@@
         \begin{align}
-            \mathcal{S} = \sum^{R}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{s}^{(3)}_{r},
+            \mathcal{S} = \sum^{R}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \cdots \circ \boldsymbol{s}^{(N)}_{r},
         \end{align}
@@
         Now, we only need to proof that either one of them are a tensor with rank three.
-The easiest way to do this is by working with the core tensor of the multilinear transformation, the tensor $\mathcal{S}$, and start a proof by contradiction.
+The easiest way to do this is by working with the core tensor of the multilinear transformation, the tensor $\mathcal{S}$, and start
+        a proof by contradiction defining that $rank(\mathcal{S}) = 2$. This means that we can write the PARAFAC Decomposition of this tensor assunto
+
+        \begin{align}
+            \mathcal{S} = \sum^{2}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \boldsymbol{s}^{(2)}_{r} \circ \boldsymbol{s}^{(3)}_{r},
+        \end{align}
 

### 2022-06-24 Report/manuscript.tex
Updating L2 Q3

@@
     and by implementing the algorithm it was possible to reach the following table of NMSE (dB) values using the validation files 
+    for the HOSVD and HOOI initialization, respectively.
 
@@
 
-    as we can see the estimation of the matrix $\boldsymbol{X}$ is perfect, but the estimated factor matrices are far from the original ones. This is simply explained by 
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|l|l|}
+        \hline
+        NNMSE($\boldsymbol{X}, \boldsymbol{\hat{X}}$) & NMSE($\boldsymbol{A}_{1}, \boldsymbol{\hat{A}}_{1}$) & NMSE($\boldsymbol{A}_{2}, \boldsymbol{\hat{A}}_{2}$) & NMSE($\boldsymbol{A}_{3}, \boldsymbol{\hat{A}}_{3}$) \\ \hline
+        -608.4705 & +5.4597 & +15.0478 & +5.8977 \\ \hline
+        \end{tabular}
+    \end{table}
+
+    as we can see the estimation of the matrix $\boldsymbol{X}$ is perfect, but the estimated factor matrices are far from the original ones for both cases. This is simply explained by 
     the scale ambiguity intrinsic to the MLS-KronF. This could be eliminated if we assume previous knowledge of either the structure of the factor matrices or some of their elements.
@@
             \centering 
-            \includegraphics[width=\textwidth]{figs/hw10a1.png} 
+            \includegraphics[width=\textwidth]{figs/hw10a2.png} 
             \caption[]%

### 2022-06-26 Additional Problems/PARAFAC and Tensor Rank/manuscript.tex
Finished L2 Q3

@@
         \begin{align}
-            \mathcal{S} = \sum^{2}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \boldsymbol{s}^{(2)}_{r} \circ \boldsymbol{s}^{(3)}_{r},
+            \mathcal{S} &= \sum^{2}_{r = 1} \boldsymbol{s}^{(1)}_{r} \circ \boldsymbol{s}^{(2)}_{r} \circ \boldsymbol{s}^{(3)}_{r},     
         \end{align}
+
+        where it is possible to rewrite the core tensor using the frontal slices notations for the PARAFAC model
+
+        \begin{align}
+            \mathcal{S}_{...1} &= \sum^{2}_{r = 1} s^{(3)}_{1,r} \boldsymbol{s}^{(1)}_{r} \boldsymbol{s}^{(2)^{\text{T}}}_{r} = \boldsymbol{S}^{(1)} \text{D}_{1}\left(\boldsymbol{S}^{(3)}\right) \boldsymbol{S}^{(2)^{\text{T}}}, \\
+            \mathcal{S}_{...2} &= \sum^{2}_{r = 1} s^{(3)}_{2,r} \boldsymbol{s}^{(1)}_{r} \boldsymbol{s}^{(2)^{\text{T}}}_{r} = \boldsymbol{S}^{(1)} \text{D}_{2}\left(\boldsymbol{S}^{(3)}\right) \boldsymbol{S}^{(2)^{\text{T}}},
+        \end{align}
+
+        and if we supose that $\mathcal{S}_{...1} = \boldsymbol{I}$ and then rewrite it with the SVD
+
+        \begin{align}
+            \mathcal{S}_{...1} &= \boldsymbol{U} \boldsymbol{\Sigma} \boldsymbol{V}^{\text{T}} = \boldsymbol{S}^{(1)} \text{D}_{1}\left(\boldsymbol{S}^{(3)}\right) \boldsymbol{S}^{(2)^{\text{T}}} = \boldsymbol{I}, \\
+        \end{align}
+
+        and we know that the SVD of the identity matrix leads to $\boldsymbol{U} = \boldsymbol{\Sigma} = \boldsymbol{V}^{\text{T}} = \boldsymbol{I}$.
+By inspecting above expression it also possible to write the following relations
+
+        \begin{align}
+            \boldsymbol{S}^{(1)} &= \boldsymbol{U} = \boldsymbol{I}, \\
+            \boldsymbol{S}^{(2)} &= \boldsymbol{V} = \boldsymbol{I}, \\
+            \text{D}_{1}\left(\boldsymbol{S}^{(3)}\right) &= \boldsymbol{\Sigma} = \boldsymbol{I}, 
+        \end{align}
+
+        and since $\boldsymbol{S}^{(1)} = \boldsymbol{S}^{(2)}  = \boldsymbol{I}$  then it is possible to write
+
+        \begin{align}
+            \mathcal{S}_{...2} &= \boldsymbol{S}^{(1)} \text{D}_{2}\left(\boldsymbol{S}^{(3)}\right) \boldsymbol{S}^{(2)^{\text{T}}}, \\
+            \mathcal{S}_{...2} &= \boldsymbol{S}^{(1)} \boldsymbol{S}^{(1)} \text{D}_{2}\left(\boldsymbol{S}^{(3)}\right) \boldsymbol{S}^{(2)^{\text{T}}} \boldsymbol{S}^{(1)^{-1}}, \\
+            \mathcal{S}_{...2} &= 
+            \begin{bmatrix}
+                1 & 0 \\
+                0 & 1
+            \end{bmatrix}
+            \begin{bmatrix}
+                1 & 0 \\
+                0 & 1
+            \end{bmatrix}
+            \text{D}_{2}\left(\boldsymbol{S}^{(3)}\right)
+            \begin{bmatrix}
+                1 & 0 \\
+                0 & 1
+            \end{bmatrix}
+            \begin{bmatrix}
+                1 & 0 \\
+                0 & 1
+            \end{bmatrix}, \\
+            \mathcal{S}_{...2} &= \text{D}_{2}\left(\boldsymbol{S}^{(3)}\right) = 
+            \begin{bmatrix}
+                s_{21} & 0 \\
+                0 & s_{22}
+            \end{bmatrix},
+        \end{align}
+
+        and thus it is possible to diagonalized the second frontal slice $\mathcal{S}_{...2}$ with matrix $\boldsymbol{S}^{(1)}$.
+However, this similarity transformation leads to an invalid Jordan matrix as defined by $\mathcal{S}_{...2}$.
+Thus, it is not possible
+        to the core tensor $\mathcal{S}$ be rank two and it must be in fact rank three.
 

### 2022-06-29 Report/manuscript.tex
First Final Version of the Report

@@
 
-    \subsection*{Implementation HOSVD}
+    \subsection*{Implementation and Validation of HOSVD}
+
+    The HOSVD algorithm was implemented and validated according the file $"hosvd\_test.mat"$. The HOSVD algorithm is straighfoward  and its process is made by sucessive SVDs
+    for each unfolding of the tensor $\mathcal{X}$. Each $\boldsymbol{U}_{n}$ matrix is formed by the most left autovectors of the SVD of the $n$th mode and the core tensor 
+    $\mathcal{S}$ is made by the inverse multilinear transformation that describes the original tensor $\mathcal{X}$. Finally in the following table there is the NMSE between
+    the validation files and the ones generated by my algorithm.
 
@@
 
-    \subsection*{Validation of HOSVD}
-
-    The multilinear rank advantage is maximized when it comes to process sparce tensors since the dimmensions can be greatly reduced without losing of too much relevant information by analysing the profile of its multiples unfoldings.
-
-    \begin{align}
-        \mathcal{X} &\in \mathbb{C}^{8 \times 4 \times 10} \to \hat{\mathcal{X}} \in \mathbb{C}^{R_{1} \times R_{2} \times R_{3}}, \\ 
-        \mathcal{X} &\in \mathbb{C}^{5 \times 5 \times 5} \to \hat{\mathcal{Y}} \in \mathbb{C}^{P_{1} \times P_{2} \times P_{3}},
-    \end{align}
+    As we can see once more in the HOSVD there is also an scale ambiguity that makes impossible to recover the exact 
+    $\boldsymbol{U}_{n}$ matrices without previous knowledge of the original structure. However, we can see that the reconstruction is perfect since the scale ambiguity cancel out each
+    other when they are used to compose the estimation of the original tensor.
+
+    \subsection*{HOSVD for Data Compression}
+
+    It was asked to implement the truncated HOSVD and validate it with the file $"hosvd\_denoising.mat"$.
+However as far as I could see the file was not provided in the folder with the validation files.
+    Nonetheless the truncated HOSVD was implemented by using the inspection of the SVD profiles of each unfolding of the tensor $\mathcal{X}$.
+The approximation was made by discarding the left singular vector of the SVD
+    that were associated with eigenvalues which values were close to zero.
+In the context of my M.Sc.
+research this function was used to truncate the dimensions of the core tensor and its factors matrices and it was indeed possible
+    to verify that some information can be lost when discarding eigenvalues but the order of loss can usually be controlled by the user.
 
@@
 
-    \subsection*{Implementation HOOI}
+    \subsection*{Implementation and Validation of HOOI}
+
+    The HOOI algorithm was implemented and validated according the file $"hosvd\_test.mat"$. The HOOI algorithm uses the HOSVD as initialization and procceds similarly to the HOSVD by taking sucessive
+    SVDs of each unfolding of the original tensor $\mathcal{X}$. Each $\boldsymbol{U}_{n}$ matrix is formed by the most left autovectors of the SVD of the $n$th mode and the core tensor 
+    $\mathcal{S}$ is made by the inverse multilinear transformation that describes the original tensor $\mathcal{X}$. Finally in the following table there is the NMSE between
+    the validation files and the ones generated by my algorithm.
 
@@
 
-    \subsection*{Validation of HOOI}
-
-    The multilinear rank advantage is maximized when it comes to process sparce tensors since the dimmensions can be greatly reduced without losing of too much relevant information by analysing the profile of its multiples unfoldings.
-
-    \begin{align}
-        \mathcal{X} &\in \mathbb{C}^{8 \times 4 \times 10} \to \hat{\mathcal{X}} \in \mathbb{C}^{R_{1} \times R_{2} \times R_{3}}, \\ 
-        \mathcal{X} &\in \mathbb{C}^{5 \times 5 \times 5} \to \hat{\mathcal{Y}} \in \mathbb{C}^{P_{1} \times P_{2} \times P_{3}},
-    \end{align}
+    As we can see again in the HOOI there is also an scale ambiguity that makes impossible to recover the exact 
+    $\boldsymbol{U}_{n}$ matrices without previous knowledge of the original structure. However, we can see that the reconstruction is perfect since the scale ambiguity cancel out each
+    other when they are used to compose the estimation of the original tensor.
+
+    \subsection*{HOOI for Data Compression}
+
+    It was asked to implement the truncated HOOI and validate it with the file $"hosvd\_denoising.mat"$.
+However as far as I could see the file was not provided in the folder with the validation files.
+    Nonetheless the truncated HOOI was implemented by using the previous full-rank HOSVD as initialization and by further inspecting the SVD profiles of each unfolding of the tensor $\mathcal{X}$.
+The approximation was made by discarding the left singular vector of the SVD
+    that were associated with eigenvalues which values were close to zero.
 
@@
 
+    Considering a third order tensor $\mathcal{X}$ obtained by the following expression
+
+    \begin{align}
+        \mathcal{X} = \sum^{R}_{r = 1} \boldsymbol{a}_{r} \circ \boldsymbol{b}_{r} \circ \boldsymbol{c}_{r} \in \mathbb{C}^{I_{1} \times I_{2} \times I_{3}},  
+    \end{align}
+
+    the ALS algorithm aims to solve the following estimation problem
+
     \begin{align}
@@
 
+    and as we can see in the following table it is possible to verify the validation of the implemented ALS algorithm.
+
+    \begin{table}[ht!]
+        \centering
+        \begin{tabular}{|l|l|l|l|}
+        \hline
+        NMSE($\mathcal{X}, \mathcal{\hat{X}}$) & NMSE($\boldsymbol{A}, \boldsymbol{\hat{A}}$) & NMSE($\boldsymbol{B}, \boldsymbol{\hat{B}}$) & NMSE($\boldsymbol{C}, \boldsymbol{\hat{C}}$) \\ \hline
+        -312.1052 & +26.0794 & -0.2457 & +29.8936 \\ \hline
+        \end{tabular}
+    \end{table}
+
+    As to be expected the reconstruction of the original tensor by the estimates of the factor matrices is perfect, but we can not say the same 
+    for the individual estimations of the factor matrices. This is according to the theory since there is a intrinsic scale ambiguity to the ALS
+    algorithm that makes impossible to perfectly estimate the factors without previous knowledge of its structure. However, when we use the estimated factors
+    to reconstruct an estimation for the original tensor the scales ambiguities cancel out each other and then we obtain a perfect estimation of the tensor $\mathcal{X}$.
+
+    \newpage
     \subsection*{Monte Carlo Experiment}
 
+    In Figure \ref{fig:hw11a1} we took a snapshot of the ALS convergence behavior for a random experiment of the asked Monte Carlo Experiment.
+    It is possible to see that for this specific experiment the algorithm took a bit more than 500 iterations to reach the desired convergence.
+    For other experiments it could have taken even less than 50 iterations. Furthermore, if convergence speed is a problem the vanilla ALS could 
+    also be modified to a newer version of the algorithm like the Rectified ALS or Enhanced Line Search (ELS) ALS.
+
     \begin{figure}[ht!]
         \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw11a1.png} \par 
+        \includegraphics[width=0.60\linewidth]{figs/hw11a1.png} \par 
         \caption{Convergence behavior of ALS algorithm.}
@@
 
+    In Figure \ref{fig:hw11a2} the Monte Carlo Experiment is used to draw the average behavior of the estimation of the factors 
+    that generate a tensor $\mathcal{X}$ using the ALS algorithm. As we can observe the factor matrices does not show any improvements in its 
+    estimation as the SNR gets bigger. This is just a consequence of the scale ambiguity problem that was commented in the previous section. Nonentheless, 
+    we can also verify that at least for the curve that represents that tensor reconstruction the performance gets better as the variance of the noise that 
+    corrupts the original tensor $\mathcal{X}$ decreases.
+
     \begin{figure}[ht!]
         \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw11a2.png} \par 
+        \includegraphics[width=0.60\linewidth]{figs/hw11a2.png} \par 
         \caption{Monter Carlo Experimento with 1000 runs for ALS algorithm.}
@@
 
+    By using the tensor kronecker product operator it is possible to write the following tensor $\mathcal{X}$
+
     \begin{align}
@@
     \end{align}
+
+    and this tensor can be further decomposed by solving the following problem using the TKPSVD algorithm
+
+    \begin{align}
+        \left( \mathcal{A}^{(1)}_{j}, \mathcal{A}^{(2)}_{j}, \cdots, \mathcal{A}^{(d)}_{j} \right) = \underset{\mathcal{A}^{(1)}_{j}, \mathcal{A}^{(2)}_{j}, \cdots, \mathcal{A}^{(d)}_{j}}{\text{min}} \left| \left| \mathcal{X} - \sigma_{i} \mathcal{A}^{(d)}_{j} \otimes \mathcal{A}^{(d-1)}_{j} \otimes \cdots \otimes \mathcal{A}^{(1)}_{j} \right| \right|_{\text{F}},
+    \end{align}
+
+    and as we can see in the following table it is possible to verify the validation of the implemented TKPSVD algorithm.
 
@@
 
+    As to be expected the reconstruction of the original tensor by the estimates of the factor matrices is perfect, but we can not say the same 
+    for the individual estimations of the factor matrices. This is according to the theory since there is a intrinsic scale ambiguity to the TKPSVD
+    algorithm that makes impossible to perfectly estimate the factors without previous knowledge of its structure. However, when we use the estimated factors
+    to reconstruct an estimation for the original tensor the scales ambiguities cancel out each other and then we obtain a perfect estimation of the tensor $\mathcal{X}$.
+
+    \newpage
     \subsection*{Monte Carlo Experiment}
 
+    In Figure \ref{fig:hw12} the Monte Carlo Experiment is used to draw the average behavior of the TKPSVD. 
+    As we can observe the factor matrices does not show any improvements in its estimation as the SNR gets bigger. This 
+    is just a consequence of the scale ambiguity problem that was commented in the previous section.
+Nonentheless, we can also verify that at least for the curve that represents that tensor reconstruction the performance gets better as
+    the variance of the noise that corrupts the original tensor $\mathcal{X}$ decreases.
+
     \begin{figure}[ht!]
         \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw12.png} \par 
+        \includegraphics[width=0.85\linewidth]{figs/hw12.png} \par 
         \caption{Monter Carlo Experiment with 1000 runs for TKPSVD algorithm.}
@@
 
+    By using the tensor contraction operator it is possible to write the following tensor $\mathcal{X}$
+
     \begin{align}
@@
 
+    and this tensor can be further decomposed by solving the following problem using the TTSVD algorithm
+
     \begin{align}
@@
     \end{align}
+
+    and it is also important to note that the TTSVD one depends of an additional input of the Tensor Train (TT) ranks. 
+    In the validation experiment it was generated a tensor $\mathcal{X}$ that follows a TT structure of $R = (3,3,3)$ and the TTSVD algorithm 
+    was used considering two different scenarios: The TT ranks $R = (3,3,3)$ and $R = (2,2,2)$. As we can see in the table the TTSVD algorithm performance
+    is strongly associated with the correct input of the TT ranks, meaning that the previous knowledge of its values are a must to obtain satisfactory results 
+    for this decomposition.
 
@@
 
+    Finally, in Figure \ref{fig:hw13} we can confirm what was observed in the previous section. The correct knowledge of the TT ranks are essential to reach
+    a decent performance for the TTSVD algorithm. Nonentheless, we can also verify that at least for the scenario $R = (3,3,3)$ the performance gets better as
+    the variance of the noise that corrupts the original tensor $\mathcal{X}$ decreases.
+
     \begin{figure}[ht!]
         \centering 
-        \includegraphics[width=0.75\linewidth]{figs/hw13.png} \par 
+        \includegraphics[width=0.65\linewidth]{figs/hw13.png} \par 
         \caption{Monter Carlo Experiment with 1000 runs for TTSVD algorithm.}

### 2022-06-29 MATLAB/homework7.m

@@ -9,23 +9,23 @@ load('homework7_HOSVD.mat');
 tenX_hat = tensor.n_mod_prod(tenS_hat,U_hat);
 
 % Checking the orthogonality
-disp('Checking the orthogonality propertie between the subtensors'...
-    'formed from the core tensor:')
+disp(['Checking the orthogonality propertie between the subtensors'...
+    'formed from the core tensor:'])
 reshape(tenS_hat(:,:,1),[],1)'*reshape(tenS_hat(:,:,4),[],1)
 
-disp('Checking the NMSE (dB) between the original tensor X and its'... '
-    reconstruction:')
+disp(['Checking the NMSE (dB) between the original tensor X and its'...
+    'reconstruction:'])
 nmsex = (norm(tensor.unfold(tenX - tenX_hat,1),'fro')^2)...
     /(norm(tensor.unfold(tenX,1),'fro')^2);
 nmsex = 20*log10(nmsex)
-disp('Checking the NMSE (dB) between the original core tensor S and its'... 
-    'reconstruction:')
+disp(['Checking the NMSE (dB) between the original core tensor S and its'... 
+    'reconstruction:'])
 nmses = (norm(tensor.unfold(tenS - tenS_hat,1),'fro')^2)...
     /(norm(tensor.unfold(tenS,1),'fro')^2);
 nmses = 20*log10(nmses)
 
-disp('Checking the NMSE (dB) between the original matrices and its'... 
-    'estimations:')
+disp(['Checking the NMSE (dB) between the original matrices and its'... 
+    'estimations:'])
 nmseU1 = (norm(U1 - U_hat{1},'fro')^2)/(norm(U1,'fro')^2)
 nmseU2 = (norm(U2 - U_hat{2},'fro')^2)/(norm(U2,'fro')^2)
 nmseU3 = (norm(U3 - U_hat{3},'fro')^2)/(norm(U3,'fro')^2)
@@ -42,13 +42,13 @@ multilinear_rank2 = size(S2);
 Xhat = tensor.n_mod_prod(S1,U1);
 Yhat = tensor.n_mod_prod(S2,U2);
 
-disp('Checking the NMSE (dB) between the original noisy tensor X and'... 
-    'its reconstruction:')
+disp(['Checking the NMSE (dB) between the original noisy tensor X and'... 
+    'its reconstruction:'])
 nmsex = (norm(tensor.unfold(X- Xhat,1),'fro')^2)...
[…]

### 2022-06-29 MATLAB/homework_11.m

@@ -44,8 +44,8 @@ for i = 2:aux
     end
 end
 
-disp('NMSE (dB) between the original tensor X and its'...
-    'reconstruction with MLSKRF:')
+disp(['NMSE (dB) between the original tensor X and its'...
+    'reconstruction with ALS:'])
 Xhat = tensor.fold(Ahat*(tensor.mtx_prod_kr(Chat,Bhat).'),[ia ib ic],1);
 nmsex = (norm(tensor.unfold(X- Xhat,1),'fro')^2)...
     /(norm(tensor.unfold(X,1),'fro')^2);
@@ -54,7 +54,7 @@ disp('NMSE (dB) between the original matrix A and its estimation:')
 nmsea = (norm(A - Ahat,'fro')^2)/(norm(A,'fro')^2);
 nmsea = 20*log10(nmsea)
 disp('NMSE (dB) between the original matrix B and its estimation:')
-nmseb = (norm(B - Bhat,'fro')^2)/(norm(B,[0.3010 0.7450 0.9330]'fro')^2);
+nmseb = (norm(B - Bhat,'fro')^2)/(norm(B,'fro')^2);
 nmseb = 20*log10(nmseb)
 disp('NMSE (dB) between the original matrix C and its estimation:')
 nmsec = (norm(C - Chat,'fro')^2)/(norm(C,'fro')^2);

### 2022-06-30 Seminar/codes/atlms_mse.m
Updating slides and Channel model

@@ -4,12 +4,13 @@ close all;
 clear all;
 
 % System parameters
-Nh = 5;
-Nv = 5;
-Kh = 3;
-Kv = 3;
-QAM = 2;
-runs = 2500;
+R = 4;
+Nh = 4;
+Nv = 4;
+Kh = 10;
+Kv = 10;
+QAM = 4;
+runs = 100;
 buffer = Nh*Nv;
 Samples = 15000;
 
@@ -29,19 +30,32 @@ for rr = 1:runs
     weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
     weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));
     
-    % M-QAM source signal
+    % Geometric Channel
+    % Angles at the IRS
+    theta_AOD_y = pi*rand(1,R)- pi/2; %AoD y.
+    theta_AOD_x = pi*rand(1,R)- pi/2; %AoD x.
+    % Steering vectors AoD x and y
+    a_x = 1/sqrt(2) * exp(1i*pi*((0:Nh-1).'*(cos(theta_AOD_x).*sin(theta_AOD_y))));
+    a_y = 1/sqrt(2) * exp(1i*pi*((0:Nv-1).'*cos(theta_AOD_y)));
+    A   = tensor.mtx_prod_kr(a_y,a_x); % NhNv x R.
+    
+    % Received Signal
     signal_d = randi([0,1],Samples,1);
     signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-    % Adding noise to the M-QAM source signal
-    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-    signal_x = signal_d + noise;
+    signal_x = zeros(Nh*Nv,Samples-R-1);
+    for ii = 1:(Samples - R - 1)
+        aux = A*signal_d(ii:ii+R-1);
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        signal_x(:,ii) = aux + noise;
+    end
+    
     kh = 1;
     kv = 1;
     % ATLMS algorithm
     for kk = 1:(Kh + Kv):(Kb*(Kh + Kv)) - 5*(Kh + Kv)
         for kh = kk:(kk+Kh-1)
             weights_v(:,kh+1) = weights_v(:,kh);
-            xmtx = signal_x(kh:kh+buffer-1);
+            xmtx = signal_x(:,kh);
[…]

### 2022-06-30 Seminar/codes/atlms_sampling.m

@@ -4,10 +4,12 @@ close all;
 clear all;
 
 % System parameters
-Nh = 5;
-Nv = 5;
-QAM = 2;
-runs = 2500;
+R = 4;
+Nh = 4;
+Nv = 4;
+QAM = 4;
+mu = 0.1;
+runs = 500;
 buffer = Nh*Nv;
 Samples = 15000;
 
@@ -15,10 +17,9 @@ Samples = 15000;
 snr = 30;
 var_noise = 1/(10^(snr/10));  
 
-%% ATLMS with learning step 0.5 and Kh = Kv = 50
-mu = 0.5;
-Kh = 50;
-Kv = 50;
+%% ATLMS with Kh = Kv = 50
+Kh = 10;
+Kv = 10;
 
 % Monter Carlo simulations
 mse = zeros(Samples,1);
@@ -30,19 +31,32 @@ for rr = 1:runs
     weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
     weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));
     
-    % M-QAM source signal
+    % Geometric Channel
+    % Angles at the IRS
+    theta_AOD_y = pi*rand(1,R)- pi/2; %AoD y.
+    theta_AOD_x = pi*rand(1,R)- pi/2; %AoD x.
+    % Steering vectors AoD x and y
+    a_x = 1/sqrt(2) * exp(1i*pi*((0:Nh-1).'*(cos(theta_AOD_x).*sin(theta_AOD_y))));
+    a_y = 1/sqrt(2) * exp(1i*pi*((0:Nv-1).'*cos(theta_AOD_y)));
+    A   = tensor.mtx_prod_kr(a_y,a_x); % NhNv x R.
+    
+    % Received Signal
     signal_d = randi([0,1],Samples,1);
     signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-    % Adding noise to the M-QAM source signal
-    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-    signal_x = signal_d + noise;
+    signal_x = zeros(Nh*Nv,Samples-R-1);
+    for ii = 1:(Samples - R - 1)
+        aux = A*signal_d(ii:ii+R-1);
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        signal_x(:,ii) = aux + noise;
+    end
[…]

### 2022-06-30 Seminar/codes/generate_curves.m

@@ -1,34 +1,0 @@
-% MSE curves
-clc;
-close all;
-clear all;
-atlms_mse;
-clc;
-close all;
-clear all;
-tlms_mse;
-clc;
-close all;
-clear all;
-lms_mse;
-clc;
-close all;
-clear all;
-nlms_mse;
-% ATLMS sampling and time curves
-clc;
-close all;
-clear all;
-atlms_sampling;
-% Modulation curves
-clc;
-close all;
-clear all;
-modulation;
-% SER curves for all algorithms
-clc;
-close all;
-clear all;
-symbol_error_rate;
-
-

### 2022-06-30 Seminar/codes/lms_mse.m

@@ -1,152 +1,0 @@
-%% LMS Algorithm
-clc;
-close all;
-clear all;
-
-% System parameters
-QAM = 2;
-runs = 2500;
-order = 1;
-Samples = 15000;
-
-% Noise energy
-snr = 30;
-var_noise = 1/(10^(snr/10));     
-
-%% 0.1 Learning Step
-mu = 0.1;
-
-% Monter Carlo simulations
-mse = zeros(Samples,1);
-for rr = 1:runs
-	rr
-    % Filter weights
-    weights = complex(zeros(order, Samples),0);
-    
-    % M-QAM source signal
-    signal_d = randi([0,1],Samples,1);
-    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-    
-    % Adding noise to the M-QAM source signal
-    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-    signal_x = signal_d + noise;
-    
-    % LMS algorithm
-    for kk = 1:(Samples - order - 1)
-        % Error between the desired signal and the filtered signal.
-        error = signal_d(kk) - weights(:,kk)' * signal_x(kk:kk+order-1); 
-        % Recursive expression.
-        weights(:,kk+1) = weights(:,kk) + 2 * mu * error * signal_x(kk:kk+order-1);
-        mse(kk,1) =  mse(kk,1) + abs(signal_d(kk) - weights(:,kk+1)'*signal_x(kk:kk+order-1)).^2;
-    end
-end
-mse = mse/runs;
-
-% MSE Curve
-figure
-txt = ['\mu = 0.1'];
-plot(1:Samples, 10*log10(mse),'-','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
-hold on;
-
-%% 0.5 Learning Step
-mu = 0.5;
-
-% Monter Carlo simulations
-mse = zeros(Samples,1);
-for rr = 1:runs
-    % Filter weights
-    weights = complex(zeros(order, Samples),0);
-    
-    % M-QAM source signal
-    signal_d = randi([0,1],Samples,1);
-    signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-    
-    % Adding noise to the M-QAM source signal
-    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-    signal_x = signal_d + noise;
-    
-    % LMS algorithm
[…]

### 2022-06-30 Seminar/codes/modulation.m

@@ -1,237 +1,0 @@
-%% Symbol Error Rate (SER) vs. SNR for different Modulations
-clc;
-close all;
-clear all;
-
-% System parameters
-Nh = 5;
-Nv = 5;
-Kh = 10;
-Kv = 10;
-
-mu = 0.1;
-runs = 1000;
-buffer = Nh*Nv;
-Samples = 15000;
-
-% SNR vector
-SNR = [0 10 20 30];
-
-%% ATLMS SER algorithm for 2-QAM
-QAM = 2;
-
-% Monter Carlo simulations
-ser = zeros(length(SNR),1);
-Kb = floor(Samples/(Kh + Kv));
-for ss = 1:length(SNR)
-    ss
-    for rr = 1:runs
-        rr
-        % Filter weights
-        weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
-        weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));
-
-        % M-QAM source signal
-        signal_d = randi([0,1],Samples,1);
-        signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-        % Adding noise to the M-QAM source signal
-        var_noise = 1/(10^(SNR(ss)/10));  
-        noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-        signal_x = signal_d + noise;
-        kh = 1;
-        kv = 1;
-        % ATLMS algorithm
-        for kk = 1:(Kh + Kv):(Kb*(Kh + Kv)) - 5*(Kh + Kv)
-            for kh = kk:(kk+Kh-1)
-                weights_v(:,kh+1) = weights_v(:,kh);
-                xmtx = signal_x(kh:kh+buffer-1);
-                uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kv));
-                error = signal_d(kh) - (tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh))')*xmtx;
-                mu_norm = mu/(norm(uh,2)^2);
-                weights_h(:,kh+1) = weights_h(:,kh) + mu_norm*uh*conj(error); 
-                weights = tensor.mtx_prod_kron(weights_v(:,kv),weights_h(:,kh));
-                if kh>250
-                    ser(ss,1) =  ser(ss,1) + (qamdemod(signal_d(kh),QAM)~=qamdemod(weights'*xmtx,QAM));
-                end
-            end
[…]

### 2022-06-30 Seminar/codes/nlms_mse.m

@@ -4,9 +4,13 @@ close all;
 clear all;
 
 % System parameters
-QAM = 2;
-runs = 2500;
-order = 1;
+R = 4;
+Nh = 4;
+Nv = 4;
+QAM = 4;
+runs = 1000;
+buffer = Nh*Nv;
+gamma = 0.1;
 Samples = 15000;
 
 % Noise energy
@@ -21,24 +25,35 @@ mse = zeros(Samples,1);
 for rr = 1:runs
 	rr
     % Filter weights
-    weights = complex(zeros(order, Samples),0);
+    weights = complex(zeros(buffer, Samples),0);
     
-    % M-QAM source signal
+    % Geometric Channel
+    % Angles at the IRS
+    theta_AOD_y = pi*rand(1,R)- pi/2; %AoD y.
+    theta_AOD_x = pi*rand(1,R)- pi/2; %AoD x.
+    % Steering vectors AoD x and y
+    a_x = 1/sqrt(2) * exp(1i*pi*((0:Nh-1).'*(cos(theta_AOD_x).*sin(theta_AOD_y))));
+    a_y = 1/sqrt(2) * exp(1i*pi*((0:Nv-1).'*cos(theta_AOD_y)));
+    A   = tensor.mtx_prod_kr(a_y,a_x); % NhNv x R.
+    
+    % Received Signal
     signal_d = randi([0,1],Samples,1);
     signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-    
-    % Adding noise to the M-QAM source signal
-    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-    signal_x = signal_d + noise;
+    signal_x = zeros(Nh*Nv,Samples-R-1);
+    for ii = 1:(Samples - R - 1)
+        aux = A*signal_d(ii:ii+R-1);
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        signal_x(:,ii) = aux + noise;
+    end
     
     % NLMS algorithm
-    for kk = 1:(Samples - order - 1)
-        mu_normalized = mu/(norm(signal_x(kk:kk+order-1)));
-       % Error between the desired signal and the filtered signal.
-        error(kk) = signal_d(kk) - weights(:,kk)' * signal_x(kk:kk+order-1); 
+    for kk = 1:(Samples - buffer - 1)
+        mu_normalized = mu/(gamma + norm(signal_x(:,kk)));
[…]

### 2022-06-30 Seminar/codes/symbol_error_rate.m

@@ -4,13 +4,13 @@ close all;
 clear all;
 
 % System parameters
-Nh = 5;
-Nv = 5;
+R = 4;
+Nh = 4;
+Nv = 4;
 Kh = 10;
 Kv = 10;
-order = 1;
+QAM = 4;
 
-QAM = 2;
 mu = 0.1;
 runs = 100;
 buffer = Nh*Nv;
@@ -26,26 +26,43 @@ ser = zeros(length(SNR),1);
 Kb = floor(Samples/(Kh + Kv));
 for ss = 1:length(SNR)
     ss
+    
+    % Noise energy
+    snr = SNR(ss);
+    var_noise = 1/(10^(snr/10));  
+    
     for rr = 1:runs
         rr
         % Filter weights
         weights_v = complex(ones(Nv,Samples),ones(Nv,Samples));
         weights_h = complex(ones(Nh,Samples),ones(Nh,Samples));
 
-        % M-QAM source signal
+        % Geometric Channel
+        % Angles at the IRS
+        theta_AOD_y = 2*pi*randn(1,R)- pi; %AoD y.
+        theta_AOD_x = 2*pi*randn(1,R)- pi; %AoD x.
+        % Steering vectors AoD x and y
+        a_x = 1/sqrt(2) * exp(1i*pi*((0:Nh-1).'*(cos(theta_AOD_x).*sin(theta_AOD_y))));
+        a_y = 1/sqrt(2) * exp(1i*pi*((0:Nv-1).'*cos(theta_AOD_y)));
+        A   = tensor.mtx_prod_kr(a_y,a_x); % NhNv x R.
+
+        % Received Signal
         signal_d = randi([0,1],Samples,1);
         signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-        % Adding noise to the M-QAM source signal
-        var_noise = 1/(10^(SNR(ss)/10));  
-        noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-        signal_x = signal_d + noise;
+        signal_x = zeros(Nh*Nv,Samples-R-1);
+        for ii = 1:(Samples - R - 1)
+            aux = A*signal_d(ii:ii+R-1);
+            noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+            signal_x(:,ii) = aux + noise;
+        end
+
         kh = 1;
         kv = 1;
         % ATLMS algorithm
[…]

### 2022-06-30 Seminar/codes/tlms_mse.m

@@ -4,10 +4,11 @@ close all;
 clear all;
 
 % System parameters
-Nh = 5;
-Nv = 5;
-QAM = 2;
-runs = 2500;
+R = 4;
+Nh = 4;
+Nv = 4;
+QAM = 4;
+runs = 100;
 buffer = Nh*Nv;
 Samples = 15000;
 
@@ -26,17 +27,28 @@ for rr = 1:runs
     weights_v = complex(randn(Nv,Samples),randn(Nv,Samples));
     weights_h = complex(randn(Nh,Samples),randn(Nh,Samples));
     
-    % M-QAM source signal
+    % Geometric Channel
+    % Angles at the IRS
+    theta_AOD_y = pi*rand(1,R)- pi/2; %AoD y.
+    theta_AOD_x = pi*rand(1,R)- pi/2; %AoD x.
+    % Steering vectors AoD x and y
+    a_x = 1/sqrt(2) * exp(1i*pi*((0:Nh-1).'*(cos(theta_AOD_x).*sin(theta_AOD_y))));
+    a_y = 1/sqrt(2) * exp(1i*pi*((0:Nv-1).'*cos(theta_AOD_y)));
+    A   = tensor.mtx_prod_kr(a_y,a_x); % NhNv x R.
+    
+    % Received Signal
     signal_d = randi([0,1],Samples,1);
     signal_d = 1/sqrt(2) * qammod(signal_d,QAM);
-   
-    % Adding noise to the M-QAM source signal
-    noise = (sqrt(var_noise/2))*(randn(Samples,1) + randn(Samples,1));
-    signal_x = signal_d + noise;
+    signal_x = zeros(Nh*Nv,Samples-R-1);
+    for ii = 1:(Samples - R - 1)
+        aux = A*signal_d(ii:ii+R-1);
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        signal_x(:,ii) = aux + noise;
+    end
     
     % TLMS algorithm
     for kk = 1:(Samples - buffer - 1)
-        xmtx = signal_x(kk:kk+buffer-1);
+        xmtx = signal_x(:,kk);
         uh = reshape(xmtx,[Nh Nv])*conj(weights_v(:,kk));
         uv = (reshape(xmtx,[Nh Nv]).')*conj(weights_h(:,kk));
[…]

### 2022-06-30 Seminar/codes/atlms_mse.m
minor corrections

@@ -45,7 +45,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     
@@ -173,7 +173,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     
@@ -236,7 +236,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     

### 2022-06-30 Seminar/codes/atlms_sampling.m

@@ -46,7 +46,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     
@@ -115,7 +115,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     
@@ -182,7 +182,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     
@@ -254,7 +254,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     

### 2022-06-30 Seminar/codes/nlms_mse.m

@@ -42,7 +42,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     
@@ -134,7 +134,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     
@@ -179,7 +179,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     

### 2022-06-30 Seminar/codes/tlms_mse.m

@@ -42,7 +42,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     
@@ -142,7 +142,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     
@@ -191,7 +191,7 @@ for rr = 1:runs
     signal_x = zeros(Nh*Nv,Samples-R-1);
     for ii = 1:(Samples - R - 1)
         aux = A*signal_d(ii:ii+R-1);
-        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + randn(Nv*Nh,1));
+        noise = (sqrt(var_noise/2))*(randn(Nv*Nh,1) + 1i*randn(Nv*Nh,1));
         signal_x(:,ii) = aux + noise;
     end
     

### 2022-07-07 Seminar/codes/atlms_sampling.m
minor corrections in presentation

@@ -18,8 +18,8 @@ snr = 30;
 var_noise = 1/(10^(snr/10));  
 
 %% ATLMS with Kh = Kv = 50
-Kh = 10;
-Kv = 10;
+Kh = 250;
+Kv = 250;
 
 % Monter Carlo simulations
 mse = zeros(Samples,1);
@@ -82,13 +82,13 @@ mse = mse/runs;
 
 % MSE Curve
 figure
-txt = ['\mu = 0.1 with K_h = K_v = 10'];
+txt = ['\mu = 0.1 with K_h = K_v = 250'];
 plot(1:Samples, 10*log10(mse),'-','color', [0.3010 0.7450 0.9330], "linewidth", 2, "markersize", 8, "DisplayName", txt);
 hold on;
 
 %% ATLMS with Kh = Kv = 250
-Kh = 100;
-Kv = 100;
+Kh = 500;
+Kv = 500;
 
 % Monter Carlo simulations
 mse = zeros(Samples,1);
@@ -149,13 +149,13 @@ aux2 = toc();
 aux2 = aux2/runs;
 mse = mse/runs;
 
-txt = ['\mu = 0.1 with K_h = K_v = 100'];
+txt = ['\mu = 0.1 with K_h = K_v = 500'];
 plot(1:Samples, 10*log10(mse),'-','color', [0.4660 0.6740 0.1880], "linewidth", 2, "markersize", 8, "DisplayName", txt);
 hold on;
 
 %% ATLMS with Kh = Kv = 500
-Kh = 500;
-Kv = 500;
+Kh = 1000;
+Kv = 1000;
 
 % Monter Carlo simulations
 mse = zeros(Samples,1);
@@ -216,7 +216,7 @@ aux3 = toc();
 aux3 = aux3/runs;
 mse = mse/runs;
 
-txt = ['\mu = 0.1 with K_h = K_v = 500'];
+txt = ['\mu = 0.1 with K_h = K_v = 1000'];
 plot(1:Samples, 10*log10(mse),'-','color', [0.9290 0.6940 0.1250], "linewidth", 2, "markersize", 8, "DisplayName", txt);
 hold off;
 title('ATLMS Behavior for Different Learning Steps and Sampling Rate');

### 2022-07-14 MATLAB/homework_13.m
minor corrections

@@ -3,7 +3,7 @@ clc;
 clear;
 close all;
 
-%% Tensor Train SVD for a fourth order tensor
+%% Tensor Train SVD for a fourth order tensor.
 I1 = 5;
 I2 = 5;
 I3 = 5;
@@ -43,7 +43,7 @@ nmsex = (norm(tensor.unfold(tenX- tenXhat,1),'fro')^2)...
     /(norm(tensor.unfold(tenX,1),'fro')^2);
 nmsex = 20*log10(nmsex)
 
-%% Monte Carlo Simulation
+%% Monte Carlo Experiment
 I1 = 5;
 I2 = 5;
 I3 = 5;

### 2022-07-14 MATLAB/tensor.m

@@ -505,7 +505,7 @@ end
 % This function computes the tensor contraction between a tensor and a matrix
 % or between two tensors.   
 % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
-% Created: June 2022
+% Created: July 2022
 
 function [tenZ] = contraction(tenX,n1,tenY,n2)
     % Obtaining the unfolds
@@ -526,7 +526,7 @@ end
 
 % This function computes the TT-SVD of a fourth order tensor but can be extended later.   
 % Author: Kenneth B. dos A. Benicio <kenneth@gtel.ufc.br>
-% Created: June 2022
+% Created: July 2022
 
 function [G] = TTSVD(tenX,Ranks)
     X_size = size(tenX);
